---
title: "Generalized Anxiety Disorder 7-Item Scale (GAD-7)"
author: "Analytics Report generated by Sentient Psychometrics"
date: "`r format(Sys.time(), '%d %B, %Y')`"
geometry: "left=2cm,right=2cm,top=1.5cm,bottom=1.2cm"
output:
  pdf_document:
    latex_engine: pdflatex
header-includes:
- \usepackage[fontsize=7.8pt]{scrextend}
- \usepackage{color}
- \usepackage{booktabs}
- \usepackage[table]{xcolor}
fontfamily: arev
always_allow_html: yes
params:
Imp_Df: 'NULL'
Sig_Imp_Df: 'NULL'
Scale_Report_Df: 'NULL'
Periods: 'NULL'
---


\begingroup\Large

\begin{center} \textbf{Information About the Generalized Anxiety Disorder 7-Item Scale (GAD-7)} \end{center} 

#What it Measures: 

* The symptoms of Generalized Anxiety Disorder, as outlined in the Diagnostic and Statistical Manual of Psychological Disorders, 4th Edition, Text Revision (DSM-IV-TR).


* Symptoms assessed include subjective anxiety, worry, difficulty relaxing, restlessness, irritability and fear of negative outcomes.



#What Higher Scores Mean:

* More severe generalized anxiety symptoms during the previous 2 weeks.


* Greater likelihood of meeting criteria for Generalized Anxiety Disorder or another anxiety disorder (e.g. Panic Disorder, Social Anxiety Disorder, Posttraumatic Stress Disorder). 


* Optimal cut-off scores will vary across settings and populations. As general guidelines, authors recommended that a cut-off score of **10** (Kroenke, Spitzer, Williams & Löwe, 2010) or **8** (Plummer, Manea, Trepel & McMillan, 2015) be employed to identify the presence of any anxiety disorder. They suggest that clinicians undertake a thorough diagnostic evalutation for anxiety disorders when an individual's responses fall above the recommended cut-off score.


#Scale Quality:

* The GAD-7 has well-established psychometric properties and is among the most common screening instruments used to assess generalized anxiety (for systematic reviews, see Kroenke, Spitzer, Williams & Löwe, 2010; Plummer, Manea, Trepel & McMillan, 2015; van Ballegooijen, Riper, Cuijpers, Oppen & Smit, 2016). 


#Scale Structure:

* 7 items.


* 4-point Likert scale.


* Respondents indicate how frequently (0 = "Not at all"; 3 = "Nearly every day") they have been bothered by the problems listed in each item (e.g. "Feeling nervous, anxious or on edge"). 

\endgroup
\newpage

```{r, echo = FALSE, warning = FALSE, comment = NA, results = 'asis'}

    #GAD-7 nonsig calculations 
    
    GAD7_Imp_Df<-dplyr::select(Imp_Df, contains("GAD7.Fullscale"))

    
    GAD7_Imp_Df<-as.data.frame(gather(GAD7_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))

    
    
    #GAD-7 sig calculations
    
    
    GAD7_Sig_Imp_Df<-dplyr::select(Sig_Imp_Df, contains("GAD7.Fullscale"))

    
    GAD7_Sig_Imp_Df<-as.data.frame(gather(GAD7_Sig_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))

    
    Improvement_Type<- c("Improvement", "Statistically Reliable Improvement")
    
    Sig_Null<- data.frame(n = "NA", Percentage = "NA")
    
    
     if(nrow(GAD7_Imp_Df) == 1 & nrow(GAD7_Sig_Imp_Df) == 1) {
      GAD7_Percentages<- rbind(GAD7_Imp_Df, GAD7_Sig_Imp_Df)
      GAD7_Percentages<- cbind(Improvement_Type, GAD7_Percentages)
    }  else if(nrow(GAD7_Imp_Df) == 1 & nrow(GAD7_Sig_Imp_Df) == 0) {
      GAD7_Percentages = rbind(GAD7_Imp_Df, Sig_Null)
       GAD7_Percentages<- cbind(Improvement_Type, GAD7_Percentages)
    } else if(nrow(GAD7_Imp_Df) == 0) {
      GAD7_Percentages<- data.frame(x = c("NA", "NA"), y = c("NA", "NA"))
      GAD7_Percentages<- cbind(Improvement_Type, GAD7_Percentages)
    }

     names(GAD7_Percentages)<- c( "", "Number of Cases Improved", "Percentage of Cases Improved")
    
     
    Scale_Names<- c("GAD7 Total")
    
    GAD7_M_Intake<- Scale_Report_Df %>% select(contains("First.Score")) %>% select(contains("GAD7")) %>% summarise_all(funs(round(mean(., na.rm = TRUE), digits = 2))) %>% rename_all(funs(c(Scale_Names)))
    GAD7_M_Discharge<- Scale_Report_Df %>% select(contains("Last.Score")) %>% select(contains("GAD7")) %>% summarise_all(funs(round(mean(., na.rm = TRUE), digits = 2))) %>% rename_all(funs(c(Scale_Names)))
    GAD7_M_Change<- Scale_Report_Df %>% select(contains("Change")) %>% select(contains("GAD7")) %>% summarise_all(funs(round(mean(., na.rm = TRUE), digits = 2))) %>% rename_all(funs(c(Scale_Names)))
    GAD7_Range<- c("Total Scale" = "0-30")

    
    GAD7_Descriptives<- rbind(GAD7_M_Intake, GAD7_M_Discharge, GAD7_M_Change, GAD7_Range)
    Data<- c("Mean Intake Score", "Mean Discharge Score", "Mean Change", "Range of Possible Scores")
    GAD7_Descriptives<- cbind(Data, GAD7_Descriptives)
  
```

##GAD-7

```{r,echo=FALSE,warning=FALSE,comment=NA,results='asis'}

kable(GAD7_Percentages, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T) 
```

```{r,echo=FALSE,warning=FALSE,comment=NA, fig.width = 4, fig.height = 1.9, fig.align='left'}
  
#GAD7 Graph
    
    GAD7_Reformat<- dplyr::select(Scale_Report_Df, Name, GAD7.Fullscale.First.Score, GAD7.Fullscale.Last.Score)
    GAD7_Reformat<- GAD7_Reformat %>% rename(Pre = GAD7.Fullscale.First.Score, Post = GAD7.Fullscale.Last.Score)
    GAD7_Reformat<- GAD7_Reformat %>% dplyr::filter(complete.cases(Pre, Post))

    GAD7_Reformat<- gather(GAD7_Reformat, Group, GAD7.Total.Score, Pre:Post)
    GAD7_Reformat$Group<- factor(GAD7_Reformat$Group, levels=unique(GAD7_Reformat$Group))
    
    GAD7_Plot<- ggplot(data = GAD7_Reformat, aes (x = factor(Group), y = GAD7.Total.Score, group = Name))
    GAD7_Plot<- GAD7_Plot + geom_line() + xlab("Time") + ylab("GAD-7 Total") 
    
    GAD7_Plot + scale_y_continuous(limits = c(0, 21), breaks = c(0,7,14,21)) + scale_x_discrete(expand = c(0.2, 0)) + theme_bw() + theme(panel.background = element_rect("#f1f1f1"), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=9, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=9, family = "AvantGarde", face = "bold")) 
```


##Average Change Over Treatment Period

```{r,echo=FALSE,warning=FALSE,comment=NA,results='asis'}

kable(GAD7_Descriptives, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T)

```

##Reporting Period
```{r,echo = FALSE,warning=FALSE,comment = NA, results='asis'}


if(!is.null(Periods)) {
  cat(Periods, sep = ", ")
} else if (is.null(Periods)) {
  cat("No reporting period was specified. All cases with complete GAD-7 data were used.")
}


```