---
title: "Illness Attitude Scales (IAS)"
author: "Analytics Report generated by Sentient Psychometrics"
date: "`r format(Sys.time(), '%d %B, %Y')`"
geometry: "left=2cm,right=2cm,top=1.5cm,bottom=1.2cm"
output:
  pdf_document:
    latex_engine: pdflatex
header-includes:
- \usepackage[fontsize=7.8pt]{scrextend}
- \usepackage{color}
- \usepackage{booktabs}
- \usepackage[table]{xcolor}
fontfamily: arev
always_allow_html: yes
params:
Imp_Df: 'NULL'
Sig_Imp_Df: 'NULL'
Scale_Report_Df: 'NULL'
Periods: 'NULL'
---


\begingroup\Large

\begin{center} \textbf{Information about the Illness Attitude Scales (IAS)} \end{center} 

#What it Measures: 

* Psychopathology and illness behaviour related to hypochondriasis. 

* Includes 9 subscales, which assess: **(1) Worry about Illness**, **(2) Concerns about Pain**, **(3) Health Habits**, **(4) Hypochondriacal Beliefs**, **(5) Thanatophobia (fear of death)**, **(6) Disease Phobia**, **(7) Bodily Preoccupations** (fixation on bodily symptoms), **(8) Treatment Experience** (frequency/degree of treatment seeking) and &&(9) Effect of Symptoms** (psychosocial impact of bodily symptoms). 


#What Higher Scores Mean:

* More severe psychological disturbance and maladaptive behaviour associated with health anxiety. 

* Greater likelihood of meeting criteria for Illness Anxiety Disorder or another somatoform disorder. 


#Scale Quality:

* Reviews have provided strong support for the IAS when compared to other measures of health anxiety, and this scale has higher test-retest reliability than the Whitely Index (Hedman, Lekander, Ljótsson, Lindefors, Rück et al., 2015; Höfling & Weck, 2013). 


#Scale Structure:

* 27 items

* 5-point Likert scale

* For all items (except those forming the Health Habits subscale), respondents are asked to indicate how frequently ("No" = 0; "Most of the time" = 4) each statement is currently true for them (e.g. "Do you examine your body to find whether there is something wrong?"). 

* A number of studies have failed to replicate the original 9-factor structure proposed by the scale developer. Instead, 2-factor (Hiller & Rief, 2002), 3-factor (Weck, Bleichardt & Hiller, 2009), and 4-factor (Crössman & Pauli, 2006) solutions have been proposed for use with different populations. Therefore, while individual subscales may have clinical utility, be cautious in interpreting them.

\endgroup

\newpage 

```{r, echo = FALSE, warning = FALSE, comment = NA, results = 'asis'}

    #IAS nonsig calculations 
    
    IAS_Imp_Df<-dplyr::select(Imp_Df, contains("IAS.Fullscale"))
    Worry_Illness_Imp_Df<-dplyr::select(Imp_Df, contains("IAS.Worry.Illness"))
   Concerns_Pain_Imp_Df<- dplyr::select(Imp_Df, contains("IAS.Concerns.Pain"))
    Health_Habits_Imp_Df<-dplyr::select(Imp_Df, contains("IAS.Health.Habits"))
    Hypochondriacal_Beliefs_Imp_Df<-dplyr::select(Imp_Df, contains("IAS.Hypochondriacal.Beliefs"))
    Thanatophobia_Imp_Df<- dplyr::select(Imp_Df, contains("IAS.Thanatophobia"))
    Disease_Phobia_Imp_Df<-dplyr::select(Imp_Df, contains("IAS.Disease.Phobia"))
    Bodily_Preoccupations_Imp_Df<-dplyr::select(Imp_Df, contains("IAS.Bodily.Preoccupations"))
    Treatment_Experience_Imp_Df<- dplyr::select(Imp_Df, contains("Treatment.Experience"))
    Effects_Symptoms_Imp_Df<-dplyr::select(Imp_Df, contains("IAS.Effects.Symptoms"))
    
    
    
    
    IAS_Imp_Df<-as.data.frame(gather(IAS_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))
    Worry_Illness_Imp_Df<-as.data.frame(gather(Worry_Illness_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))
   Concerns_Pain_Imp_Df<-as.data.frame(gather(Concerns_Pain_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))
    
     Health_Habits_Imp_Df<-as.data.frame(gather(Health_Habits_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))
     Hypochondriacal_Beliefs_Imp_Df<-as.data.frame(gather(Hypochondriacal_Beliefs_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))
    
     Thanatophobia_Imp_Df<-as.data.frame(gather(Thanatophobia_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))
    
     Disease_Phobia_Imp_Df<-as.data.frame(gather(Disease_Phobia_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))
    Bodily_Preoccupations_Imp_Df<-as.data.frame(gather(Bodily_Preoccupations_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))
    Treatment_Experience_Imp_Df<-as.data.frame(gather(Treatment_Experience_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))
    
     Effects_Symptoms_Imp_Df<-as.data.frame(gather(Effects_Symptoms_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))

    
    #IAS sig calculations
    
    
    IAS_Sig_Imp_Df<-dplyr::select(Sig_Imp_Df, contains("IAS.Fullscale"))
    Worry_Illness_Sig_Imp_Df<-dplyr::select(Sig_Imp_Df, contains("IAS.Worry.Illness"))
   Concerns_Pain_Sig_Imp_Df<- dplyr::select(Sig_Imp_Df, contains("IAS.Concerns.Pain"))
    Health_Habits_Sig_Imp_Df<-dplyr::select(Sig_Imp_Df, contains("IAS.Health.Habits"))
    Hypochondriacal_Beliefs_Sig_Imp_Df<-dplyr::select(Sig_Imp_Df, contains("IAS.Hypochondriacal.Beliefs"))
    Thanatophobia_Sig_Imp_Df<- dplyr::select(Sig_Imp_Df, contains("IAS.Thanatophobia"))
    Disease_Phobia_Sig_Imp_Df<-dplyr::select(Sig_Imp_Df, contains("IAS.Disease.Phobia"))
    Bodily_Preoccupations_Sig_Imp_Df<-dplyr::select(Sig_Imp_Df, contains("IAS.Bodily.Preoccupations"))
    Treatment_Experience_Sig_Imp_Df<- dplyr::select(Sig_Imp_Df, contains("IAS.Treatment.Experience"))
    Effects_Symptoms_Sig_Imp_Df<-dplyr::select(Sig_Imp_Df, contains("IAS.Effects.Symptoms"))

    
    
      IAS_Sig_Imp_Df<-as.data.frame(gather(IAS_Sig_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))
    Worry_Illness_Sig_Imp_Df<-as.data.frame(gather(Worry_Illness_Sig_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))
   Concerns_Pain_Sig_Imp_Df<-as.data.frame(gather(Concerns_Pain_Sig_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))
    
     Health_Habits_Sig_Imp_Df<-as.data.frame(gather(Health_Habits_Sig_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))
     Hypochondriacal_Beliefs_Sig_Imp_Df<-as.data.frame(gather(Hypochondriacal_Beliefs_Sig_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))
    Thanatophobia_Sig_Imp_Df<-as.data.frame(gather(Thanatophobia_Sig_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))
    
     Disease_Phobia_Sig_Imp_Df<-as.data.frame(gather(Disease_Phobia_Sig_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))
    Bodily_Preoccupations_Sig_Imp_Df<-as.data.frame(gather(Bodily_Preoccupations_Sig_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))
    Treatment_Experience_Sig_Imp_Df<-as.data.frame(gather(Treatment_Experience_Sig_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))
    
     Effects_Symptoms_Sig_Imp_Df<-as.data.frame(gather(Effects_Symptoms_Sig_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))

    Improvement_Type<- c("Improvement", "Statistically Reliable Improvement")
    
    Sig_Null<- data.frame(n = "NA", Percentage = "NA")
    
    
    if(nrow(IAS_Imp_Df) == 1 & nrow(IAS_Sig_Imp_Df) == 1) {
      IAS_Percentages<- rbind(IAS_Imp_Df, IAS_Sig_Imp_Df)
      IAS_Percentages<- cbind(Improvement_Type, IAS_Percentages)
    }  else if(nrow(IAS_Imp_Df) == 1 & nrow(IAS_Sig_Imp_Df) == 0) {
      IAS_Percentages = rbind(IAS_Imp_Df, Sig_Null)
       IAS_Percentages<- cbind(Improvement_Type, IAS_Percentages)
    } else if(nrow(IAS_Imp_Df) == 0) {
      IAS_Percentages<- data.frame(x = c("NA", "NA"), y = c("NA", "NA"))
      IAS_Percentages<- cbind(Improvement_Type, IAS_Percentages)
    }

     names(IAS_Percentages)<- c( "", "Number of Cases Improved", "Percentage of Cases Improved")


       
       if(nrow(Worry_Illness_Imp_Df) == 1 & nrow(Worry_Illness_Sig_Imp_Df) == 1) {
      Worry_Illness_Percentages<- rbind(Worry_Illness_Imp_Df, Worry_Illness_Sig_Imp_Df)
      Worry_Illness_Percentages<- cbind(Improvement_Type, Worry_Illness_Percentages)
    }  else if(nrow(Worry_Illness_Imp_Df) == 1 & nrow(Worry_Illness_Sig_Imp_Df) == 0) {
      Worry_Illness_Percentages = rbind(Worry_Illness_Imp_Df, Sig_Null)
       Worry_Illness_Percentages<- cbind(Improvement_Type, Worry_Illness_Percentages)
    } else if(nrow(Worry_Illness_Imp_Df) == 0) {
      Worry_Illness_Percentages<- data.frame(x = c("NA", "NA"), y = c("NA", "NA"))
      Worry_Illness_Percentages<- cbind(Improvement_Type, Worry_Illness_Percentages)
    }

     names(Worry_Illness_Percentages)<- c( "", "Number of Cases Improved", "Percentage of Cases Improved")


    
       if(nrow(Concerns_Pain_Imp_Df) == 1 & nrow(Concerns_Pain_Sig_Imp_Df) == 1) {
     Concerns_Pain_Percentages<- rbind(Concerns_Pain_Imp_Df,Concerns_Pain_Sig_Imp_Df)
     Concerns_Pain_Percentages<- cbind(Improvement_Type,Concerns_Pain_Percentages)
    }  else if(nrow(Concerns_Pain_Imp_Df) == 1 & nrow(Concerns_Pain_Sig_Imp_Df) == 0) {
     Concerns_Pain_Percentages = rbind(Concerns_Pain_Imp_Df, Sig_Null)
      Concerns_Pain_Percentages<- cbind(Improvement_Type,Concerns_Pain_Percentages)
    } else if(nrow(Concerns_Pain_Imp_Df) == 0) {
     Concerns_Pain_Percentages<- data.frame(x = c("NA", "NA"), y = c("NA", "NA"))
     Concerns_Pain_Percentages<- cbind(Improvement_Type,Concerns_Pain_Percentages)
    }

     names(Concerns_Pain_Percentages)<- c( "", "Number of Cases Improved", "Percentage of Cases Improved")
    
    
    
      if(nrow(Health_Habits_Imp_Df) == 1 & nrow(Health_Habits_Sig_Imp_Df) == 1) {
      Health_Habits_Percentages<- rbind(Health_Habits_Imp_Df, Health_Habits_Sig_Imp_Df)
      Health_Habits_Percentages<- cbind(Improvement_Type, Health_Habits_Percentages)
    }  else if(nrow(Health_Habits_Imp_Df) == 1 & nrow(Health_Habits_Sig_Imp_Df) == 0) {
      Health_Habits_Percentages = rbind(Health_Habits_Imp_Df, Sig_Null)
       Health_Habits_Percentages<- cbind(Improvement_Type, Health_Habits_Percentages)
    } else if(nrow(Health_Habits_Imp_Df) == 0) {
      Health_Habits_Percentages<- data.frame(x = c("NA", "NA"), y = c("NA", "NA"))
      Health_Habits_Percentages<- cbind(Improvement_Type, Health_Habits_Percentages)
    }

     names(Health_Habits_Percentages)<- c( "", "Number of Cases Improved", "Percentage of Cases Improved")

    
  
    
      if(nrow(Hypochondriacal_Beliefs_Imp_Df) == 1 & nrow(Hypochondriacal_Beliefs_Sig_Imp_Df) == 1) {
      Hypochondriacal_Beliefs_Percentages<- rbind(Hypochondriacal_Beliefs_Imp_Df, Hypochondriacal_Beliefs_Sig_Imp_Df)
      Hypochondriacal_Beliefs_Percentages<- cbind(Improvement_Type, Hypochondriacal_Beliefs_Percentages)
    }  else if(nrow(Hypochondriacal_Beliefs_Imp_Df) == 1 & nrow(Hypochondriacal_Beliefs_Sig_Imp_Df) == 0) {
      Hypochondriacal_Beliefs_Percentages = rbind(Hypochondriacal_Beliefs_Imp_Df, Sig_Null)
       Hypochondriacal_Beliefs_Percentages<- cbind(Improvement_Type, Hypochondriacal_Beliefs_Percentages)
    } else if(nrow(Hypochondriacal_Beliefs_Imp_Df) == 0) {
      Hypochondriacal_Beliefs_Percentages<- data.frame(x = c("NA", "NA"), y = c("NA", "NA"))
      Hypochondriacal_Beliefs_Percentages<- cbind(Improvement_Type, Hypochondriacal_Beliefs_Percentages)
    }

     names(Hypochondriacal_Beliefs_Percentages)<- c( "", "Number of Cases Improved", "Percentage of Cases Improved")


    
     if(nrow(Thanatophobia_Imp_Df) == 1 & nrow(Thanatophobia_Sig_Imp_Df) == 1) {
      Thanatophobia_Percentages<- rbind(Thanatophobia_Imp_Df, Thanatophobia_Sig_Imp_Df)
      Thanatophobia_Percentages<- cbind(Improvement_Type, Thanatophobia_Percentages)
    }  else if(nrow(Thanatophobia_Imp_Df) == 1 & nrow(Thanatophobia_Sig_Imp_Df) == 0) {
      Thanatophobia_Percentages = rbind(Thanatophobia_Imp_Df, Sig_Null)
       Thanatophobia_Percentages<- cbind(Improvement_Type, Thanatophobia_Percentages)
    } else if(nrow(Thanatophobia_Imp_Df) == 0) {
      Thanatophobia_Percentages<- data.frame(x = c("NA", "NA"), y = c("NA", "NA"))
      Thanatophobia_Percentages<- cbind(Improvement_Type, Thanatophobia_Percentages)
    }

     names(Thanatophobia_Percentages)<- c( "", "Number of Cases Improved", "Percentage of Cases Improved")


     
     if(nrow(Disease_Phobia_Imp_Df) == 1 & nrow(Disease_Phobia_Sig_Imp_Df) == 1) {
      Disease_Phobia_Percentages<- rbind(Disease_Phobia_Imp_Df, Disease_Phobia_Sig_Imp_Df)
      Disease_Phobia_Percentages<- cbind(Improvement_Type, Disease_Phobia_Percentages)
    }  else if(nrow(Disease_Phobia_Imp_Df) == 1 & nrow(Disease_Phobia_Sig_Imp_Df) == 0) {
      Disease_Phobia_Percentages = rbind(Disease_Phobia_Imp_Df, Sig_Null)
       Disease_Phobia_Percentages<- cbind(Improvement_Type, Disease_Phobia_Percentages)
    } else if(nrow(Disease_Phobia_Imp_Df) == 0) {
      Disease_Phobia_Percentages<- data.frame(x = c("NA", "NA"), y = c("NA", "NA"))
      Disease_Phobia_Percentages<- cbind(Improvement_Type, Disease_Phobia_Percentages)
    }

     names(Disease_Phobia_Percentages)<- c( "", "Number of Cases Improved", "Percentage of Cases Improved")
   
    
    
      if(nrow(Bodily_Preoccupations_Imp_Df) == 1 & nrow(Bodily_Preoccupations_Sig_Imp_Df) == 1) {
      Bodily_Preoccupations_Percentages<- rbind(Bodily_Preoccupations_Imp_Df, Bodily_Preoccupations_Sig_Imp_Df)
      Bodily_Preoccupations_Percentages<- cbind(Improvement_Type, Bodily_Preoccupations_Percentages)
    }  else if(nrow(Bodily_Preoccupations_Imp_Df) == 1 & nrow(Bodily_Preoccupations_Sig_Imp_Df) == 0) {
      Bodily_Preoccupations_Percentages = rbind(Bodily_Preoccupations_Imp_Df, Sig_Null)
       Bodily_Preoccupations_Percentages<- cbind(Improvement_Type, Bodily_Preoccupations_Percentages)
    } else if(nrow(Bodily_Preoccupations_Imp_Df) == 0) {
      Bodily_Preoccupations_Percentages<- data.frame(x = c("NA", "NA"), y = c("NA", "NA"))
      Bodily_Preoccupations_Percentages<- cbind(Improvement_Type, Bodily_Preoccupations_Percentages)
    }

     names(Bodily_Preoccupations_Percentages)<- c( "", "Number of Cases Improved", "Percentage of Cases Improved")


     
      if(nrow(Treatment_Experience_Imp_Df) == 1 & nrow(Treatment_Experience_Sig_Imp_Df) == 1) {
      Treatment_Experience_Percentages<- rbind(Treatment_Experience_Imp_Df, Treatment_Experience_Sig_Imp_Df)
      Treatment_Experience_Percentages<- cbind(Improvement_Type, Treatment_Experience_Percentages)
    }  else if(nrow(Treatment_Experience_Imp_Df) == 1 & nrow(Treatment_Experience_Sig_Imp_Df) == 0) {
      Treatment_Experience_Percentages = rbind(Treatment_Experience_Imp_Df, Sig_Null)
       Treatment_Experience_Percentages<- cbind(Improvement_Type, Treatment_Experience_Percentages)
    } else if(nrow(Treatment_Experience_Imp_Df) == 0) {
      Treatment_Experience_Percentages<- data.frame(x = c("NA", "NA"), y = c("NA", "NA"))
      Treatment_Experience_Percentages<- cbind(Improvement_Type, Treatment_Experience_Percentages)
    }

     names(Treatment_Experience_Percentages)<- c( "", "Number of Cases Improved", "Percentage of Cases Improved")
    
    
   
    if(nrow(Effects_Symptoms_Imp_Df) == 1 & nrow(Effects_Symptoms_Sig_Imp_Df) == 1) {
      Effects_Symptoms_Percentages<- rbind(Effects_Symptoms_Imp_Df, Effects_Symptoms_Sig_Imp_Df)
      Effects_Symptoms_Percentages<- cbind(Improvement_Type, Effects_Symptoms_Percentages)
    }  else if(nrow(Effects_Symptoms_Imp_Df) == 1 & nrow(Effects_Symptoms_Sig_Imp_Df) == 0) {
      Effects_Symptoms_Percentages = rbind(Effects_Symptoms_Imp_Df, Sig_Null)
       Effects_Symptoms_Percentages<- cbind(Improvement_Type, Effects_Symptoms_Percentages)
    } else if(nrow(Effects_Symptoms_Imp_Df) == 0) {
      Effects_Symptoms_Percentages<- data.frame(x = c("NA", "NA"), y = c("NA", "NA"))
      Effects_Symptoms_Percentages<- cbind(Improvement_Type, Effects_Symptoms_Percentages)
    }

     names(Effects_Symptoms_Percentages)<- c( "", "Number of Cases Improved", "Percentage of Cases Improved")


      Scale_Names<- c("IAS Total", "Illness Worry", "Pain Concerns", "Health Habits", "Hypochondriacal Beliefs", "Thanatophobia", "Disease Phobia", "Bodily Preoccupations", "Treatment Experience", "Symptoms Effects")
    
    IAS_M_Intake<- Scale_Report_Df %>% select(contains("First.Score")) %>% select(contains("IAS")) %>% summarise_all(funs(round(mean(., na.rm = TRUE), digits = 2))) %>% rename_all(funs(c(Scale_Names)))
    IAS_M_Discharge<- Scale_Report_Df %>% select(contains("Last.Score")) %>% select(contains("IAS")) %>% summarise_all(funs(round(mean(., na.rm = TRUE), digits = 2))) %>% rename_all(funs(c(Scale_Names)))
    IAS_M_Change<- Scale_Report_Df %>% select(contains("Change")) %>% select(contains("IAS")) %>% summarise_all(funs(round(mean(., na.rm = TRUE), digits = 2))) %>% rename_all(funs(c(Scale_Names)))
    IAS_Range<- c("Total Scale" = "0-108","Illness Worry" = "0-12",  "Pain Concerns" = "0-12",  "Health Habits" = "0-12", "Hypochondriacal Beliefs" = "0-12", "Thanatophobia" = "0-12", "Disease Phobia" = "0-12", "Bodily Preoccupations" = "0-12", "Treatment Experience" = "0-12", "Symptoms Effects" = "0-12")

    
    IAS_Descriptives<- rbind(IAS_M_Intake, IAS_M_Discharge, IAS_M_Change, IAS_Range)
    Data<- c("Mean Intake Score", "Mean Discharge Score", "Mean Change", "Range of Possible Scores")
    IAS_Descriptives<- cbind(Data, IAS_Descriptives) 
  
```

##IAS Total Scale

```{r,echo=FALSE,warning=FALSE,comment=NA,results='asis'}

kable(IAS_Percentages, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T) 
```

```{r,echo=FALSE,warning=FALSE,comment=NA, fig.width = 4, fig.height = 1.9, fig.align='left'}

    IAS_Reformat<- dplyr::select(Scale_Report_Df, Name, IAS.Fullscale.First.Score, IAS.Fullscale.Last.Score)
    IAS_Reformat<- IAS_Reformat %>% rename(Pre = IAS.Fullscale.First.Score, Post = IAS.Fullscale.Last.Score)
    IAS_Reformat<- IAS_Reformat %>% dplyr::filter(complete.cases(Pre, Post))

    IAS_Reformat<- gather(IAS_Reformat, Group, IAS.Total.Score, Pre:Post)
    IAS_Reformat$Group<- factor(IAS_Reformat$Group, levels=unique(IAS_Reformat$Group))
    
    IAS_Plot<- ggplot(data = IAS_Reformat, aes (x = factor(Group), y = IAS.Total.Score, group = Name))
    IAS_Plot<- IAS_Plot + geom_line() + xlab("Time") + ylab("IAS Total") 
    
    IAS_Plot + scale_y_continuous(limits = c(0, 108), breaks = c(0,36,72,108)) + scale_x_discrete(expand = c(0.2, 0)) + theme_bw() + theme(panel.background = element_rect("#f1f1f1"), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=9, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=9, family = "AvantGarde", face = "bold")) 
```

##Worry About Illness Subscale

```{r,echo=FALSE,warning=FALSE,comment=NA,results='asis'}

kable(Worry_Illness_Percentages, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T)
```

```{r,echo=FALSE,warning=FALSE,comment=NA, fig.width = 4, fig.height = 1.9, fig.align='left'}
IAS_Worry_Illness_Reformat<- dplyr::select(Scale_Report_Df, Name, IAS.Worry.Illness.First.Score, IAS.Worry.Illness.Last.Score)
    IAS_Worry_Illness_Reformat<- IAS_Worry_Illness_Reformat %>% rename(Pre = IAS.Worry.Illness.First.Score, Post = IAS.Worry.Illness.Last.Score)
    IAS_Worry_Illness_Reformat<- IAS_Worry_Illness_Reformat %>% dplyr::filter(complete.cases(Pre, Post))

    IAS_Worry_Illness_Reformat<- gather(IAS_Worry_Illness_Reformat, Group, IAS.Worry.Illness.Score, Pre:Post)
    IAS_Worry_Illness_Reformat$Group<- factor(IAS_Worry_Illness_Reformat$Group, levels=unique(IAS_Worry_Illness_Reformat$Group))
    
    IAS_Worry_Illness_Plot<- ggplot(data = IAS_Worry_Illness_Reformat, aes(x = factor(Group), y = IAS.Worry.Illness.Score, group = Name))
    IAS_Worry_Illness_Plot<- IAS_Worry_Illness_Plot + geom_line() + xlab("Time") + ylab("Illness Worry") 
    
    IAS_Worry_Illness_Plot + scale_y_continuous(limits = c(0, 12), breaks = c(0,4,8,12)) + scale_x_discrete(expand = c(0.2, 0)) + theme_bw() + theme(panel.background = element_rect("#f1f1f1"), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=9, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=9, family = "AvantGarde", face = "bold")) 
    

```

##Concerns About Pain Subscale 

```{r,echo=FALSE,warning=FALSE,comment=NA,results='asis'}

kable(Concerns_Pain_Percentages, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T)

```

```{r,echo=FALSE,warning=FALSE,comment=NA,results='asis', fig.width = 4, fig.height = 1.9, fig.align='left'}
IAS_Concerns_Pain_Reformat<- dplyr::select(Scale_Report_Df, Name, IAS.Concerns.Pain.First.Score, IAS.Concerns.Pain.Last.Score)
    IAS_Concerns_Pain_Reformat<- IAS_Concerns_Pain_Reformat %>% rename(Pre = IAS.Concerns.Pain.First.Score, Post = IAS.Concerns.Pain.Last.Score)
    IAS_Concerns_Pain_Reformat<- IAS_Concerns_Pain_Reformat %>% dplyr::filter(complete.cases(Pre, Post))

    IAS_Concerns_Pain_Reformat<- gather(IAS_Concerns_Pain_Reformat, Group, IAS.Concerns.Pain.Score, Pre:Post)
    IAS_Concerns_Pain_Reformat$Group<- factor(IAS_Concerns_Pain_Reformat$Group, levels=unique(IAS_Concerns_Pain_Reformat$Group))
    
    IAS_Concerns_Pain_Plot<- ggplot(data = IAS_Concerns_Pain_Reformat, aes (x = factor(Group), y = IAS.Concerns.Pain.Score, group = Name))
    IAS_Concerns_Pain_Plot<- IAS_Concerns_Pain_Plot + geom_line() + xlab("Time") + ylab("Pain Concerns") 
    
    IAS_Concerns_Pain_Plot + scale_y_continuous(limits = c(0, 12), breaks = c(0, 4, 8, 12)) + scale_x_discrete(expand = c(0.2, 0)) + theme_bw() + theme(panel.background = element_rect("#f1f1f1"), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=9, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=9, family = "AvantGarde", face = "bold")) 
```

\newpage

##Health Habits Subscale

```{r,echo=FALSE,warning=FALSE,comment=NA,results='asis'}

kable(Health_Habits_Percentages, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T)
```

```{r,echo=FALSE,warning=FALSE,comment=NA, fig.width = 4, fig.height = 1.9, fig.align='left'}
IAS_Health_Habits_Reformat<- dplyr::select(Scale_Report_Df, Name, IAS.Health.Habits.First.Score, IAS.Health.Habits.Last.Score)
    IAS_Health_Habits_Reformat<- IAS_Health_Habits_Reformat %>% rename(Pre = IAS.Health.Habits.First.Score, Post = IAS.Health.Habits.Last.Score)
    IAS_Health_Habits_Reformat<- IAS_Health_Habits_Reformat %>% dplyr::filter(complete.cases(Pre, Post))

    IAS_Health_Habits_Reformat<- gather(IAS_Health_Habits_Reformat, Group, IAS.Health.Habits.Score, Pre:Post)
    IAS_Health_Habits_Reformat$Group<- factor(IAS_Health_Habits_Reformat$Group, levels=unique(IAS_Health_Habits_Reformat$Group))
    
    IAS_Health_Habits_Plot<- ggplot(data = IAS_Health_Habits_Reformat, aes(x = factor(Group), y = IAS.Health.Habits.Score, group = Name))
    IAS_Health_Habits_Plot<- IAS_Health_Habits_Plot + geom_line() + xlab("Time") + ylab("Health Habits") 
    
    IAS_Health_Habits_Plot + scale_y_continuous(limits = c(0, 12), breaks = c(0, 4, 8, 12)) + scale_x_discrete(expand = c(0.2, 0)) + theme_bw() + theme(panel.background = element_rect("#f1f1f1"), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=9, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=9, family = "AvantGarde", face = "bold")) 
    

```

##Hypochondriacal Beliefs Subscale

```{r,echo=FALSE,warning=FALSE,comment=NA,results='asis'}

kable(Hypochondriacal_Beliefs_Percentages, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T)
```

```{r,echo=FALSE,warning=FALSE,comment=NA, fig.width = 4, fig.height = 1.9, fig.align='left'}
IAS_Hypochondriacal_Beliefs_Reformat<- dplyr::select(Scale_Report_Df, Name, IAS.Hypochondriacal.Beliefs.First.Score, IAS.Hypochondriacal.Beliefs.Last.Score)
    IAS_Hypochondriacal_Beliefs_Reformat<- IAS_Hypochondriacal_Beliefs_Reformat %>% rename(Pre = IAS.Hypochondriacal.Beliefs.First.Score, Post = IAS.Hypochondriacal.Beliefs.Last.Score)
    IAS_Hypochondriacal_Beliefs_Reformat<- IAS_Hypochondriacal_Beliefs_Reformat %>% dplyr::filter(complete.cases(Pre, Post))

    IAS_Hypochondriacal_Beliefs_Reformat<- gather(IAS_Hypochondriacal_Beliefs_Reformat, Group, IAS.Hypochondriacal.Beliefs.Score, Pre:Post)
    IAS_Hypochondriacal_Beliefs_Reformat$Group<- factor(IAS_Hypochondriacal_Beliefs_Reformat$Group, levels=unique(IAS_Hypochondriacal_Beliefs_Reformat$Group))
    
    IAS_Hypochondriacal_Beliefs_Plot<- ggplot(data = IAS_Hypochondriacal_Beliefs_Reformat, aes(x = factor(Group), y = IAS.Hypochondriacal.Beliefs.Score, group = Name))
    IAS_Hypochondriacal_Beliefs_Plot<- IAS_Hypochondriacal_Beliefs_Plot + geom_line() + xlab("Time") + ylab("Hypochondriacal Beliefs") 
    
    IAS_Hypochondriacal_Beliefs_Plot + scale_y_continuous(limits = c(0, 12), breaks = c(0, 4, 8, 12)) + scale_x_discrete(expand = c(0.2, 0)) + theme_bw() + theme(panel.background = element_rect("#f1f1f1"), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=9, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=9, family = "AvantGarde", face = "bold")) 
    

```


##Thanatophobia Subscale

```{r,echo=FALSE,warning=FALSE,comment=NA,results='asis'}

kable(Thanatophobia_Percentages, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T)
```

```{r,echo=FALSE,warning=FALSE,comment=NA, fig.width = 4, fig.height = 1.9, fig.align='left'}
IAS_Thanatophobia_Reformat<- dplyr::select(Scale_Report_Df, Name, IAS.Thanatophobia.First.Score, IAS.Thanatophobia.Last.Score)
    IAS_Thanatophobia_Reformat<- IAS_Thanatophobia_Reformat %>% rename(Pre = IAS.Thanatophobia.First.Score, Post = IAS.Thanatophobia.Last.Score)
    IAS_Thanatophobia_Reformat<- IAS_Thanatophobia_Reformat %>% dplyr::filter(complete.cases(Pre, Post))

    IAS_Thanatophobia_Reformat<- gather(IAS_Thanatophobia_Reformat, Group, IAS.Thanatophobia.Score, Pre:Post)
    IAS_Thanatophobia_Reformat$Group<- factor(IAS_Thanatophobia_Reformat$Group, levels=unique(IAS_Thanatophobia_Reformat$Group))
    
    IAS_Thanatophobia_Plot<- ggplot(data = IAS_Thanatophobia_Reformat, aes(x = factor(Group), y = IAS.Thanatophobia.Score, group = Name))
    IAS_Thanatophobia_Plot<- IAS_Thanatophobia_Plot + geom_line() + xlab("Time") + ylab("Thanatophobia") 
    
    IAS_Thanatophobia_Plot + scale_y_continuous(limits = c(0, 12), breaks = c(0, 4, 8, 12)) + scale_x_discrete(expand = c(0.2, 0)) + theme_bw() + theme(panel.background = element_rect("#f1f1f1"), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=9, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=9, family = "AvantGarde", face = "bold")) 
    

```

\newpage

##Disease Phobia Subscale

```{r,echo=FALSE,warning=FALSE,comment=NA,results='asis'}

kable(Disease_Phobia_Percentages, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T)
```

```{r,echo=FALSE,warning=FALSE,comment=NA, fig.width = 4, fig.height = 1.9, fig.align='left'}
IAS_Disease_Phobia_Reformat<- dplyr::select(Scale_Report_Df, Name, IAS.Disease.Phobia.First.Score, IAS.Disease.Phobia.Last.Score)
    IAS_Disease_Phobia_Reformat<- IAS_Disease_Phobia_Reformat %>% rename(Pre = IAS.Disease.Phobia.First.Score, Post = IAS.Disease.Phobia.Last.Score)
    IAS_Disease_Phobia_Reformat<- IAS_Disease_Phobia_Reformat %>% dplyr::filter(complete.cases(Pre, Post))

    IAS_Disease_Phobia_Reformat<- gather(IAS_Disease_Phobia_Reformat, Group, IAS.Disease.Phobia.Score, Pre:Post)
    IAS_Disease_Phobia_Reformat$Group<- factor(IAS_Disease_Phobia_Reformat$Group, levels=unique(IAS_Disease_Phobia_Reformat$Group))
    
    IAS_Disease_Phobia_Plot<- ggplot(data = IAS_Disease_Phobia_Reformat, aes(x = factor(Group), y = IAS.Disease.Phobia.Score, group = Name))
    IAS_Disease_Phobia_Plot<- IAS_Disease_Phobia_Plot + geom_line() + xlab("Time") + ylab("Disease Phobia") 
    
    IAS_Disease_Phobia_Plot + scale_y_continuous(limits = c(0, 12), breaks = c(0, 4, 8, 12)) + scale_x_discrete(expand = c(0.2, 0)) + theme_bw() + theme(panel.background = element_rect("#f1f1f1"), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=9, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=9, family = "AvantGarde", face = "bold")) 
    

```


##Bodily Preoccupations Subscale

```{r,echo=FALSE,warning=FALSE,comment=NA,results='asis'}

kable(Bodily_Preoccupations_Percentages, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T)
```

```{r,echo=FALSE,warning=FALSE,comment=NA, fig.width = 4, fig.height = 1.9, fig.align='left'}
    IAS_Bodily_Preoccupations_Reformat<- dplyr::select(Scale_Report_Df, Name, IAS.Bodily.Preoccupations.First.Score, IAS.Bodily.Preoccupations.Last.Score)
    IAS_Bodily_Preoccupations_Reformat<- IAS_Bodily_Preoccupations_Reformat %>% rename(Pre = IAS.Bodily.Preoccupations.First.Score, Post = IAS.Bodily.Preoccupations.Last.Score)
    IAS_Bodily_Preoccupations_Reformat<- IAS_Bodily_Preoccupations_Reformat %>% dplyr::filter(complete.cases(Pre, Post))

    IAS_Bodily_Preoccupations_Reformat<- gather(IAS_Bodily_Preoccupations_Reformat, Group, IAS.Bodily.Preoccupations.Score, Pre:Post)
    IAS_Bodily_Preoccupations_Reformat$Group<- factor(IAS_Bodily_Preoccupations_Reformat$Group, levels=unique(IAS_Bodily_Preoccupations_Reformat$Group))
    
    IAS_Bodily_Preoccupations_Plot<- ggplot(data = IAS_Bodily_Preoccupations_Reformat, aes(x = factor(Group), y = IAS.Bodily.Preoccupations.Score, group = Name))
    IAS_Bodily_Preoccupations_Plot<- IAS_Bodily_Preoccupations_Plot + geom_line() + xlab("Time") + ylab("Bodily Preoccupations") 
    
    IAS_Bodily_Preoccupations_Plot + scale_y_continuous(limits = c(0, 12), breaks = c(0, 4, 8, 12)) + scale_x_discrete(expand = c(0.2, 0)) + theme_bw() + theme(panel.background = element_rect("#f1f1f1"), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=9, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=9, family = "AvantGarde", face = "bold")) 
    

```



##Treatment Experience Subscale

```{r,echo=FALSE,warning=FALSE,comment=NA,results='asis'}

kable(Treatment_Experience_Percentages, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T)
```

```{r,echo=FALSE,warning=FALSE,comment=NA, fig.width = 4, fig.height = 1.9, fig.align='left'}
IAS_Treatment_Experience_Reformat<- dplyr::select(Scale_Report_Df, Name, IAS.Treatment.Experience.First.Score, IAS.Treatment.Experience.Last.Score)
    IAS_Treatment_Experience_Reformat<- IAS_Treatment_Experience_Reformat %>% rename(Pre = IAS.Treatment.Experience.First.Score, Post = IAS.Treatment.Experience.Last.Score)
    IAS_Treatment_Experience_Reformat<- IAS_Treatment_Experience_Reformat %>% dplyr::filter(complete.cases(Pre, Post))

    IAS_Treatment_Experience_Reformat<- gather(IAS_Treatment_Experience_Reformat, Group, IAS.Treatment.Experience.Score, Pre:Post)
    IAS_Treatment_Experience_Reformat$Group<- factor(IAS_Treatment_Experience_Reformat$Group, levels=unique(IAS_Treatment_Experience_Reformat$Group))
    
    IAS_Treatment_Experience_Plot<- ggplot(data = IAS_Treatment_Experience_Reformat, aes(x = factor(Group), y = IAS.Treatment.Experience.Score, group = Name))
    IAS_Treatment_Experience_Plot<- IAS_Treatment_Experience_Plot + geom_line() + xlab("Time") + ylab("Treatment Experience") 
    
    IAS_Treatment_Experience_Plot + scale_y_continuous(limits = c(0, 12), breaks = c(0, 4, 8, 12)) + scale_x_discrete(expand = c(0.2, 0)) + theme_bw() + theme(panel.background = element_rect("#f1f1f1"), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=9, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=9, family = "AvantGarde", face = "bold")) 
    

```

\newpage

##Effect of Symptoms Subscale

```{r,echo=FALSE,warning=FALSE,comment=NA,results='asis'}

kable(Effects_Symptoms_Percentages, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T)
```

```{r,echo=FALSE,warning=FALSE,comment=NA, fig.width = 4, fig.height = 1.9, fig.align='left'}
IAS_Effects_Symptoms_Reformat<- dplyr::select(Scale_Report_Df, Name, IAS.Effects.Symptoms.First.Score, IAS.Effects.Symptoms.Last.Score)
    IAS_Effects_Symptoms_Reformat<- IAS_Effects_Symptoms_Reformat %>% rename(Pre = IAS.Effects.Symptoms.First.Score, Post = IAS.Effects.Symptoms.Last.Score)
    IAS_Effects_Symptoms_Reformat<- IAS_Effects_Symptoms_Reformat %>% dplyr::filter(complete.cases(Pre, Post))

    IAS_Effects_Symptoms_Reformat<- gather(IAS_Effects_Symptoms_Reformat, Group, IAS.Effects.Symptoms.Score, Pre:Post)
    IAS_Effects_Symptoms_Reformat$Group<- factor(IAS_Effects_Symptoms_Reformat$Group, levels=unique(IAS_Effects_Symptoms_Reformat$Group))
    
    IAS_Effects_Symptoms_Plot<- ggplot(data = IAS_Effects_Symptoms_Reformat, aes(x = factor(Group), y = IAS.Effects.Symptoms.Score, group = Name))
    IAS_Effects_Symptoms_Plot<- IAS_Effects_Symptoms_Plot + geom_line() + xlab("Time") + ylab("Self Worth") 
    
    IAS_Effects_Symptoms_Plot + scale_y_continuous(limits = c(0, 12), breaks = c(0, 4, 8, 12)) + scale_x_discrete(expand = c(0.2, 0)) + theme_bw() + theme(panel.background = element_rect("#f1f1f1"), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=9, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=9, family = "AvantGarde", face = "bold")) 
    

```


##Average Change Over Treatment Period

####See last page.

```{r,echo=FALSE,warning=FALSE,comment=NA,results='asis'}


cat('\n#', "Reporting Period", '\n')
cat('\n')

if(!is.null(Periods)) {
  cat(Periods, sep = ", ")
} else if (is.null(Periods)) {
  cat("No reporting period was specified. All cases with complete IAS data were used.")
}


IAS_Descriptives_Tab<- kable(IAS_Descriptives, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F, latex_options = "striped") %>% row_spec(0, bold = T) %>% kable_styling(latex_options="scale_down")

landscape(IAS_Descriptives_Tab)

```
