---
title: "Insomnia Severity Index (ISI)"
author: "Analytics Report generated by Sentient Psychometrics"
date: "`r format(Sys.time(), '%d %B, %Y')`"
geometry: "left=2cm,right=2cm,top=1.5cm,bottom=1.2cm"
output:
  pdf_document:
    latex_engine: pdflatex
header-includes:
- \usepackage[fontsize=7.8pt]{scrextend}
- \usepackage{color}
- \usepackage{booktabs}
- \usepackage[table]{xcolor}
fontfamily: arev
always_allow_html: yes
params:
Imp_Df: 'NULL'
Sig_Imp_Df: 'NULL'
Scale_Report_Df: 'NULL'
Periods: 'NULL'
---


\begingroup\Large

\begin{center} \textbf{Information About the Insomnia Severity Index (ISI)} \end{center} 

#What it Measures: 

* The perceived severity of insomnia symptoms as well as the extent to which those symptoms cause distress and daytime impairment.

* Scale content aligns in part with DSM-IV criteria for insomnia. 

#What Higher Scores Mean:

* Insomnia symptoms that are more severe, distressing and resultant in daytime impairment. 

* A score of **15** is recommended to indicate the likely presence of clinical insomnia (with moderate severity). However, a more recent study conducted by the original scale developer recommended a cut-off score of **10** for detecting insomnia cases in a large community sample (Morin, Belleville, Bélanger & Ivers, 2011). 


#Scale Quality:

* The ISI was reviewed as being "essential" for use in treatment efficacy and effectiveness studies (Buyusse, Ancoli-Israel, Edinger, Lichstein & Morin, 2005). 


#Scale Structure:

* 7 items 

* 5-point Likert scale

* Respondents rate the severity of problems with falling asleep, staying asleep and waking up too early (i.e. 0 = "none", 4 = "very"). For the remaining questions, respndents answer questions about how much each statement applies to them (e.g. "How satisfied/dissatisfied are you with your current sleeping pattern?; 0 = "very satisfied"; 4 = "very dissatisfied"). 

* There has been limited research examining the factor structure of the ISI. Studies have supported a single factor structure (Sierra, Guillén-Serrano & Santos-Iglesias, 2008), a single-factor structure with reduced items (Dragioti, Wiklund, Alföldi & Gerdle, 2015), and a 3-factor structure (Fernandez-Mendoza et al., 2012). 

\endgroup

\newpage

```{r, echo = FALSE, warning = FALSE, comment = NA, results = 'asis'}

    #ISI nonsig calculations 
    
    ISI_Imp_Df<-dplyr::select(Imp_Df, contains("ISI.Fullscale"))

    
    ISI_Imp_Df<-as.data.frame(gather(ISI_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))

    
    
    #ISI sig calculations
    
    
    ISI_Sig_Imp_Df<-dplyr::select(Sig_Imp_Df, contains("ISI.Fullscale"))

    
    ISI_Sig_Imp_Df<-as.data.frame(gather(ISI_Sig_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))

    
    Improvement_Type<- c("Improvement", "Statistically Reliable Improvement")
    
    Sig_Null<- data.frame(n = "NA", Percentage = "NA")
    
    
     if(nrow(ISI_Imp_Df) == 1 & nrow(ISI_Sig_Imp_Df) == 1) {
      ISI_Percentages<- rbind(ISI_Imp_Df, ISI_Sig_Imp_Df)
      ISI_Percentages<- cbind(Improvement_Type, ISI_Percentages)
    }  else if(nrow(ISI_Imp_Df) == 1 & nrow(ISI_Sig_Imp_Df) == 0) {
      ISI_Percentages = rbind(ISI_Imp_Df, Sig_Null)
       ISI_Percentages<- cbind(Improvement_Type, ISI_Percentages)
    } else if(nrow(ISI_Imp_Df) == 0) {
      ISI_Percentages<- data.frame(x = c("NA", "NA"), y = c("NA", "NA"))
      ISI_Percentages<- cbind(Improvement_Type, ISI_Percentages)
    }

     names(ISI_Percentages)<- c( "", "Number of Cases Improved", "Percentage of Cases Improved")
    
     
    Scale_Names<- c("ISI Total")
    
    ISI_M_Intake<- Scale_Report_Df %>% select(contains("First.Score")) %>% select(contains("ISI")) %>% summarise_all(funs(round(mean(., na.rm = TRUE), digits = 2))) %>% rename_all(funs(c(Scale_Names)))
    ISI_M_Discharge<- Scale_Report_Df %>% select(contains("Last.Score")) %>% select(contains("ISI")) %>% summarise_all(funs(round(mean(., na.rm = TRUE), digits = 2))) %>% rename_all(funs(c(Scale_Names)))
    ISI_M_Change<- Scale_Report_Df %>% select(contains("Change")) %>% select(contains("ISI")) %>% summarise_all(funs(round(mean(., na.rm = TRUE), digits = 2))) %>% rename_all(funs(c(Scale_Names)))
    ISI_Range<- c("Total Scale" = "0-30")

    
    ISI_Descriptives<- rbind(ISI_M_Intake, ISI_M_Discharge, ISI_M_Change, ISI_Range)
    Data<- c("Mean Intake Score", "Mean Discharge Score", "Mean Change", "Range of Possible Scores")
    ISI_Descriptives<- cbind(Data, ISI_Descriptives)
  
```

##ISI

```{r,echo=FALSE,warning=FALSE,comment=NA,results='asis'}

kable(ISI_Percentages, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T) 
```

```{r,echo=FALSE,warning=FALSE,comment=NA, fig.width = 4, fig.height = 1.9, fig.align='left'}
  
#ISI Graph
    
    ISI_Reformat<- dplyr::select(Scale_Report_Df, Name, ISI.Fullscale.First.Score, ISI.Fullscale.Last.Score)
    ISI_Reformat<- ISI_Reformat %>% rename(Pre = ISI.Fullscale.First.Score, Post = ISI.Fullscale.Last.Score)
    ISI_Reformat<- ISI_Reformat %>% dplyr::filter(complete.cases(Pre, Post))

    ISI_Reformat<- gather(ISI_Reformat, Group, ISI.Total.Score, Pre:Post)
    ISI_Reformat$Group<- factor(ISI_Reformat$Group, levels=unique(ISI_Reformat$Group))
    
    ISI_Plot<- ggplot(data = ISI_Reformat, aes (x = factor(Group), y = ISI.Total.Score, group = Name))
    ISI_Plot<- ISI_Plot + geom_line() + xlab("Time") + ylab("ISI Total") 
    
    ISI_Plot + scale_y_continuous(limits = c(0, 28), breaks = c(0,7,14,21,28)) + scale_x_discrete(expand = c(0.2, 0)) + theme_bw() + theme(panel.background = element_rect("#f1f1f1"), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=9, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=9, family = "AvantGarde", face = "bold")) 
```


##Average Change Over Treatment Period

```{r,echo=FALSE,warning=FALSE,comment=NA,results='asis'}

kable(ISI_Descriptives, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T) %>% column_spec(1, width = "6cm")

```

##Reporting Period
```{r,echo = FALSE,warning=FALSE,comment = NA, results='asis'}


if(!is.null(Periods)) {
  cat(Periods, sep = ", ")
} else if (is.null(Periods)) {
  cat("No reporting period was specified. All cases with complete ISI data were used.")
}


```