---
title: "Panic Disorder Severity Scale-Self-Report (PDSS-SR)"
author: "Analytics Report generated by Sentient Psychometrics"
date: "`r format(Sys.time(), '%d %B, %Y')`"
geometry: "left=2cm,right=2cm,top=1.5cm,bottom=1.2cm"
output:
  pdf_document:
    latex_engine: pdflatex
header-includes:
- \usepackage[fontsize=7.8pt]{scrextend}
- \usepackage{color}
- \usepackage{booktabs}
- \usepackage[table]{xcolor}
fontfamily: arev
always_allow_html: yes
params:
Imp_Df: 'NULL'
Sig_Imp_Df: 'NULL'
Scale_Report_Df: 'NULL'
Periods: 'NULL'
---



\begingroup\Large

\begin{center} \textbf{Information About the Panic Disorder Severity Scale (PDSS)} \end{center} 

#What it Measures: 

* The severity of Panic Disorder symptoms during the past month.


* Five items assess each core symptom of Panic Disorder with our without Agoraphobia, as outlined in the Diagnostic & Statistical Manual of Mental Disorders, 4th Edition (DSM-IV). Two items assess occupational and social impairment.


#What Higher Scores Mean:

* More severe Panic Disorder symptomatology.


#Scale Quality:

* The PDSS-SR has well-established psychometric properties and is one of the most widely-used self-report measures of panic symptom severity (Elkins, Pincus & Comer, 2014; Keough, Hoge, Pollack & Shear, 2012). 


#Scale Structure:

* Contains 7 items.


* A 5-Point Likert scale captures the frequency of panic attacks and limited symptom episodes (LSEs), distress caused by panic and LSEs, anticipatory anxiety, agorophobic fear/avoidance, panic-related sensation fear/avoidance and social impairment.


* Psychometric research has provided support for a single factor structure (Shear et al., 1997). 

\endgroup
\newpage

```{r, echo = FALSE, warning = FALSE, comment = NA, results = 'asis'}

    #PDSS-SR nonsig calculations 
    
    PDSS_Imp_Df<-dplyr::select(Imp_Df, contains("PDSS.Fullscale"))

    
    PDSS_Imp_Df<-as.data.frame(gather(PDSS_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))

    
    
    #PDSS-SR sig calculations
    
    
    PDSS_Sig_Imp_Df<-dplyr::select(Sig_Imp_Df, contains("PDSS.Fullscale"))

    
    PDSS_Sig_Imp_Df<-as.data.frame(gather(PDSS_Sig_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))

    
    Improvement_Type<- c("Improvement", "Statistically Reliable Improvement")
    
    Sig_Null<- data.frame(n = "NA", Percentage = "NA")
    
    
     if(nrow(PDSS_Imp_Df) == 1 & nrow(PDSS_Sig_Imp_Df) == 1) {
      PDSS_Percentages<- rbind(PDSS_Imp_Df, PDSS_Sig_Imp_Df)
      PDSS_Percentages<- cbind(Improvement_Type, PDSS_Percentages)
    }  else if(nrow(PDSS_Imp_Df) == 1 & nrow(PDSS_Sig_Imp_Df) == 0) {
      PDSS_Percentages = rbind(PDSS_Imp_Df, Sig_Null)
       PDSS_Percentages<- cbind(Improvement_Type, PDSS_Percentages)
    } else if(nrow(PDSS_Imp_Df) == 0) {
      PDSS_Percentages<- data.frame(x = c("NA", "NA"), y = c("NA", "NA"))
      PDSS_Percentages<- cbind(Improvement_Type, PDSS_Percentages)
    }

     names(PDSS_Percentages)<- c( "", "Number of Cases Improved", "Percentage of Cases Improved")
    
     
    Scale_Names<- c("PDSS Total")
    
    PDSS_M_Intake<- Scale_Report_Df %>% select(contains("First.Score")) %>% select(contains("PDSS")) %>% summarise_all(funs(round(mean(., na.rm = TRUE), digits = 2))) %>% rename_all(funs(c(Scale_Names)))
    PDSS_M_Discharge<- Scale_Report_Df %>% select(contains("Last.Score")) %>% select(contains("PDSS")) %>% summarise_all(funs(round(mean(., na.rm = TRUE), digits = 2))) %>% rename_all(funs(c(Scale_Names)))
    PDSS_M_Change<- Scale_Report_Df %>% select(contains("Change")) %>% select(contains("PDSS")) %>% summarise_all(funs(round(mean(., na.rm = TRUE), digits = 2))) %>% rename_all(funs(c(Scale_Names)))
    PDSS_Range<- c("Total Scale" = "0-28")

    
    PDSS_Descriptives<- rbind(PDSS_M_Intake, PDSS_M_Discharge, PDSS_M_Change, PDSS_Range)
    Data<- c("Mean Intake Score", "Mean Discharge Score", "Mean Change", "Range of Possible Scores")
    PDSS_Descriptives<- cbind(Data, PDSS_Descriptives)
  
```

##PDSS-SR 

```{r,echo=FALSE,warning=FALSE,comment=NA,results='asis'}

kable(PDSS_Percentages, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T) 
```

```{r,echo=FALSE,warning=FALSE,comment=NA, fig.width = 4, fig.height = 1.9, fig.align='left'}
  
#PDSS Graph
    
    PDSS_Reformat<- dplyr::select(Scale_Report_Df, Name, PDSS.Fullscale.First.Score, PDSS.Fullscale.Last.Score)
    PDSS_Reformat<- PDSS_Reformat %>% rename(Pre = PDSS.Fullscale.First.Score, Post = PDSS.Fullscale.Last.Score)
    PDSS_Reformat<- PDSS_Reformat %>% dplyr::filter(complete.cases(Pre, Post))

    PDSS_Reformat<- gather(PDSS_Reformat, Group, PDSS.Total.Score, Pre:Post)
    PDSS_Reformat$Group<- factor(PDSS_Reformat$Group, levels=unique(PDSS_Reformat$Group))
    
    PDSS_Plot<- ggplot(data = PDSS_Reformat, aes (x = factor(Group), y = PDSS.Total.Score, group = Name))
    PDSS_Plot<- PDSS_Plot + geom_line() + xlab("Time") + ylab("PDSS-SR Total") 
    
    PDSS_Plot + scale_y_continuous(limits = c(0, 28), breaks = c(0,7,14,21,28)) + scale_x_discrete(expand = c(0.2, 0)) + theme_bw() + theme(panel.background = element_rect("#f1f1f1"), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=9, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=9, family = "AvantGarde", face = "bold")) 
```


##Average Change Over Treatment Period

```{r,echo=FALSE,warning=FALSE,comment=NA,results='asis'}

kable(PDSS_Descriptives, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T) %>% column_spec(1, width = "6cm")

```

##Reporting Period
```{r,echo = FALSE,warning=FALSE,comment = NA, results='asis'}


if(!is.null(Periods)) {
  cat(Periods, sep = ", ")
} else if (is.null(Periods)) {
  cat("No reporting period was specified. All cases with complete PDSS-SR data were used.")
}


```