---
title: "Patient Health Questionnaire-9 (PHQ-9)"
author: "Analytics Report generated by Sentient Psychometrics"
date: "`r format(Sys.time(), '%d %B, %Y')`"
geometry: "left=2cm,right=2cm,top=1.5cm,bottom=1.2cm"
output:
  pdf_document:
    latex_engine: pdflatex
header-includes:
- \usepackage[fontsize=7.8pt]{scrextend}
- \usepackage{color}
- \usepackage{booktabs}
- \usepackage[table]{xcolor}
fontfamily: arev
always_allow_html: yes
params:
Imp_Df: 'NULL'
Sig_Imp_Df: 'NULL'
Scale_Report_Df: 'NULL'
Periods: 'NULL'
---


\begingroup\Large

\begin{center} \textbf{Information About the Patient Health Quesionnaire-9 (PHQ-9)} \end{center} 

#What it Measures: 

* Symptoms of Depression over the previous 2 weeks.


* Symptoms of Depression are based on the 9 criteria for depressive disorders outlined in the Diagnostic and Statistical Manual of Psychological Disorders, 4th Edition (DSM-IV).


* Symptoms assessed include anhedonia, low mood, sleep difficulties, appetite change, self-deprecating thoughts, concentration problems, changes in psychomotor speed, and thoughts of death/self-harm.


* An additional tenth item assesses the degree to which depressive symptoms have resulted in functional impairment. 


#What Higher Scores Mean:

* More severe depressive symptomatology over the previous 2 weeks.


* Greater likelihood of meeting criteria for Major Depressive Disorder.  


* A cut-off score of **10** has been used to make a provisional diagnosis of depression across different settings (for meta analyses, see Mitchell, Yadegarfar, Gill & Stubbs, 2016; Moriarty, Gilbody, McMillan & Manea, 2015).


#Scale Quality:

* The PHQ-9 is the most commonly-used screening measure for depression in primary care and has well-established psychometric properties (Moriarty, Gilbody, McMillan & Manea, 2015). 


#Scale Structure:

* 9 items.


* 4-point Likert scale.


* Respondents indicate how frequently (0 = "Not at all"; 3 = "Nearly every day") they have been bothered by the problems listed in each item (e.g. "Little interest or pleasure in doing things"). 

\endgroup

\newpage

```{r, echo = FALSE, warning = FALSE, comment = NA, results = 'asis'}

    #PHQ-9 nonsig calculations 
    
    PHQ9_Imp_Df<-dplyr::select(Imp_Df, contains("PHQ9.Fullscale"))

    
    PHQ9_Imp_Df<-as.data.frame(gather(PHQ9_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))

    
    
    #PHQ-9 sig calculations
    
    
    PHQ9_Sig_Imp_Df<-dplyr::select(Sig_Imp_Df, contains("PHQ9.Fullscale"))

    
    PHQ9_Sig_Imp_Df<-as.data.frame(gather(PHQ9_Sig_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))

    
    Improvement_Type<- c("Improvement", "Statistically Reliable Improvement")
    
    Sig_Null<- data.frame(n = "NA", Percentage = "NA")
    
    
     if(nrow(PHQ9_Imp_Df) == 1 & nrow(PHQ9_Sig_Imp_Df) == 1) {
      PHQ9_Percentages<- rbind(PHQ9_Imp_Df, PHQ9_Sig_Imp_Df)
      PHQ9_Percentages<- cbind(Improvement_Type, PHQ9_Percentages)
    }  else if(nrow(PHQ9_Imp_Df) == 1 & nrow(PHQ9_Sig_Imp_Df) == 0) {
      PHQ9_Percentages = rbind(PHQ9_Imp_Df, Sig_Null)
       PHQ9_Percentages<- cbind(Improvement_Type, PHQ9_Percentages)
    } else if(nrow(PHQ9_Imp_Df) == 0) {
      PHQ9_Percentages<- data.frame(x = c("NA", "NA"), y = c("NA", "NA"))
      PHQ9_Percentages<- cbind(Improvement_Type, PHQ9_Percentages)
    }

     names(PHQ9_Percentages)<- c( "", "Number of Cases Improved", "Percentage of Cases Improved")
    
     
    Scale_Names<- c("PHQ9 Total")
    
    PHQ9_M_Intake<- Scale_Report_Df %>% select(contains("First.Score")) %>% select(contains("PHQ9")) %>% summarise_all(funs(round(mean(., na.rm = TRUE), digits = 2))) %>% rename_all(funs(c(Scale_Names)))
    PHQ9_M_Discharge<- Scale_Report_Df %>% select(contains("Last.Score")) %>% select(contains("PHQ9")) %>% summarise_all(funs(round(mean(., na.rm = TRUE), digits = 2))) %>% rename_all(funs(c(Scale_Names)))
    PHQ9_M_Change<- Scale_Report_Df %>% select(contains("Change")) %>% select(contains("PHQ9")) %>% summarise_all(funs(round(mean(., na.rm = TRUE), digits = 2))) %>% rename_all(funs(c(Scale_Names)))
    PHQ9_Range<- c("Total Scale" = "0-30")

    
    PHQ9_Descriptives<- rbind(PHQ9_M_Intake, PHQ9_M_Discharge, PHQ9_M_Change, PHQ9_Range)
    Data<- c("Mean Intake Score", "Mean Discharge Score", "Mean Change", "Range of Possible Scores")
    PHQ9_Descriptives<- cbind(Data, PHQ9_Descriptives)
  
```

##PHQ-9 

```{r,echo=FALSE,warning=FALSE,comment=NA,results='asis'}

kable(PHQ9_Percentages, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T) 
```

```{r,echo=FALSE,warning=FALSE,comment=NA, fig.width = 4, fig.height = 1.9, fig.align='left'}
  
#PHQ9 Graph
    
    PHQ9_Reformat<- dplyr::select(Scale_Report_Df, Name, PHQ9.Fullscale.First.Score, PHQ9.Fullscale.Last.Score)
    PHQ9_Reformat<- PHQ9_Reformat %>% rename(Pre = PHQ9.Fullscale.First.Score, Post = PHQ9.Fullscale.Last.Score)
    PHQ9_Reformat<- PHQ9_Reformat %>% dplyr::filter(complete.cases(Pre, Post))

    PHQ9_Reformat<- gather(PHQ9_Reformat, Group, PHQ9.Total.Score, Pre:Post)
    PHQ9_Reformat$Group<- factor(PHQ9_Reformat$Group, levels=unique(PHQ9_Reformat$Group))
    
    PHQ9_Plot<- ggplot(data = PHQ9_Reformat, aes (x = factor(Group), y = PHQ9.Total.Score, group = Name))
    PHQ9_Plot<- PHQ9_Plot + geom_line() + xlab("Time") + ylab("PHQ-9 Total") 
    
    PHQ9_Plot + scale_y_continuous(limits = c(0, 27), breaks = c(0,9,18,27)) + scale_x_discrete(expand = c(0.2, 0)) + theme_bw() + theme(panel.background = element_rect("#f1f1f1"), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=9, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=9, family = "AvantGarde", face = "bold")) 
```


##Average Change Over Treatment Period

```{r,echo=FALSE,warning=FALSE,comment=NA,results='asis'}

kable(PHQ9_Descriptives, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T) %>% column_spec(1, width = "6cm")

```

##Reporting Period
```{r,echo = FALSE,warning=FALSE,comment = NA, results='asis'}


if(!is.null(Periods)) {
  cat(Periods, sep = ", ")
} else if (is.null(Periods)) {
  cat("No reporting period was specified. All cases with complete PHQ-9 data were used.")
}


```