---
title: "Pain Self-Perception Scale (PSPS)"
author: "Analytics Report generated by Sentient Psychometrics"
date: "`r format(Sys.time(), '%d %B, %Y')`"
geometry: "left=2cm,right=2cm,top=1.5cm,bottom=1.2cm"
output:
  pdf_document:
    latex_engine: pdflatex
header-includes:
- \usepackage[fontsize=7.8pt]{scrextend}
- \usepackage{color}
- \usepackage{booktabs}
- \usepackage[table]{xcolor}
fontfamily: arev
always_allow_html: yes
params:
Imp_Df: 'NULL'
Sig_Imp_Df: 'NULL'
Scale_Report_Df: 'NULL'
Periods: 'NULL'
---


\begingroup\Large

\begin{center} \textbf{Information About the Pain Self-Perception Scale (PSPS)} \end{center} 

#What it Measures: 

* Mental defeat associated with the experience of pain.


#What Higher Scores Mean:

* A more severe degree of perceived mental defeat linked to pain. 


#Scale Quality:

* At least 2 studies have conducted psychometric evaluations of the PSPS (Garcia-Campayo, Rodero, del Hoyo, Alda & Gili, 2010; Tang, Salkovskis & Hanna, 2007). 

* The original psychometric evaluation of the PSPS revealed high internal consistency and test-retest reliability (Tang, Salkovskis & Hanna, 2007). 


#Scale Structure:

* 24 items.

* 5-point Likert scale.

* Respondents indicate how much (0 = "not at all/never"; 4 = "very strongly") each item applied to their experience during a recent episode of intense pain (e.g. "I felt down and out"). 

* The PSPS has a 1-factor solution (Tang, Salkovskis & Hanna, 2007). 

\endgroup
\newpage

```{r, echo = FALSE, warning = FALSE, comment = NA, results = 'asis'}

    #PSPS nonsig calculations 
    
    PSPS_Imp_Df<-dplyr::select(Imp_Df, contains("PSPS.Fullscale"))

    
    PSPS_Imp_Df<-as.data.frame(gather(PSPS_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))

    
    
    #PSPS sig calculations
    
    
    PSPS_Sig_Imp_Df<-dplyr::select(Sig_Imp_Df, contains("PSPS.Fullscale"))

    
    PSPS_Sig_Imp_Df<-as.data.frame(gather(PSPS_Sig_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))

    
    Improvement_Type<- c("Improvement", "Statistically Reliable Improvement")
    
    Sig_Null<- data.frame(n = "NA", Percentage = "NA")
    
    
     if(nrow(PSPS_Imp_Df) == 1 & nrow(PSPS_Sig_Imp_Df) == 1) {
      PSPS_Percentages<- rbind(PSPS_Imp_Df, PSPS_Sig_Imp_Df)
      PSPS_Percentages<- cbind(Improvement_Type, PSPS_Percentages)
    }  else if(nrow(PSPS_Imp_Df) == 1 & nrow(PSPS_Sig_Imp_Df) == 0) {
      PSPS_Percentages = rbind(PSPS_Imp_Df, Sig_Null)
       PSPS_Percentages<- cbind(Improvement_Type, PSPS_Percentages)
    } else if(nrow(PSPS_Imp_Df) == 0) {
      PSPS_Percentages<- data.frame(x = c("NA", "NA"), y = c("NA", "NA"))
      PSPS_Percentages<- cbind(Improvement_Type, PSPS_Percentages)
    }

     names(PSPS_Percentages)<- c( "", "Number of Cases Improved", "Percentage of Cases Improved")
    
     
    Scale_Names<- c("PSPS Total")
    
    PSPS_M_Intake<- Scale_Report_Df %>% select(contains("First.Score")) %>% select(contains("PSPS")) %>% summarise_all(funs(round(mean(., na.rm = TRUE), digits = 2))) %>% rename_all(funs(c(Scale_Names)))
    PSPS_M_Discharge<- Scale_Report_Df %>% select(contains("Last.Score")) %>% select(contains("PSPS")) %>% summarise_all(funs(round(mean(., na.rm = TRUE), digits = 2))) %>% rename_all(funs(c(Scale_Names)))
    PSPS_M_Change<- Scale_Report_Df %>% select(contains("Change")) %>% select(contains("PSPS")) %>% summarise_all(funs(round(mean(., na.rm = TRUE), digits = 2))) %>% rename_all(funs(c(Scale_Names)))
    PSPS_Range<- c("Total Scale" = "0-96")

    
    PSPS_Descriptives<- rbind(PSPS_M_Intake, PSPS_M_Discharge, PSPS_M_Change, PSPS_Range)
    Data<- c("Mean Intake Score", "Mean Discharge Score", "Mean Change", "Range of Possible Scores")
    PSPS_Descriptives<- cbind(Data, PSPS_Descriptives)
  
```

##PSPS 

```{r,echo=FALSE,warning=FALSE,comment=NA,results='asis'}

kable(PSPS_Percentages, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T) 
```

```{r,echo=FALSE,warning=FALSE,comment=NA, fig.width = 4, fig.height = 1.9, fig.align='left'}
  
#PSPS Graph
    
    PSPS_Reformat<- dplyr::select(Scale_Report_Df, Name, PSPS.Fullscale.First.Score, PSPS.Fullscale.Last.Score)
    PSPS_Reformat<- PSPS_Reformat %>% rename(Pre = PSPS.Fullscale.First.Score, Post = PSPS.Fullscale.Last.Score)
    PSPS_Reformat<- PSPS_Reformat %>% dplyr::filter(complete.cases(Pre, Post))

    PSPS_Reformat<- gather(PSPS_Reformat, Group, PSPS.Total.Score, Pre:Post)
    PSPS_Reformat$Group<- factor(PSPS_Reformat$Group, levels=unique(PSPS_Reformat$Group))
    
    PSPS_Plot<- ggplot(data = PSPS_Reformat, aes (x = factor(Group), y = PSPS.Total.Score, group = Name))
    PSPS_Plot<- PSPS_Plot + geom_line() + xlab("Time") + ylab("PSPS Total") 
    
    PSPS_Plot + scale_y_continuous(limits = c(0, 96), breaks = c(0,24,48,72,96)) + scale_x_discrete(expand = c(0.2, 0)) + theme_bw() + theme(panel.background = element_rect("#f1f1f1"), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=9, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=9, family = "AvantGarde", face = "bold")) 
```


##Average Change Over Treatment Period

```{r,echo=FALSE,warning=FALSE,comment=NA,results='asis'}

kable(PSPS_Descriptives, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T) 

```

##Reporting Period
```{r,echo = FALSE,warning=FALSE,comment = NA, results='asis'}


if(!is.null(Periods)) {
  cat(Periods, sep = ", ")
} else if (is.null(Periods)) {
  cat("No reporting period was specified. All cases with complete PSPS data were used.")
}


```