---
title: "Severity of Dependence Scale (SDS)"
author: "Analytics Report generated by Sentient Psychometrics"
date: "`r format(Sys.time(), '%d %B, %Y')`"
geometry: "left=2cm,right=2cm,top=1.5cm,bottom=1.2cm"
output:
  pdf_document:
    latex_engine: pdflatex
header-includes:
- \usepackage[fontsize=7.8pt]{scrextend}
- \usepackage{color}
- \usepackage{booktabs}
- \usepackage[table]{xcolor}
fontfamily: arev
always_allow_html: yes
params:
Imp_Df: 'NULL'
Sig_Imp_Df: 'NULL'
Scale_Report_Df: 'NULL'
Periods: 'NULL'
---


\begingroup\Large

\begin{center} \textbf{Information About the Severity of Dependence Scale (SDS)} \end{center} 

#What it Measures: 

* Degree of drug dependence in the past month. Longer timeframes for drug dependence (e.g. 12 months or 3 months) have also been employed clinically and for research purposes. 

#What Higher Scores Mean:

* More severe drug dependence.

* The SDS is **not** a diagnostic instrument.

* Researchers have recommended cut-off scores for different types of substance use. If a patient scores on or above the recommended cut-off score, he or she is more likely to meet critera for a substance use disorder. 


#Scale Quality:

* The SDS is one of the most widely-employed and well-researched instruments for assessing severity of substance use (for a review see Piontek, Kraus & Klempova, 2008). 

#Scale Structure:

* Contains 5 items. 

* 4-point Likert scale.

* Respondents are asked about the controllability of their use and associated worry. Questions are based on frequency (e.g. "a little") and difficulty (e.g."quite difficult"). 

* Items have been shown to load on a single factor (Gossop, Darke, Griffiths, Hando, Powis et al., 1995). 

\endgroup
\newpage

```{r, echo = FALSE, warning = FALSE, comment = NA, results = 'asis'}

    #SDS nonsig calculations 
    
    SDS_Imp_Df<-dplyr::select(Imp_Df, contains("SDS.Fullscale"))

    
    SDS_Imp_Df<-as.data.frame(gather(SDS_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))

    
    
    #SDS sig calculations
    
    
    SDS_Sig_Imp_Df<-dplyr::select(Sig_Imp_Df, contains("SDS.Fullscale"))

    
    SDS_Sig_Imp_Df<-as.data.frame(gather(SDS_Sig_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))

    
    Improvement_Type<- c("Improvement", "Statistically Reliable Improvement")
    
    Sig_Null<- data.frame(n = "NA", Percentage = "NA")
    
    
     if(nrow(SDS_Imp_Df) == 1 & nrow(SDS_Sig_Imp_Df) == 1) {
      SDS_Percentages<- rbind(SDS_Imp_Df, SDS_Sig_Imp_Df)
      SDS_Percentages<- cbind(Improvement_Type, SDS_Percentages)
    }  else if(nrow(SDS_Imp_Df) == 1 & nrow(SDS_Sig_Imp_Df) == 0) {
      SDS_Percentages = rbind(SDS_Imp_Df, Sig_Null)
       SDS_Percentages<- cbind(Improvement_Type, SDS_Percentages)
    } else if(nrow(SDS_Imp_Df) == 0) {
      SDS_Percentages<- data.frame(x = c("NA", "NA"), y = c("NA", "NA"))
      SDS_Percentages<- cbind(Improvement_Type, SDS_Percentages)
    }

     names(SDS_Percentages)<- c( "", "Number of Cases Improved", "Percentage of Cases Improved")
    
     
    Scale_Names<- c("SDS Total")
    
    SDS_M_Intake<- Scale_Report_Df %>% select(contains("First.Score")) %>% select(contains("SDS")) %>% summarise_all(funs(round(mean(., na.rm = TRUE), digits = 2))) %>% rename_all(funs(c(Scale_Names)))
    SDS_M_Discharge<- Scale_Report_Df %>% select(contains("Last.Score")) %>% select(contains("SDS")) %>% summarise_all(funs(round(mean(., na.rm = TRUE), digits = 2))) %>% rename_all(funs(c(Scale_Names)))
    SDS_M_Change<- Scale_Report_Df %>% select(contains("Change")) %>% select(contains("SDS")) %>% summarise_all(funs(round(mean(., na.rm = TRUE), digits = 2))) %>% rename_all(funs(c(Scale_Names)))
    SDS_Range<- c("Total Scale" = "0-15")

    
    SDS_Descriptives<- rbind(SDS_M_Intake, SDS_M_Discharge, SDS_M_Change, SDS_Range)
    Data<- c("Mean Intake Score", "Mean Discharge Score", "Mean Change", "Range of Possible Scores")
    SDS_Descriptives<- cbind(Data, SDS_Descriptives)
  
```

##SDS

```{r,echo=FALSE,warning=FALSE,comment=NA,results='asis'}

kable(SDS_Percentages, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T) 
```

```{r,echo=FALSE,warning=FALSE,comment=NA, fig.width = 4, fig.height = 1.9, fig.align='left'}
  
#SDS Graph
    
    SDS_Reformat<- dplyr::select(Scale_Report_Df, Name, SDS.Fullscale.First.Score, SDS.Fullscale.Last.Score)
    SDS_Reformat<- SDS_Reformat %>% rename(Pre = SDS.Fullscale.First.Score, Post = SDS.Fullscale.Last.Score)
    SDS_Reformat<- SDS_Reformat %>% dplyr::filter(complete.cases(Pre, Post))

    SDS_Reformat<- gather(SDS_Reformat, Group, SDS.Total.Score, Pre:Post)
    SDS_Reformat$Group<- factor(SDS_Reformat$Group, levels=unique(SDS_Reformat$Group))
    
    SDS_Plot<- ggplot(data = SDS_Reformat, aes (x = factor(Group), y = SDS.Total.Score, group = Name))
    SDS_Plot<- SDS_Plot + geom_line() + xlab("Time") + ylab("SDS Total") 
    
    SDS_Plot + scale_y_continuous(limits = c(0, 15), breaks = c(0,3,6,9,12,15)) + scale_x_discrete(expand = c(0.2, 0)) + theme_bw() + theme(panel.background = element_rect("#f1f1f1"), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=9, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=9, family = "AvantGarde", face = "bold")) 
```


##Average Change Over Treatment Period

```{r,echo=FALSE,warning=FALSE,comment=NA,results='asis'}

kable(SDS_Descriptives, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T) 

```

##Reporting Period
```{r,echo = FALSE,warning=FALSE,comment = NA, results='asis'}


if(!is.null(Periods)) {
  cat(Periods, sep = ", ")
} else if (is.null(Periods)) {
  cat("No reporting period was specified. All cases with complete SDS data were used.")
}


```