---
title: "Somatic Symptom Disorder - B Criteria Scale (SSD-12)"
author: "Analytics Report generated by Sentient Psychometrics"
date: "`r format(Sys.time(), '%d %B, %Y')`"
geometry: "left=2cm,right=2cm,top=1.5cm,bottom=1.2cm"
output:
  pdf_document:
    latex_engine: pdflatex
header-includes:
- \usepackage[fontsize=7.8pt]{scrextend}
- \usepackage{color}
- \usepackage{booktabs}
- \usepackage[table]{xcolor}
fontfamily: arev
always_allow_html: yes
params:
Imp_Df: 'NULL'
Sig_Imp_Df: 'NULL'
Scale_Report_Df: 'NULL'
Periods: 'NULL'
---


\begingroup\Large

\begin{center} \textbf{Somatic Symptom Disorder - B Criteria Scale (SSD-12)} \end{center} 

#What it Measures: 

* Criterion B symptoms of Somatic Symptom Disorder, as outlined in the Diagnostic and Statistical Manual of Mental Disorders (DSM-5) (i.e. excessive and disproportionate thoughts, feelings and behaviours relating to distressing somatic symptoms). 

#What Higher Scores Mean:

* Greater psychological burden of somatic symptoms/complaints.

* Greater likelihood of meeting criteria for Somatic Symptom Disorder

#Scale Quality:

* At least four investigations, including a large-scale population study, suggest that the SSD-12 has strong psychometric properties 
(Barsky, 2015; Toussaint, Löwe, Brähler & Jordan, 2017; Toussaint, Murray, Voigt, Herzog, Gierk, Kroenke, Rief, Henningsen & Löwe, 2016;
Toussaint, Riedl, Kehrer, Schneider, Löwer & Linde, 2017).


#Scale Structure:

* Research has supported a general factor structure (Toussaint, Löwe, Brähler & Jordan, 2017; Toussaint, Murray, Voigt, Herzog, Gierk, Kroenke, Rief, Henningsen & Löwe, 2016;Toussaint, Riedl, Kehrer, Schneider, Löwer & Linde, 2017). 

\endgroup
\newpage

```{r, echo = FALSE, warning = FALSE, comment = NA, results = 'asis'}

    #SSD-12 nonsig calculations 
    
    SSD12_Imp_Df<-dplyr::select(Imp_Df, contains("SSD12.Fullscale"))

    
    SSD12_Imp_Df<-as.data.frame(gather(SSD12_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))

    
    
    #SSD-12 sig calculations
    
    
    SSD12_Sig_Imp_Df<-dplyr::select(Sig_Imp_Df, contains("SSD12.Fullscale"))

    
    SSD12_Sig_Imp_Df<-as.data.frame(gather(SSD12_Sig_Imp_Df, "Outcome", "Value") %>% na.omit() %>% count(Outcome,Value) %>% mutate(Percentage = paste0(round(100 * n/sum(n), 0), "%"))) %>% dplyr::filter(Value == "Yes") %>% dplyr::select(-c(Outcome,Value))

    
    Improvement_Type<- c("Improvement", "Statistically Reliable Improvement")
    
    Sig_Null<- data.frame(n = "NA", Percentage = "NA")
    
    
     if(nrow(SSD12_Imp_Df) == 1 & nrow(SSD12_Sig_Imp_Df) == 1) {
      SSD12_Percentages<- rbind(SSD12_Imp_Df, SSD12_Sig_Imp_Df)
      SSD12_Percentages<- cbind(Improvement_Type, SSD12_Percentages)
    }  else if(nrow(SSD12_Imp_Df) == 1 & nrow(SSD12_Sig_Imp_Df) == 0) {
      SSD12_Percentages = rbind(SSD12_Imp_Df, Sig_Null)
       SSD12_Percentages<- cbind(Improvement_Type, SSD12_Percentages)
    } else if(nrow(SSD12_Imp_Df) == 0) {
      SSD12_Percentages<- data.frame(x = c("NA", "NA"), y = c("NA", "NA"))
      SSD12_Percentages<- cbind(Improvement_Type, SSD12_Percentages)
    }

     names(SSD12_Percentages)<- c( "", "Number of Cases Improved", "Percentage of Cases Improved")
    
     
    Scale_Names<- c("SSD-12 Total")
    
    SSD12_M_Intake<- Scale_Report_Df %>% select(contains("First.Score")) %>% select(contains("SSD12")) %>% summarise_all(funs(round(mean(., na.rm = TRUE), digits = 2))) %>% rename_all(funs(c(Scale_Names)))
    SSD12_M_Discharge<- Scale_Report_Df %>% select(contains("Last.Score")) %>% select(contains("SSD12")) %>% summarise_all(funs(round(mean(., na.rm = TRUE), digits = 2))) %>% rename_all(funs(c(Scale_Names)))
    SSD12_M_Change<- Scale_Report_Df %>% select(contains("Change")) %>% select(contains("SSD12")) %>% summarise_all(funs(round(mean(., na.rm = TRUE), digits = 2))) %>% rename_all(funs(c(Scale_Names)))
    SSD12_Range<- c("Total Scale" = "0-30")

    
    SSD12_Descriptives<- rbind(SSD12_M_Intake, SSD12_M_Discharge, SSD12_M_Change, SSD12_Range)
    Data<- c("Mean Intake Score", "Mean Discharge Score", "Mean Change", "Range of Possible Scores")
    SSD12_Descriptives<- cbind(Data, SSD12_Descriptives)
  
```

##SSD-12

```{r,echo=FALSE,warning=FALSE,comment=NA,results='asis'}

kable(SSD12_Percentages, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T) 
```

```{r,echo=FALSE,warning=FALSE,comment=NA, fig.width = 4, fig.height = 1.9, fig.align='left'}
  
#SSD12 Graph
    
    SSD12_Reformat<- dplyr::select(Scale_Report_Df, Name, SSD12.Fullscale.First.Score, SSD12.Fullscale.Last.Score)
    SSD12_Reformat<- SSD12_Reformat %>% rename(Pre = SSD12.Fullscale.First.Score, Post = SSD12.Fullscale.Last.Score)
    SSD12_Reformat<- SSD12_Reformat %>% dplyr::filter(complete.cases(Pre, Post))

    SSD12_Reformat<- gather(SSD12_Reformat, Group, SSD12.Total.Score, Pre:Post)
    SSD12_Reformat$Group<- factor(SSD12_Reformat$Group, levels=unique(SSD12_Reformat$Group))
    
    SSD12_Plot<- ggplot(data = SSD12_Reformat, aes (x = factor(Group), y = SSD12.Total.Score, group = Name))
    SSD12_Plot<- SSD12_Plot + geom_line() + xlab("Time") + ylab("SSD-12 Total") 
    
    SSD12_Plot + scale_y_continuous(limits = c(0, 48), breaks = c(0,12,24,36,48)) + scale_x_discrete(expand = c(0.2, 0)) + theme_bw() + theme(panel.background = element_rect("#f1f1f1"), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=9, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=9, family = "AvantGarde", face = "bold")) 
```


##Average Change Over Treatment Period

```{r,echo=FALSE,warning=FALSE,comment=NA,results='asis'}

kable(SSD12_Descriptives, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T)

```

##Reporting Period
```{r,echo = FALSE,warning=FALSE,comment = NA, results='asis'}


if(!is.null(Periods)) {
  cat(Periods, sep = ", ")
} else if (is.null(Periods)) {
  cat("No reporting period was specified. All cases with complete SSD-12 data were used.")
}


```