---
title: "Tampa Scale of Kinesiophobia (TSK)"
author: "Report generated by PsychlytX"
date: "`r format(Sys.time(), '%d %B, %Y')`"
geometry: "left=2cm,right=2cm,top=1.5cm,bottom=1.2cm"
output:
  pdf_document:
    latex_engine: pdflatex
header-includes:
- \usepackage[fontsize=7.8pt]{scrextend}
- \usepackage{color}
- \usepackage{booktabs}
- \usepackage[table]{xcolor}
fontfamily: arev
always_allow_html: yes
params:
PN: 'NULL' 
CN: 'NULL'
Stats_Table_Fullscale: 'NULL'
Tab_Reference: 'NULL'
Stats_Table_Somatic_Focus: 'NULL'
Stats_Table_Activity_Avoidance: 'NULL'
Entered_Scores_Df: 'NULL'
Cutoff_Names: 'NULL'
Item_Df: 'NULL'
Graph_Up_Lim: 'NULL'
Y_Vals: 'NULL'
Y_Vals_Labs: 'NULL'
Graph_Title: 'NULL'
Graph_Up_Lim_AA: 'NULL'
Y_Vals_AA: 'NULL'
Y_Vals_Labs_AA: 'NULL'
subtitle: '**Patient:** `r PN` **|** **Clinician:** `r CN`'
---

```{r,echo = FALSE,warning=FALSE,comment = NA}
knitr::opts_chunk$set(fig.width=7,fig.height=3) 

```

#TSK Total Scale 

##Response Summary

```{r,echo=FALSE,warning=FALSE,comment=NA}
Scores_Table<- Entered_Scores_Df[,c(1,2,3,4,5,6,7)]
names(Scores_Table)<- c("Date", "Score", "Change", "Predicted Score", "Standard Error", "CI Upper Limit", "CI Lower Limit")
kable(Scores_Table, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T)
```


##Data Employed in Reliable Change Analyses

```{r,echo=FALSE,warning=FALSE,comment=NA}

Stats_Table_Fullscale<- kable(Stats_Table_Fullscale, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T) %>% row_spec(0, bold = T)

add_footnote(Stats_Table_Fullscale, c(paste("Source of Reference Population Mean and Sd:", Tab_Reference), paste("Source of Test-Retest Reliability: Woby, Roach, Urmston & Watson (2005)")), notation = "number")
```


##Trend

```{r,echo=FALSE,warning=FALSE,comment=FALSE,message=FALSE, fig.width=8}
 p1<- ggplot(Entered_Scores_Df, aes(x=factor(Entered_Scores_Df$Date, levels = Entered_Scores_Df$Date), y=Entered_Scores_Df$Score, group = 1)) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_1[1], linetype = paste(Cutoff_Names$Cutoff_Name_1[1],":",Entered_Scores_Df$Cutoff_Score_1[1])), color = "#827717", 
size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_2[1], linetype = paste(Cutoff_Names$Cutoff_Name_2[1],":",Entered_Scores_Df$Cutoff_Score_2[1])), color = "#827717", size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_3[1], linetype = paste(Cutoff_Names$Cutoff_Name_3[1],":",Entered_Scores_Df$Cutoff_Score_3[1])), color = "#827717", size = 0.4) + scale_linetype_manual(guide = guide_legend(reverse = TRUE), name = "Cut-Off Scores", values = c("dotted", "longdash", "solid"), limits = c(paste(Cutoff_Names$Cutoff_Name_1[1],":",Entered_Scores_Df$Cutoff_Score_1[1]),
                                                   paste(Cutoff_Names$Cutoff_Name_2[1],":",Entered_Scores_Df$Cutoff_Score_2[1]),
                                                   paste(Cutoff_Names$Cutoff_Name_3[1],":",Entered_Scores_Df$Cutoff_Score_3[1]))) +
  geom_errorbar(aes(ymin=Entered_Scores_Df$CI_Lower_Lim, ymax=Entered_Scores_Df$CI_Upper_Lim), width=.2, size = 0.6,
                 position=position_dodge(0.05), color = "#d35400") + geom_line(color = "#00004c", size = 1) + geom_point(shape=23, fill="#00004c", color="#00004c", size=1.5) + geom_label_repel(aes(label = paste0("Change = ", Entered_Scores_Df$Change)), y = -10, segment.color = 'transparent', size = 3, family = "AvantGarde", face = "bold") + geom_label_repel(aes(label = paste0(Entered_Scores_Df$Score)), size = 3, family = "AvantGarde", face = "bold")
                        
p1<- p1+labs(x="Date", y = paste0(Graph_Title)) +
theme_bw() + theme(panel.background = element_rect("#f1f1f1"), panel.grid.major = element_blank(), panel.grid.major.y = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + scale_y_continuous(limits = c(-10, Graph_Up_Lim), breaks = Y_Vals, labels = paste0(Y_Vals_Labs)) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=12, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=12, family = "AvantGarde", face = "bold"), legend.title=element_text(size=10, family = "AvantGarde"), legend.text=element_text(size=9, family = "AvantGarde"), text=element_text(size=12, family="AvantGarde"))
print(p1) 
```

##Score Differences Between All Pairs of Timepoints 
#####Statistically reliable change is indicated by ** 
```{r, echo = FALSE, warning = FALSE,comment=NA, message=FALSE}

if(length(Entered_Scores_Df$Date) == 2) {  

Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score[2] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[2] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2], "**")
      } else if(Rep_Df$Score[2] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[2] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2])
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df2<- data.frame(Time1, SigChange2)
      names(Change_Rep_Df2)[2]<- paste0(Rep_Df$Date[2])  
  

kable(Change_Rep_Df2, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
  
} 
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 3) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score[2] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[2] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2], "**")
      } else if(Rep_Df$Score[2] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[2] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2])
      }
      
      if(Rep_Df$Score[3] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[3] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange3<- paste((Rep_Df$Score[3] - Rep_Df$Score[1]), "**")
      } else if(Rep_Df$Score[3] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[3] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange3<- paste((Rep_Df$Score[3] - Rep_Df$Score[1]))
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df3<- data.frame(Time1, SigChange2, SigChange3)
      names(Change_Rep_Df3)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df3)[3]<- paste0(Rep_Df$Date[3])  
  
  
kable(Change_Rep_Df3, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 3) {

 if(Rep_Df$Score[3] > Rep_Df$CI_Upper_Lim[2] | Rep_Df$Score[3] < Rep_Df$CI_Lower_Lim[2]) {
        SigChange3a<- paste(Rep_Df$Change[3], "**")
      } else if(Rep_Df$Score[3] < Rep_Df$CI_Upper_Lim[2] & Rep_Df$Score[3] > Rep_Df$CI_Lower_Lim[2]) {
        SigChange3a<- paste(Rep_Df$Change[3])
      }
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df3a<- data.frame(Time2, SigChange3a)
      names(Change_Rep_Df3a)[2]<- paste0(Rep_Df$Date[3])  
  
  
kable(Change_Rep_Df3a, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)

}
  
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score[2] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[2] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2], "**")
      } else if(Rep_Df$Score[2] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[2] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2])
      }
      
      if(Rep_Df$Score[3] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[3] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange3<- paste((Rep_Df$Score[3] - Rep_Df$Score[1]), "**")
      } else if(Rep_Df$Score[3] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[3] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange3<- paste((Rep_Df$Score[3] - Rep_Df$Score[1]))
      }
      
      if(Rep_Df$Score[4] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[4] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange4<- paste((Rep_Df$Score[4] - Rep_Df$Score[1]), "**")
      } else if(Rep_Df$Score[4] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[4] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange4<- paste((Rep_Df$Score[4] - Rep_Df$Score[1]))
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df4<- data.frame(Time1, SigChange2, SigChange3, SigChange4)
      names(Change_Rep_Df4)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df4)[3]<- paste0(Rep_Df$Date[3])
      names(Change_Rep_Df4)[4]<- paste0(Rep_Df$Date[4])
      
  
kable(Change_Rep_Df4, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
if(Rep_Df$Score[3] > Rep_Df$CI_Upper_Lim[2] | Rep_Df$Score[3] < Rep_Df$CI_Lower_Lim[2]) {
        SigChange4a<- paste(Rep_Df$Change[3], "**")
      } else if(Rep_Df$Score[3] < Rep_Df$CI_Upper_Lim[2] & Rep_Df$Score[3] > Rep_Df$CI_Lower_Lim[2]) {
        SigChange4a<- paste(Rep_Df$Change[3])
      }
      
      if(Rep_Df$Score[4] > Rep_Df$CI_Upper_Lim[2] | Rep_Df$Score[4] < Rep_Df$CI_Lower_Lim[2]) {
        SigChange4b<- paste((Rep_Df$Score[4] - Rep_Df$Score[2]), "**")
      } else if(Rep_Df$Score[4] < Rep_Df$CI_Upper_Lim[2] & Rep_Df$Score[4] > Rep_Df$CI_Lower_Lim[2]) {
        SigChange4b<- paste((Rep_Df$Score[4] - Rep_Df$Score[2]))
      }
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df4a<- data.frame(Time2, SigChange4a, SigChange4b)
      names(Change_Rep_Df4a)[2]<- paste0(Rep_Df$Date[3])  
      names(Change_Rep_Df4a)[3]<- paste0(Rep_Df$Date[4])   
  
kable(Change_Rep_Df4a, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
    if(Rep_Df$Score[4] > Rep_Df$CI_Upper_Lim[3] | Rep_Df$Score[4] < Rep_Df$CI_Lower_Lim[3]) {
        SigChange4c<- paste(Rep_Df$Change[4], "**")
      } else if(Rep_Df$Score[4] < Rep_Df$CI_Upper_Lim[3] & Rep_Df$Score[4] > Rep_Df$CI_Lower_Lim[3]) {
        SigChange4c<- paste(Rep_Df$Change[4])
      }
      
      Time3<- paste0(Rep_Df$Date[3])
      Change_Rep_Df4b<- data.frame(Time3, SigChange4c)
      names(Change_Rep_Df4b)[2]<- paste0(Rep_Df$Date[4])    
  
  
kable(Change_Rep_Df4b, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE, comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score[2] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[2] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2], "**")
      } else if(Rep_Df$Score[2] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[2] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2])
      }
      
      if(Rep_Df$Score[3] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[3] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange3<- paste((Rep_Df$Score[3] - Rep_Df$Score[1]), "**")
      } else if(Rep_Df$Score[3] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[3] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange3<- paste((Rep_Df$Score[3] - Rep_Df$Score[1]))
      }
      
      if(Rep_Df$Score[4] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[4] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange4<- paste((Rep_Df$Score[4] - Rep_Df$Score[1]), "**")
      } else if(Rep_Df$Score[4] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[4] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange4<- paste((Rep_Df$Score[4] - Rep_Df$Score[1]))
      }
      
      if(Rep_Df$Score[5] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[5] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange5<- paste((Rep_Df$Score[5] - Rep_Df$Score[1]), "**")
      } else if(Rep_Df$Score[5] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[5] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange5<- paste((Rep_Df$Score[5] - Rep_Df$Score[1]))
      }
      
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df5<- data.frame(Time1, SigChange2, SigChange3, SigChange4, SigChange5)
      names(Change_Rep_Df5)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df5)[3]<- paste0(Rep_Df$Date[3])
      names(Change_Rep_Df5)[4]<- paste0(Rep_Df$Date[4])
      names(Change_Rep_Df5)[5]<- paste0(Rep_Df$Date[5])  
  
  
kable(Change_Rep_Df5, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
 if(Rep_Df$Score[3] > Rep_Df$CI_Upper_Lim[2] | Rep_Df$Score[3] < Rep_Df$CI_Lower_Lim[2]) {
        SigChange5a<- paste(Rep_Df$Change[3], "**")
      } else if(Rep_Df$Score[3] < Rep_Df$CI_Upper_Lim[2] & Rep_Df$Score[3] > Rep_Df$CI_Lower_Lim[2]) {
        SigChange5a<- paste(Rep_Df$Change[3])
      }
      
      if(Rep_Df$Score[4] > Rep_Df$CI_Upper_Lim[2] | Rep_Df$Score[4] < Rep_Df$CI_Lower_Lim[2]) {
        SigChange5b<- paste((Rep_Df$Score[4] - Rep_Df$Score[2]), "**")
      } else if(Rep_Df$Score[4] < Rep_Df$CI_Upper_Lim[2] & Rep_Df$Score[4] > Rep_Df$CI_Lower_Lim[2]) {
        SigChange5b<- paste((Rep_Df$Score[4] - Rep_Df$Score[2]))
      }
      
      if(Rep_Df$Score[5] > Rep_Df$CI_Upper_Lim[2] | Rep_Df$Score[5] < Rep_Df$CI_Lower_Lim[2]) {
        SigChange5c<- paste((Rep_Df$Score[5] - Rep_Df$Score[2]), "**")
      } else if(Rep_Df$Score[5] < Rep_Df$CI_Upper_Lim[2] & Rep_Df$Score[5] > Rep_Df$CI_Lower_Lim[2]) {
        SigChange5c<- paste((Rep_Df$Score[5] - Rep_Df$Score[2]))
      }
      
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df5a<- data.frame(Time2, SigChange5a, SigChange5b, SigChange5c)
      names(Change_Rep_Df5a)[2]<- paste0(Rep_Df$Date[3])  
      names(Change_Rep_Df5a)[3]<- paste0(Rep_Df$Date[4]) 
      names(Change_Rep_Df5a)[4]<- paste0(Rep_Df$Date[5])   
  
kable(Change_Rep_Df5a, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
if(Rep_Df$Score[4] > Rep_Df$CI_Upper_Lim[3] | Rep_Df$Score[4] < Rep_Df$CI_Lower_Lim[3]) {
        SigChange5d<- paste(Rep_Df$Change[4], "**")
      } else if(Rep_Df$Score[4] < Rep_Df$CI_Upper_Lim[3] & Rep_Df$Score[4] > Rep_Df$CI_Lower_Lim[3]) {
        SigChange5d<- paste(Rep_Df$Change[4])
      }
      
      if(Rep_Df$Score[5] > Rep_Df$CI_Upper_Lim[3] | Rep_Df$Score[5] < Rep_Df$CI_Lower_Lim[3]) {
        SigChange5e<- paste((Rep_Df$Score[5] - Rep_Df$Score[3]), "**")
      } else if(Rep_Df$Score[5] < Rep_Df$CI_Upper_Lim[3] & Rep_Df$Score[5] > Rep_Df$CI_Lower_Lim[3]) {
        SigChange5e<- paste((Rep_Df$Score[5] - Rep_Df$Score[3]))
      }
      
      
      Time3<- paste0(Rep_Df$Date[3])
      Change_Rep_Df5b<- data.frame(Time3, SigChange5d, SigChange5e)
      names(Change_Rep_Df5b)[2]<- paste0(Rep_Df$Date[4])  
      names(Change_Rep_Df5b)[3]<- paste0(Rep_Df$Date[5])    
  
kable(Change_Rep_Df5b, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
 if(Rep_Df$Score[5] > Rep_Df$CI_Upper_Lim[4] | Rep_Df$Score[5] < Rep_Df$CI_Lower_Lim[4]) {
        SigChange5f<- paste(Rep_Df$Change[5], "**")
      } else if(Rep_Df$Score[5] < Rep_Df$CI_Upper_Lim[4] & Rep_Df$Score[5] > Rep_Df$CI_Lower_Lim[4]) {
        SigChange5f<- paste(Rep_Df$Change[5])
      }
      
      Time4<- paste0(Rep_Df$Date[4])
      Change_Rep_Df5c<- data.frame(Time4, SigChange5f)
      names(Change_Rep_Df5c)[2]<- paste0(Rep_Df$Date[5])   
  
kable(Change_Rep_Df5c, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

\newpage

#Somatic Focus Subscale

##Response Summary

```{r, echo = FALSE, warning = FALSE, comment=NA}

Scores_Table_Somatic_Focus<- Entered_Scores_Df[,c(1,11,12,13,14,15,16)]
names(Scores_Table_Somatic_Focus)<-  c("Date", "Score", "Change", "Predicted Score", "Standard Error", "CI Upper Limit", "CI Lower Limit")
kable(Scores_Table_Somatic_Focus, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T)
```

##Data Employed in Reliable Change Analyses

```{r, echo = FALSE, warning = FALSE, comment=NA}

Stats_Table_Somatic_Focus<- kable(Stats_Table_Somatic_Focus, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T) %>% row_spec(0, bold = T)

add_footnote(Stats_Table_Somatic_Focus, c(paste("Source of Reference Population Mean and Sd:", Tab_Reference), paste("Source of Reliability (value is internal consistency, not test-retest reliability): Roelofs et al. (2011)")), notation = "number")
```

##Trend

```{r, echo = FALSE, warning=FALSE, comment=FALSE, message=FALSE, fig.width=8}

 p2<- ggplot(Entered_Scores_Df, aes(x=factor(Entered_Scores_Df$Date, levels = Entered_Scores_Df$Date), y=Entered_Scores_Df$Score_Somatic_Focus, group = 1)) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Somatic_Focus_1[1], linetype = paste(Cutoff_Names$Cutoff_Name_Somatic_Focus_1[1],":",Entered_Scores_Df$Cutoff_Score_Somatic_Focus_1[1])),  color = "#827717", 
size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Somatic_Focus_2[1], linetype = paste(Cutoff_Names$Cutoff_Name_Somatic_Focus_2[1],":",Entered_Scores_Df$Cutoff_Score_Somatic_Focus_2[1])), color = "#827717", size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Somatic_Focus_3[1], linetype = paste(Cutoff_Names$Cutoff_Name_Somatic_Focus_3[1],":",Entered_Scores_Df$Cutoff_Score_Somatic_Focus_3[1])), color = "#827717", size = 0.4) +
  scale_linetype_manual(guide = guide_legend(reverse = TRUE), name = "Cut-Off Scores", values = c("dotted", "longdash", "solid"),
limits = c(paste(Cutoff_Names$Cutoff_Name_Somatic_Focus_1[1],":",Entered_Scores_Df$Cutoff_Score_Somatic_Focus_1[1]),                                                   paste(Cutoff_Names$Cutoff_Name_Somatic_Focus_2[1],":",Entered_Scores_Df$Cutoff_Score_Somatic_Focus_2[1]),                                  paste(Cutoff_Names$Cutoff_Name_Somatic_Focus_3[1],":",Entered_Scores_Df$Cutoff_Score_Somatic_Focus_3[1]))) +
  geom_errorbar(aes(ymin=Entered_Scores_Df$CI_Lower_Lim_Somatic_Focus, ymax=Entered_Scores_Df$CI_Upper_Lim_Somatic_Focus), width=.2, size = 0.6,
                 position=position_dodge(0.05), color = "#d35400") + geom_line(color = "#00004c", size = 1) + geom_point(shape=23, fill="#00004c", color="#00004c", size=1.5) + geom_label_repel(aes(label = paste0("Change = ", Entered_Scores_Df$Change_Somatic_Focus)), y = -10, segment.color = 'transparent', size = 3, family = "AvantGarde") + geom_label_repel(aes(label = paste0(Entered_Scores_Df$Score_Somatic_Focus)), size = 3, family = "AvantGarde") 
  
p2<- p2+labs(x="Date", y = "Somatic Focus Score") +
theme_bw() + theme(panel.background = element_rect("#f1f1f1"), panel.grid.major = element_blank(), panel.grid.major.y = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + scale_y_continuous(limits = c(-10, 30), breaks = c(0,4,8,12,16,20), labels = c('0 Min','4','8','12','16','20 Max')) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=12, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=12, family = "AvantGarde", face = "bold"), legend.title=element_text(size=10, family = "AvantGarde"), legend.text=element_text(size=9, family = "AvantGarde"), text=element_text(size=12, family="AvantGarde")) 
print(p2)
```



##Score Differences Between All Pairs of Timepoints 
#####Statistically reliable change is indicated by **

```{r, echo = FALSE, warning = FALSE, comment=NA}


if(length(Entered_Scores_Df$Date) == 2) {  
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Somatic_Focus[2] > Rep_Df$CI_Upper_Lim_Somatic_Focus[1] | Rep_Df$Score_Somatic_Focus[2] < Rep_Df$CI_Lower_Lim_Somatic_Focus[1]) {
        SigChange2_Somatic_Focus<- paste(Rep_Df$Change_Somatic_Focus[2], "**")
      } else if(Rep_Df$Score_Somatic_Focus[2] < Rep_Df$CI_Upper_Lim_Somatic_Focus[1] & Rep_Df$Score_Somatic_Focus[2] > Rep_Df$CI_Lower_Lim_Somatic_Focus[1]) {
        SigChange2_Somatic_Focus<- paste(Rep_Df$Change_Somatic_Focus[2])
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df2_Somatic_Focus<- data.frame(Time1, SigChange2_Somatic_Focus)
      names(Change_Rep_Df2_Somatic_Focus)[2]<- paste0(Rep_Df$Date[2])  
  

kable(Change_Rep_Df2_Somatic_Focus, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
  
} 
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 3) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Somatic_Focus[2] > Rep_Df$CI_Upper_Lim_Somatic_Focus[1] | Rep_Df$Score_Somatic_Focus[2] < Rep_Df$CI_Lower_Lim_Somatic_Focus[1]) {
        SigChange2_Somatic_Focus<- paste(Rep_Df$Change_Somatic_Focus[2], "**")
      } else if(Rep_Df$Score_Somatic_Focus[2] < Rep_Df$CI_Upper_Lim_Somatic_Focus[1] & Rep_Df$Score_Somatic_Focus[2] > Rep_Df$CI_Lower_Lim_Somatic_Focus[1]) {
        SigChange2_Somatic_Focus<- paste(Rep_Df$Change_Somatic_Focus[2])
      }
      
      if(Rep_Df$Score_Somatic_Focus[3] > Rep_Df$CI_Upper_Lim_Somatic_Focus[1] | Rep_Df$Score_Somatic_Focus[3] < Rep_Df$CI_Lower_Lim_Somatic_Focus[1]) {
        SigChange3_Somatic_Focus<- paste((Rep_Df$Score_Somatic_Focus[3] - Rep_Df$Score_Somatic_Focus[1]), "**")
      } else if(Rep_Df$Score_Somatic_Focus[3] < Rep_Df$CI_Upper_Lim_Somatic_Focus[1] & Rep_Df$Score_Somatic_Focus[3] > Rep_Df$CI_Lower_Lim_Somatic_Focus[1]) {
        SigChange3_Somatic_Focus<- paste((Rep_Df$Score_Somatic_Focus[3] - Rep_Df$Score_Somatic_Focus[1]))
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df3_Somatic_Focus<- data.frame(Time1, SigChange2, SigChange3)
      names(Change_Rep_Df3_Somatic_Focus)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df3_Somatic_Focus)[3]<- paste0(Rep_Df$Date[3])  
  
  
kable(Change_Rep_Df3_Somatic_Focus, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 3) {

 if(Rep_Df$Score_Somatic_Focus[3] > Rep_Df$CI_Upper_Lim_Somatic_Focus[2] | Rep_Df$Score_Somatic_Focus[3] < Rep_Df$CI_Lower_Lim_Somatic_Focus[2]) {
        SigChange3a_Somatic_Focus<- paste(Rep_Df$Change_Somatic_Focus[3], "**")
      } else if(Rep_Df$Score_Somatic_Focus[3] < Rep_Df$CI_Upper_Lim_Somatic_Focus[2] & Rep_Df$Score_Somatic_Focus[3] > Rep_Df$CI_Lower_Lim_Somatic_Focus[2]) {
        SigChange3a_Somatic_Focus<- paste(Rep_Df$Change_Somatic_Focus[3])
      }
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df3a_Somatic_Focus<- data.frame(Time2, SigChange3a_Somatic_Focus)
      names(Change_Rep_Df3a_Somatic_Focus)[2]<- paste0(Rep_Df$Date[3])  
  
  
kable(Change_Rep_Df3a_Somatic_Focus, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)

}
  
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Somatic_Focus[2] > Rep_Df$CI_Upper_Lim_Somatic_Focus[1] | Rep_Df$Score_Somatic_Focus[2] < Rep_Df$CI_Lower_Lim_Somatic_Focus[1]) {
        SigChange2_Somatic_Focus<- paste(Rep_Df$Change_Somatic_Focus[2], "**")
      } else if(Rep_Df$Score_Somatic_Focus[2] < Rep_Df$CI_Upper_Lim_Somatic_Focus[1] & Rep_Df$Score_Somatic_Focus[2] > Rep_Df$CI_Lower_Lim_Somatic_Focus[1]) {
        SigChange2_Somatic_Focus<- paste(Rep_Df$Change_Somatic_Focus[2])
      }
      
      if(Rep_Df$Score_Somatic_Focus[3] > Rep_Df$CI_Upper_Lim_Somatic_Focus[1] | Rep_Df$Score_Somatic_Focus[3] < Rep_Df$CI_Lower_Lim_Somatic_Focus[1]) {
        SigChange3_Somatic_Focus<- paste((Rep_Df$Score_Somatic_Focus[3] - Rep_Df$Score_Somatic_Focus[1]), "**")
      } else if(Rep_Df$Score_Somatic_Focus[3] < Rep_Df$CI_Upper_Lim_Somatic_Focus[1] & Rep_Df$Score_Somatic_Focus[3] > Rep_Df$CI_Lower_Lim_Somatic_Focus[1]) {
        SigChange3_Somatic_Focus<- paste((Rep_Df$Score_Somatic_Focus[3] - Rep_Df$Score_Somatic_Focus[1]))
      }
      
      if(Rep_Df$Score_Somatic_Focus[4] > Rep_Df$CI_Upper_Lim_Somatic_Focus[1] | Rep_Df$Score_Somatic_Focus[4] < Rep_Df$CI_Lower_Lim_Somatic_Focus[1]) {
        SigChange4_Somatic_Focus<- paste((Rep_Df$Score_Somatic_Focus[4] - Rep_Df$Score_Somatic_Focus[1]), "**")
      } else if(Rep_Df$Score_Somatic_Focus[4] < Rep_Df$CI_Upper_Lim_Somatic_Focus[1] & Rep_Df$Score_Somatic_Focus[4] > Rep_Df$CI_Lower_Lim_Somatic_Focus[1]) {
        SigChange4_Somatic_Focus<- paste((Rep_Df$Score_Somatic_Focus[4] - Rep_Df$Score_Somatic_Focus[1]))
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df4_Somatic_Focus<- data.frame(Time1, SigChange2_Somatic_Focus, SigChange3_Somatic_Focus, SigChange4_Somatic_Focus)
      names(Change_Rep_Df4_Somatic_Focus)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df4_Somatic_Focus)[3]<- paste0(Rep_Df$Date[3])
      names(Change_Rep_Df4_Somatic_Focus)[4]<- paste0(Rep_Df$Date[4])
      
  
kable(Change_Rep_Df4_Somatic_Focus, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
if(Rep_Df$Score_Somatic_Focus[3] > Rep_Df$CI_Upper_Lim_Somatic_Focus[2] | Rep_Df$Score_Somatic_Focus[3] < Rep_Df$CI_Lower_Lim_Somatic_Focus[2]) {
        SigChange4a_Somatic_Focus<- paste(Rep_Df$Change_Somatic_Focus[3], "**")
      } else if(Rep_Df$Score_Somatic_Focus[3] < Rep_Df$CI_Upper_Lim_Somatic_Focus[2] & Rep_Df$Score_Somatic_Focus[3] > Rep_Df$CI_Lower_Lim_Somatic_Focus[2]) {
        SigChange4a_Somatic_Focus<- paste(Rep_Df$Change_Somatic_Focus[3])
      }
      
      if(Rep_Df$Score_Somatic_Focus[4] > Rep_Df$CI_Upper_Lim_Somatic_Focus[2] | Rep_Df$Score_Somatic_Focus[4] < Rep_Df$CI_Lower_Lim_Somatic_Focus[2]) {
        SigChange4b_Somatic_Focus<- paste((Rep_Df$Score_Somatic_Focus[4] - Rep_Df$Score_Somatic_Focus[2]), "**")
      } else if(Rep_Df$Score_Somatic_Focus[4] < Rep_Df$CI_Upper_Lim_Somatic_Focus[2] & Rep_Df$Score_Somatic_Focus[4] > Rep_Df$CI_Lower_Lim_Somatic_Focus[2]) {
        SigChange4b_Somatic_Focus<- paste((Rep_Df$Score_Somatic_Focus[4] - Rep_Df$Score_Somatic_Focus[2]))
      }
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df4a_Somatic_Focus<- data.frame(Time2, SigChange4a_Somatic_Focus, SigChange4b_Somatic_Focus)
      names(Change_Rep_Df4a_Somatic_Focus)[2]<- paste0(Rep_Df$Date[3])  
      names(Change_Rep_Df4a_Somatic_Focus)[3]<- paste0(Rep_Df$Date[4])   
  
kable(Change_Rep_Df4a_Somatic_Focus, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
    if(Rep_Df$Score_Somatic_Focus[4] > Rep_Df$CI_Upper_Lim_Somatic_Focus[3] | Rep_Df$Score_Somatic_Focus[4] < Rep_Df$CI_Lower_Lim_Somatic_Focus[3]) {
        SigChange4c_Somatic_Focus<- paste(Rep_Df$Change_Somatic_Focus[4], "**")
      } else if(Rep_Df$Score_Somatic_Focus[4] < Rep_Df$CI_Upper_Lim_Somatic_Focus[3] & Rep_Df$Score_Somatic_Focus[4] > Rep_Df$CI_Lower_Lim_Somatic_Focus[3]) {
        SigChange4c_Somatic_Focus<- paste(Rep_Df$Change_Somatic_Focus[4])
      }
      
      Time3<- paste0(Rep_Df$Date[3])
      Change_Rep_Df4b_Somatic_Focus<- data.frame(Time3, SigChange4c_Somatic_Focus)
      names(Change_Rep_Df4b_Somatic_Focus)[2]<- paste0(Rep_Df$Date[4])    
  
  
kable(Change_Rep_Df4b_Somatic_Focus, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Somatic_Focus[2] > Rep_Df$CI_Upper_Lim_Somatic_Focus[1] | Rep_Df$Score_Somatic_Focus[2] < Rep_Df$CI_Lower_Lim_Somatic_Focus[1]) {
        SigChange2_Somatic_Focus<- paste(Rep_Df$Change_Somatic_Focus[2], "**")
      } else if(Rep_Df$Score_Somatic_Focus[2] < Rep_Df$CI_Upper_Lim_Somatic_Focus[1] & Rep_Df$Score_Somatic_Focus[2] > Rep_Df$CI_Lower_Lim_Somatic_Focus[1]) {
        SigChange2_Somatic_Focus<- paste(Rep_Df$Change_Somatic_Focus[2])
      }
      
      if(Rep_Df$Score_Somatic_Focus[3] > Rep_Df$CI_Upper_Lim_Somatic_Focus[1] | Rep_Df$Score_Somatic_Focus[3] < Rep_Df$CI_Lower_Lim_Somatic_Focus[1]) {
        SigChange3_Somatic_Focus<- paste((Rep_Df$Score_Somatic_Focus[3] - Rep_Df$Score_Somatic_Focus[1]), "**")
      } else if(Rep_Df$Score_Somatic_Focus[3] < Rep_Df$CI_Upper_Lim_Somatic_Focus[1] & Rep_Df$Score_Somatic_Focus[3] > Rep_Df$CI_Lower_Lim_Somatic_Focus[1]) {
        SigChange3_Somatic_Focus<- paste((Rep_Df$Score_Somatic_Focus[3] - Rep_Df$Score_Somatic_Focus[1]))
      }
      
      if(Rep_Df$Score_Somatic_Focus[4] > Rep_Df$CI_Upper_Lim_Somatic_Focus[1] | Rep_Df$Score_Somatic_Focus[4] < Rep_Df$CI_Lower_Lim_Somatic_Focus[1]) {
        SigChange4_Somatic_Focus<- paste((Rep_Df$Score_Somatic_Focus[4] - Rep_Df$Score_Somatic_Focus[1]), "**")
      } else if(Rep_Df$Score_Somatic_Focus[4] < Rep_Df$CI_Upper_Lim_Somatic_Focus[1] & Rep_Df$Score_Somatic_Focus[4] > Rep_Df$CI_Lower_Lim_Somatic_Focus[1]) {
        SigChange4_Somatic_Focus<- paste((Rep_Df$Score_Somatic_Focus[4] - Rep_Df$Score_Somatic_Focus[1]))
      }
      
      if(Rep_Df$Score_Somatic_Focus[5] > Rep_Df$CI_Upper_Lim_Somatic_Focus[1] | Rep_Df$Score_Somatic_Focus[5] < Rep_Df$CI_Lower_Lim_Somatic_Focus[1]) {
        SigChange5_Somatic_Focus<- paste((Rep_Df$Score_Somatic_Focus[5] - Rep_Df$Score_Somatic_Focus[1]), "**")
      } else if(Rep_Df$Score_Somatic_Focus[5] < Rep_Df$CI_Upper_Lim_Somatic_Focus[1] & Rep_Df$Score_Somatic_Focus[5] > Rep_Df$CI_Lower_Lim_Somatic_Focus[1]) {
        SigChange5_Somatic_Focus<- paste((Rep_Df$Score_Somatic_Focus[5] - Rep_Df$Score_Somatic_Focus[1]))
      }
      
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df5_Somatic_Focus<- data.frame(Time1, SigChange2_Somatic_Focus, SigChange3_Somatic_Focus, SigChange4_Somatic_Focus, SigChange5_Somatic_Focus)
      names(Change_Rep_Df5_Somatic_Focus)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df5_Somatic_Focus)[3]<- paste0(Rep_Df$Date[3])
      names(Change_Rep_Df5_Somatic_Focus)[4]<- paste0(Rep_Df$Date[4])
      names(Change_Rep_Df5_Somatic_Focus)[5]<- paste0(Rep_Df$Date[5])  
  
  
kable(Change_Rep_Df5_Somatic_Focus, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
 if(Rep_Df$Score_Somatic_Focus[3] > Rep_Df$CI_Upper_Lim_Somatic_Focus[2] | Rep_Df$Score_Somatic_Focus[3] < Rep_Df$CI_Lower_Lim_Somatic_Focus[2]) {
        SigChange5a_Somatic_Focus<- paste(Rep_Df$Change_Somatic_Focus[3], "**")
      } else if(Rep_Df$Score_Somatic_Focus[3] < Rep_Df$CI_Upper_Lim_Somatic_Focus[2] & Rep_Df$Score_Somatic_Focus[3] > Rep_Df$CI_Lower_Lim_Somatic_Focus[2]) {
        SigChange5a_Somatic_Focus<- paste(Rep_Df$Change_Somatic_Focus[3])
      }
      
      if(Rep_Df$Score_Somatic_Focus[4] > Rep_Df$CI_Upper_Lim_Somatic_Focus[2] | Rep_Df$Score_Somatic_Focus[4] < Rep_Df$CI_Lower_Lim_Somatic_Focus[2]) {
        SigChange5b_Somatic_Focus<- paste((Rep_Df$Score_Somatic_Focus[4] - Rep_Df$Score_Somatic_Focus[2]), "**")
      } else if(Rep_Df$Score_Somatic_Focus[4] < Rep_Df$CI_Upper_Lim_Somatic_Focus[2] & Rep_Df$Score_Somatic_Focus[4] > Rep_Df$CI_Lower_Lim_Somatic_Focus[2]) {
        SigChange5b_Somatic_Focus<- paste((Rep_Df$Score_Somatic_Focus[4] - Rep_Df$Score_Somatic_Focus[2]))
      }
      
      if(Rep_Df$Score_Somatic_Focus[5] > Rep_Df$CI_Upper_Lim_Somatic_Focus[2] | Rep_Df$Score_Somatic_Focus[5] < Rep_Df$CI_Lower_Lim_Somatic_Focus[2]) {
        SigChange5c_Somatic_Focus<- paste((Rep_Df$Score_Somatic_Focus[5] - Rep_Df$Score_Somatic_Focus[2]), "**")
      } else if(Rep_Df$Score_Somatic_Focus[5] < Rep_Df$CI_Upper_Lim_Somatic_Focus[2] & Rep_Df$Score_Somatic_Focus[5] > Rep_Df$CI_Lower_Lim_Somatic_Focus[2]) {
        SigChange5c_Somatic_Focus<- paste((Rep_Df$Score_Somatic_Focus[5] - Rep_Df$Score_Somatic_Focus[2]))
      }
      
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df5a_Somatic_Focus<- data.frame(Time2, SigChange5a_Somatic_Focus, SigChange5b_Somatic_Focus, SigChange5c_Somatic_Focus)
      names(Change_Rep_Df5a_Somatic_Focus)[2]<- paste0(Rep_Df$Date[3])  
      names(Change_Rep_Df5a_Somatic_Focus)[3]<- paste0(Rep_Df$Date[4]) 
      names(Change_Rep_Df5a_Somatic_Focus)[4]<- paste0(Rep_Df$Date[5])   
  
kable(Change_Rep_Df5a_Somatic_Focus, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
if(Rep_Df$Score_Somatic_Focus[4] > Rep_Df$CI_Upper_Lim_Somatic_Focus[3] | Rep_Df$Score_Somatic_Focus[4] < Rep_Df$CI_Lower_Lim_Somatic_Focus[3]) {
        SigChange5d_Somatic_Focus<- paste(Rep_Df$Change_Somatic_Focus[4], "**")
      } else if(Rep_Df$Score_Somatic_Focus[4] < Rep_Df$CI_Upper_Lim_Somatic_Focus[3] & Rep_Df$Score_Somatic_Focus[4] > Rep_Df$CI_Lower_Lim_Somatic_Focus[3]) {
        SigChange5d_Somatic_Focus<- paste(Rep_Df$Change_Somatic_Focus[4])
      }
      
      if(Rep_Df$Score_Somatic_Focus[5] > Rep_Df$CI_Upper_Lim_Somatic_Focus[3] | Rep_Df$Score_Somatic_Focus[5] < Rep_Df$CI_Lower_Lim_Somatic_Focus[3]) {
        SigChange5e_Somatic_Focus<- paste((Rep_Df$Score_Somatic_Focus[5] - Rep_Df$Score_Somatic_Focus[3]), "**")
      } else if(Rep_Df$Score_Somatic_Focus[5] < Rep_Df$CI_Upper_Lim_Somatic_Focus[3] & Rep_Df$Score_Somatic_Focus[5] > Rep_Df$CI_Lower_Lim_Somatic_Focus[3]) {
        SigChange5e_Somatic_Focus<- paste((Rep_Df$Score_Somatic_Focus[5] - Rep_Df$Score_Somatic_Focus[3]))
      }
      
      
      Time3<- paste0(Rep_Df$Date[3])
      Change_Rep_Df5b_Somatic_Focus<- data.frame(Time3, SigChange5d_Somatic_Focus, SigChange5e_Somatic_Focus)
      names(Change_Rep_Df5b_Somatic_Focus)[2]<- paste0(Rep_Df$Date[4])  
      names(Change_Rep_Df5b_Somatic_Focus)[3]<- paste0(Rep_Df$Date[5])    
  
kable(Change_Rep_Df5b_Somatic_Focus, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
 if(Rep_Df$Score_Somatic_Focus[5] > Rep_Df$CI_Upper_Lim_Somatic_Focus[4] | Rep_Df$Score_Somatic_Focus[5] < Rep_Df$CI_Lower_Lim_Somatic_Focus[4]) {
        SigChange5f_Somatic_Focus<- paste(Rep_Df$Change_Somatic_Focus[5], "**")
      } else if(Rep_Df$Score_Somatic_Focus[5] < Rep_Df$CI_Upper_Lim_Somatic_Focus[4] & Rep_Df$Score_Somatic_Focus[5] > Rep_Df$CI_Lower_Lim_Somatic_Focus[4]) {
        SigChange5f_Somatic_Focus<- paste(Rep_Df$Change_Somatic_Focus[5])
      }
      
      Time4<- paste0(Rep_Df$Date[4])
      Change_Rep_Df5c_Somatic_Focus<- data.frame(Time4, SigChange5f_Somatic_Focus)
      names(Change_Rep_Df5c_Somatic_Focus)[2]<- paste0(Rep_Df$Date[5])   
  
kable(Change_Rep_Df5c_Somatic_Focus, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```


\newpage

#Activity Avoidance Subscale

##Response Summary
```{r, echo = FALSE, warning = FALSE, , comment=NA}

Scores_Table_Activity_Avoidance<- Entered_Scores_Df[,c(1,20,21,22,23,24,25)]
names(Scores_Table_Activity_Avoidance)<-  c("Date", "Score", "Change", "Predicted Score", "Standard Error", "CI Upper Limit", "CI Lower Limit")

kable(Scores_Table_Activity_Avoidance, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T)
```

##Data Employed in Reliable Change Analyses
```{r, echo = FALSE, warning = FALSE, , comment=NA}

Stats_Table_Activity_Avoidance<- kable(Stats_Table_Activity_Avoidance, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T) %>% row_spec(0, bold = T)

add_footnote(Stats_Table_Activity_Avoidance, c(paste("Source of Reference Population Mean and Sd:", Tab_Reference), paste("Source of Reliability (value is internal consistency, not test-retest reliability): Roelofs et al. (2011)")), notation = "number")
```

##Trend
```{r, echo = FALSE, warning=FALSE, comment=FALSE, message=FALSE, fig.width=8}

 p3<- ggplot(Entered_Scores_Df, aes(x=factor(Entered_Scores_Df$Date, levels = Entered_Scores_Df$Date), y=Entered_Scores_Df$Score_Activity_Avoidance, group = 1)) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Activity_Avoidance_1[1], linetype = paste(Cutoff_Names$Cutoff_Name_Activity_Avoidance_1[1],":",Entered_Scores_Df$Cutoff_Score_Activity_Avoidance_1[1])), color = "#827717", 
size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Activity_Avoidance_2[1], linetype = paste(Cutoff_Names$Cutoff_Name_Activity_Avoidance_2[1],":",Entered_Scores_Df$Cutoff_Score_Activity_Avoidance_2[1])), color = "#827717", size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Activity_Avoidance_3[1], linetype = paste(Cutoff_Names$Cutoff_Name_Activity_Avoidance_3[1],":",Entered_Scores_Df$Cutoff_Score_Activity_Avoidance_3[1])), color = "#827717", size = 0.4) + scale_linetype_manual(guide = guide_legend(reverse = TRUE), name = "Cut-Off Scores", values = c("dotted", "longdash", "solid"), limits = c(paste(Cutoff_Names$Cutoff_Name_Activity_Avoidance_1[1],":",Entered_Scores_Df$Cutoff_Score_Activity_Avoidance_1[1]),                                           paste(Cutoff_Names$Cutoff_Name_Activity_Avoidance_2[1],":",Entered_Scores_Df$Cutoff_Score_Activity_Avoidance_2[1]),                                            paste(Cutoff_Names$Cutoff_Name_Activity_Avoidance_3[1],":",Entered_Scores_Df$Cutoff_Score_Activity_Avoidance_3[1]))) +
  geom_errorbar(aes(ymin=Entered_Scores_Df$CI_Lower_Lim_Activity_Avoidance, ymax=Entered_Scores_Df$CI_Upper_Lim_Activity_Avoidance), width=.2, size = 0.6,
                 position=position_dodge(0.05), color = "#d35400") + geom_line(color = "#00004c", size = 1) + geom_point(shape=23, fill="#00004c", color="#00004c", size=1.5) + geom_label_repel(aes(label = paste0("Change = ", Entered_Scores_Df$Change_Activity_Avoidance)), y = -10, segment.color = 'transparent', size = 3, family = "AvantGarde") + geom_label_repel(aes(label = paste0(Entered_Scores_Df$Score_Activity_Avoidance)), size = 3, family = "AvantGarde") 
  
p3<- p3+labs(x="Date", y = "Activity Avoidance Score") +
theme_bw() + theme(panel.background = element_rect("#f1f1f1"), panel.grid.major = element_blank(), panel.grid.major.y = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + scale_y_continuous(limits = c(-10, Graph_Up_Lim_AA), breaks = Y_Vals_AA,
                             labels = paste0(Y_Vals_Labs_AA)) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=12, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=12, family = "AvantGarde", face = "bold"), legend.title=element_text(size=10, family = "AvantGarde"), legend.text=element_text(size=9, family = "AvantGarde"), text=element_text(size=12, family="AvantGarde")) 
print(p3)
```


##Score Differences Between All Pairs of Timepoints 
#####Statistically reliable change is indicated by **
```{r, echo = FALSE, warning = FALSE,comment=NA}


if(length(Entered_Scores_Df$Date) == 2) {  
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Activity_Avoidance[2] > Rep_Df$CI_Upper_Lim_Activity_Avoidance[1] | Rep_Df$Score_Activity_Avoidance[2] < Rep_Df$CI_Lower_Lim_Activity_Avoidance[1]) {
        SigChange2_Activity_Avoidance<- paste(Rep_Df$Change_Activity_Avoidance[2], "**")
      } else if(Rep_Df$Score_Activity_Avoidance[2] < Rep_Df$CI_Upper_Lim_Activity_Avoidance[1] & Rep_Df$Score_Activity_Avoidance[2] > Rep_Df$CI_Lower_Lim_Activity_Avoidance[1]) {
        SigChange2_Activity_Avoidance<- paste(Rep_Df$Change_Activity_Avoidance[2])
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df2_Activity_Avoidance<- data.frame(Time1, SigChange2_Activity_Avoidance)
      names(Change_Rep_Df2_Activity_Avoidance)[2]<- paste0(Rep_Df$Date[2])  
  

kable(Change_Rep_Df2_Activity_Avoidance, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
  
} 
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 3) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Activity_Avoidance[2] > Rep_Df$CI_Upper_Lim_Activity_Avoidance[1] | Rep_Df$Score_Activity_Avoidance[2] < Rep_Df$CI_Lower_Lim_Activity_Avoidance[1]) {
        SigChange2_Activity_Avoidance<- paste(Rep_Df$Change_Activity_Avoidance[2], "**")
      } else if(Rep_Df$Score_Activity_Avoidance[2] < Rep_Df$CI_Upper_Lim_Activity_Avoidance[1] & Rep_Df$Score_Activity_Avoidance[2] > Rep_Df$CI_Lower_Lim_Activity_Avoidance[1]) {
        SigChange2_Activity_Avoidance<- paste(Rep_Df$Change_Activity_Avoidance[2])
      }
      
      if(Rep_Df$Score_Activity_Avoidance[3] > Rep_Df$CI_Upper_Lim_Activity_Avoidance[1] | Rep_Df$Score_Activity_Avoidance[3] < Rep_Df$CI_Lower_Lim_Activity_Avoidance[1]) {
        SigChange3_Activity_Avoidance<- paste((Rep_Df$Score_Activity_Avoidance[3] - Rep_Df$Score_Activity_Avoidance[1]), "**")
      } else if(Rep_Df$Score_Activity_Avoidance[3] < Rep_Df$CI_Upper_Lim_Activity_Avoidance[1] & Rep_Df$Score_Activity_Avoidance[3] > Rep_Df$CI_Lower_Lim_Activity_Avoidance[1]) {
        SigChange3_Activity_Avoidance<- paste((Rep_Df$Score_Activity_Avoidance[3] - Rep_Df$Score_Activity_Avoidance[1]))
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df3_Activity_Avoidance<- data.frame(Time1, SigChange2, SigChange3)
      names(Change_Rep_Df3_Activity_Avoidance)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df3_Activity_Avoidance)[3]<- paste0(Rep_Df$Date[3])  
  
  
kable(Change_Rep_Df3_Activity_Avoidance, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 3) {

 if(Rep_Df$Score_Activity_Avoidance[3] > Rep_Df$CI_Upper_Lim_Activity_Avoidance[2] | Rep_Df$Score_Activity_Avoidance[3] < Rep_Df$CI_Lower_Lim_Activity_Avoidance[2]) {
        SigChange3a_Activity_Avoidance<- paste(Rep_Df$Change_Activity_Avoidance[3], "**")
      } else if(Rep_Df$Score_Activity_Avoidance[3] < Rep_Df$CI_Upper_Lim_Activity_Avoidance[2] & Rep_Df$Score_Activity_Avoidance[3] > Rep_Df$CI_Lower_Lim_Activity_Avoidance[2]) {
        SigChange3a_Activity_Avoidance<- paste(Rep_Df$Change_Activity_Avoidance[3])
      }
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df3a_Activity_Avoidance<- data.frame(Time2, SigChange3a_Activity_Avoidance)
      names(Change_Rep_Df3a_Activity_Avoidance)[2]<- paste0(Rep_Df$Date[3])  
  
  
kable(Change_Rep_Df3a_Activity_Avoidance, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)

}
  
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Activity_Avoidance[2] > Rep_Df$CI_Upper_Lim_Activity_Avoidance[1] | Rep_Df$Score_Activity_Avoidance[2] < Rep_Df$CI_Lower_Lim_Activity_Avoidance[1]) {
        SigChange2_Activity_Avoidance<- paste(Rep_Df$Change_Activity_Avoidance[2], "**")
      } else if(Rep_Df$Score_Activity_Avoidance[2] < Rep_Df$CI_Upper_Lim_Activity_Avoidance[1] & Rep_Df$Score_Activity_Avoidance[2] > Rep_Df$CI_Lower_Lim_Activity_Avoidance[1]) {
        SigChange2_Activity_Avoidance<- paste(Rep_Df$Change_Activity_Avoidance[2])
      }
      
      if(Rep_Df$Score_Activity_Avoidance[3] > Rep_Df$CI_Upper_Lim_Activity_Avoidance[1] | Rep_Df$Score_Activity_Avoidance[3] < Rep_Df$CI_Lower_Lim_Activity_Avoidance[1]) {
        SigChange3_Activity_Avoidance<- paste((Rep_Df$Score_Activity_Avoidance[3] - Rep_Df$Score_Activity_Avoidance[1]), "**")
      } else if(Rep_Df$Score_Activity_Avoidance[3] < Rep_Df$CI_Upper_Lim_Activity_Avoidance[1] & Rep_Df$Score_Activity_Avoidance[3] > Rep_Df$CI_Lower_Lim_Activity_Avoidance[1]) {
        SigChange3_Activity_Avoidance<- paste((Rep_Df$Score_Activity_Avoidance[3] - Rep_Df$Score_Activity_Avoidance[1]))
      }
      
      if(Rep_Df$Score_Activity_Avoidance[4] > Rep_Df$CI_Upper_Lim_Activity_Avoidance[1] | Rep_Df$Score_Activity_Avoidance[4] < Rep_Df$CI_Lower_Lim_Activity_Avoidance[1]) {
        SigChange4_Activity_Avoidance<- paste((Rep_Df$Score_Activity_Avoidance[4] - Rep_Df$Score_Activity_Avoidance[1]), "**")
      } else if(Rep_Df$Score_Activity_Avoidance[4] < Rep_Df$CI_Upper_Lim_Activity_Avoidance[1] & Rep_Df$Score_Activity_Avoidance[4] > Rep_Df$CI_Lower_Lim_Activity_Avoidance[1]) {
        SigChange4_Activity_Avoidance<- paste((Rep_Df$Score_Activity_Avoidance[4] - Rep_Df$Score_Activity_Avoidance[1]))
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df4_Activity_Avoidance<- data.frame(Time1, SigChange2_Activity_Avoidance, SigChange3_Activity_Avoidance, SigChange4_Activity_Avoidance)
      names(Change_Rep_Df4_Activity_Avoidance)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df4_Activity_Avoidance)[3]<- paste0(Rep_Df$Date[3])
      names(Change_Rep_Df4_Activity_Avoidance)[4]<- paste0(Rep_Df$Date[4])
      
  
kable(Change_Rep_Df4_Activity_Avoidance, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
if(Rep_Df$Score_Activity_Avoidance[3] > Rep_Df$CI_Upper_Lim_Activity_Avoidance[2] | Rep_Df$Score_Activity_Avoidance[3] < Rep_Df$CI_Lower_Lim_Activity_Avoidance[2]) {
        SigChange4a_Activity_Avoidance<- paste(Rep_Df$Change_Activity_Avoidance[3], "**")
      } else if(Rep_Df$Score_Activity_Avoidance[3] < Rep_Df$CI_Upper_Lim_Activity_Avoidance[2] & Rep_Df$Score_Activity_Avoidance[3] > Rep_Df$CI_Lower_Lim_Activity_Avoidance[2]) {
        SigChange4a_Activity_Avoidance<- paste(Rep_Df$Change_Activity_Avoidance[3])
      }
      
      if(Rep_Df$Score_Activity_Avoidance[4] > Rep_Df$CI_Upper_Lim_Activity_Avoidance[2] | Rep_Df$Score_Activity_Avoidance[4] < Rep_Df$CI_Lower_Lim_Activity_Avoidance[2]) {
        SigChange4b_Activity_Avoidance<- paste((Rep_Df$Score_Activity_Avoidance[4] - Rep_Df$Score_Activity_Avoidance[2]), "**")
      } else if(Rep_Df$Score_Activity_Avoidance[4] < Rep_Df$CI_Upper_Lim_Activity_Avoidance[2] & Rep_Df$Score_Activity_Avoidance[4] > Rep_Df$CI_Lower_Lim_Activity_Avoidance[2]) {
        SigChange4b_Activity_Avoidance<- paste((Rep_Df$Score_Activity_Avoidance[4] - Rep_Df$Score_Activity_Avoidance[2]))
      }
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df4a_Activity_Avoidance<- data.frame(Time2, SigChange4a_Activity_Avoidance, SigChange4b_Activity_Avoidance)
      names(Change_Rep_Df4a_Activity_Avoidance)[2]<- paste0(Rep_Df$Date[3])  
      names(Change_Rep_Df4a_Activity_Avoidance)[3]<- paste0(Rep_Df$Date[4])   
  
  
kable(Change_Rep_Df4a_Activity_Avoidance, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
    if(Rep_Df$Score_Activity_Avoidance[4] > Rep_Df$CI_Upper_Lim_Activity_Avoidance[3] | Rep_Df$Score_Activity_Avoidance[4] < Rep_Df$CI_Lower_Lim_Activity_Avoidance[3]) {
        SigChange4c_Activity_Avoidance<- paste(Rep_Df$Change_Activity_Avoidance[4], "**")
      } else if(Rep_Df$Score_Activity_Avoidance[4] < Rep_Df$CI_Upper_Lim_Activity_Avoidance[3] & Rep_Df$Score_Activity_Avoidance[4] > Rep_Df$CI_Lower_Lim_Activity_Avoidance[3]) {
        SigChange4c_Activity_Avoidance<- paste(Rep_Df$Change_Activity_Avoidance[4])
      }
      
      Time3<- paste0(Rep_Df$Date[3])
      Change_Rep_Df4b_Activity_Avoidance<- data.frame(Time3, SigChange4c_Activity_Avoidance)
      names(Change_Rep_Df4b_Activity_Avoidance)[2]<- paste0(Rep_Df$Date[4])    
  
  
  
kable(Change_Rep_Df4b_Activity_Avoidance, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Activity_Avoidance[2] > Rep_Df$CI_Upper_Lim_Activity_Avoidance[1] | Rep_Df$Score_Activity_Avoidance[2] < Rep_Df$CI_Lower_Lim_Activity_Avoidance[1]) {
        SigChange2_Activity_Avoidance<- paste(Rep_Df$Change[2], "**")
      } else if(Rep_Df$Score_Activity_Avoidance[2] < Rep_Df$CI_Upper_Lim_Activity_Avoidance[1] & Rep_Df$Score_Activity_Avoidance[2] > Rep_Df$CI_Lower_Lim_Activity_Avoidance[1]) {
        SigChange2_Activity_Avoidance<- paste(Rep_Df$Change[2])
      }
      
      if(Rep_Df$Score_Activity_Avoidance[3] > Rep_Df$CI_Upper_Lim_Activity_Avoidance[1] | Rep_Df$Score_Activity_Avoidance[3] < Rep_Df$CI_Lower_Lim_Activity_Avoidance[1]) {
        SigChange3_Activity_Avoidance<- paste((Rep_Df$Score_Activity_Avoidance[3] - Rep_Df$Score_Activity_Avoidance[1]), "**")
      } else if(Rep_Df$Score_Activity_Avoidance[3] < Rep_Df$CI_Upper_Lim_Activity_Avoidance[1] & Rep_Df$Score_Activity_Avoidance[3] > Rep_Df$CI_Lower_Lim_Activity_Avoidance[1]) {
        SigChange3_Activity_Avoidance<- paste((Rep_Df$Score_Activity_Avoidance[3] - Rep_Df$Score_Activity_Avoidance[1]))
      }
      
      if(Rep_Df$Score_Activity_Avoidance[4] > Rep_Df$CI_Upper_Lim_Activity_Avoidance[1] | Rep_Df$Score_Activity_Avoidance[4] < Rep_Df$CI_Lower_Lim_Activity_Avoidance[1]) {
        SigChange4_Activity_Avoidance<- paste((Rep_Df$Score_Activity_Avoidance[4] - Rep_Df$Score_Activity_Avoidance[1]), "**")
      } else if(Rep_Df$Score_Activity_Avoidance[4] < Rep_Df$CI_Upper_Lim_Activity_Avoidance[1] & Rep_Df$Score_Activity_Avoidance[4] > Rep_Df$CI_Lower_Lim_Activity_Avoidance[1]) {
        SigChange4_Activity_Avoidance<- paste((Rep_Df$Score_Activity_Avoidance[4] - Rep_Df$Score_Activity_Avoidance[1]))
      }
      
      if(Rep_Df$Score_Activity_Avoidance[5] > Rep_Df$CI_Upper_Lim_Activity_Avoidance[1] | Rep_Df$Score_Activity_Avoidance[5] < Rep_Df$CI_Lower_Lim_Activity_Avoidance[1]) {
        SigChange5_Activity_Avoidance<- paste((Rep_Df$Score_Activity_Avoidance[5] - Rep_Df$Score_Activity_Avoidance[1]), "**")
      } else if(Rep_Df$Score_Activity_Avoidance[5] < Rep_Df$CI_Upper_Lim_Activity_Avoidance[1] & Rep_Df$Score_Activity_Avoidance[5] > Rep_Df$CI_Lower_Lim_Activity_Avoidance[1]) {
        SigChange5_Activity_Avoidance<- paste((Rep_Df$Score_Activity_Avoidance[5] - Rep_Df$Score_Activity_Avoidance[1]))
      }
      
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df5_Activity_Avoidance<- data.frame(Time1, SigChange2_Activity_Avoidance, SigChange3_Activity_Avoidance, SigChange4_Activity_Avoidance, SigChange5_Activity_Avoidance)
      names(Change_Rep_Df5_Activity_Avoidance)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df5_Activity_Avoidance)[3]<- paste0(Rep_Df$Date[3])
      names(Change_Rep_Df5_Activity_Avoidance)[4]<- paste0(Rep_Df$Date[4])
      names(Change_Rep_Df5_Activity_Avoidance)[5]<- paste0(Rep_Df$Date[5])  
  
  
kable(Change_Rep_Df5_Activity_Avoidance, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
 if(Rep_Df$Score_Activity_Avoidance[3] > Rep_Df$CI_Upper_Lim_Activity_Avoidance[2] | Rep_Df$Score_Activity_Avoidance[3] < Rep_Df$CI_Lower_Lim_Activity_Avoidance[2]) {
        SigChange5a_Activity_Avoidance<- paste(Rep_Df$Change_Activity_Avoidance[3], "**")
      } else if(Rep_Df$Score_Activity_Avoidance[3] < Rep_Df$CI_Upper_Lim_Activity_Avoidance[2] & Rep_Df$Score_Activity_Avoidance[3] > Rep_Df$CI_Lower_Lim_Activity_Avoidance[2]) {
        SigChange5a_Activity_Avoidance<- paste(Rep_Df$Change_Activity_Avoidance[3])
      }
      
      if(Rep_Df$Score_Activity_Avoidance[4] > Rep_Df$CI_Upper_Lim_Activity_Avoidance[2] | Rep_Df$Score_Activity_Avoidance[4] < Rep_Df$CI_Lower_Lim_Activity_Avoidance[2]) {
        SigChange5b_Activity_Avoidance<- paste((Rep_Df$Score_Activity_Avoidance[4] - Rep_Df$Score_Activity_Avoidance[2]), "**")
      } else if(Rep_Df$Score_Activity_Avoidance[4] < Rep_Df$CI_Upper_Lim_Activity_Avoidance[2] & Rep_Df$Score_Activity_Avoidance[4] > Rep_Df$CI_Lower_Lim_Activity_Avoidance[2]) {
        SigChange5b_Activity_Avoidance<- paste((Rep_Df$Score_Activity_Avoidance[4] - Rep_Df$Score_Activity_Avoidance[2]))
      }
      
      if(Rep_Df$Score_Activity_Avoidance[5] > Rep_Df$CI_Upper_Lim_Activity_Avoidance[2] | Rep_Df$Score_Activity_Avoidance[5] < Rep_Df$CI_Lower_Lim_Activity_Avoidance[2]) {
        SigChange5c_Activity_Avoidance<- paste((Rep_Df$Score_Activity_Avoidance[5] - Rep_Df$Score_Activity_Avoidance[2]), "**")
      } else if(Rep_Df$Score_Activity_Avoidance[5] < Rep_Df$CI_Upper_Lim_Activity_Avoidance[2] & Rep_Df$Score_Activity_Avoidance[5] > Rep_Df$CI_Lower_Lim_Activity_Avoidance[2]) {
        SigChange5c_Activity_Avoidance<- paste((Rep_Df$Score_Activity_Avoidance[5] - Rep_Df$Score_Activity_Avoidance[2]))
      }
      
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df5a_Activity_Avoidance<- data.frame(Time2, SigChange5a_Activity_Avoidance, SigChange5b_Activity_Avoidance, SigChange5c_Activity_Avoidance)
      names(Change_Rep_Df5a_Activity_Avoidance)[2]<- paste0(Rep_Df$Date[3])  
      names(Change_Rep_Df5a_Activity_Avoidance)[3]<- paste0(Rep_Df$Date[4]) 
      names(Change_Rep_Df5a_Activity_Avoidance)[4]<- paste0(Rep_Df$Date[5])   
  
kable(Change_Rep_Df5a_Activity_Avoidance, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
if(Rep_Df$Score_Activity_Avoidance[4] > Rep_Df$CI_Upper_Lim_Activity_Avoidance[3] | Rep_Df$Score_Activity_Avoidance[4] < Rep_Df$CI_Lower_Lim_Activity_Avoidance[3]) {
        SigChange5d_Activity_Avoidance<- paste(Rep_Df$Change_Activity_Avoidance[4], "**")
      } else if(Rep_Df$Score_Activity_Avoidance[4] < Rep_Df$CI_Upper_Lim_Activity_Avoidance[3] & Rep_Df$Score_Activity_Avoidance[4] > Rep_Df$CI_Lower_Lim_Activity_Avoidance[3]) {
        SigChange5d_Activity_Avoidance<- paste(Rep_Df$Change_Activity_Avoidance[4])
      }
      
      if(Rep_Df$Score_Activity_Avoidance[5] > Rep_Df$CI_Upper_Lim_Activity_Avoidance[3] | Rep_Df$Score_Activity_Avoidance[5] < Rep_Df$CI_Lower_Lim_Activity_Avoidance[3]) {
        SigChange5e_Activity_Avoidance<- paste((Rep_Df$Score_Activity_Avoidance[5] - Rep_Df$Score_Activity_Avoidance[3]), "**")
      } else if(Rep_Df$Score_Activity_Avoidance[5] < Rep_Df$CI_Upper_Lim_Activity_Avoidance[3] & Rep_Df$Score_Activity_Avoidance[5] > Rep_Df$CI_Lower_Lim_Activity_Avoidance[3]) {
        SigChange5e_Activity_Avoidance<- paste((Rep_Df$Score_Activity_Avoidance[5] - Rep_Df$Score_Activity_Avoidance[3]))
      }
      
      
      Time3<- paste0(Rep_Df$Date[3])
      Change_Rep_Df5b_Activity_Avoidance<- data.frame(Time3, SigChange5d_Activity_Avoidance, SigChange5e_Activity_Avoidance)
      names(Change_Rep_Df5b_Activity_Avoidance)[2]<- paste0(Rep_Df$Date[4])  
      names(Change_Rep_Df5b_Activity_Avoidance)[3]<- paste0(Rep_Df$Date[5])    
  
kable(Change_Rep_Df5b_Activity_Avoidance, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
 if(Rep_Df$Score_Activity_Avoidance[5] > Rep_Df$CI_Upper_Lim_Activity_Avoidance[4] | Rep_Df$Score_Activity_Avoidance[5] < Rep_Df$CI_Lower_Lim_Activity_Avoidance[4]) {
        SigChange5f_Activity_Avoidance<- paste(Rep_Df$Change_Activity_Avoidance[5], "**")
      } else if(Rep_Df$Score_Activity_Avoidance[5] < Rep_Df$CI_Upper_Lim_Activity_Avoidance[4] & Rep_Df$Score_Activity_Avoidance[5] > Rep_Df$CI_Lower_Lim_Activity_Avoidance[4]) {
        SigChange5f_Activity_Avoidance<- paste(Rep_Df$Change_Activity_Avoidance[5])
      }
      
      Time4<- paste0(Rep_Df$Date[4])
      Change_Rep_Df5c_Activity_Avoidance<- data.frame(Time4, SigChange5f_Activity_Avoidance)
      names(Change_Rep_Df5c_Activity_Avoidance)[2]<- paste0(Rep_Df$Date[5])   
  
kable(Change_Rep_Df5c_Activity_Avoidance, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

\newpage 

#Most Recent Item Scores

#`r Scores_Table[nrow(Scores_Table),1]`

```{r,echo=FALSE,warning=FALSE,comment=NA}

kable(Item_Df, format = "latex", booktabs = T) %>% kable_styling(position = "left", full_width = T, font_size = 12, latex_options = "striped") %>% row_spec(0, bold = T)
```

\newpage 

\begingroup\Large

\begin{center} \textbf{Information About The Tampa Scale of Kinesiophobia - 11 (TSK-11)} \end{center} 

#What it Measures: 




#What Higher Scores Mean:




#Scale Quality:




#Scale Structure:



\endgroup
