---
title: "Social Interaction Anxiety Scale (SIAS)"
author: "Report generated by PsychlytX"
date: "`r format(Sys.time(), '%d %B, %Y')`"
geometry: "left=2cm,right=2cm,top=1.5cm,bottom=1.2cm"
output:
  pdf_document:
    latex_engine: pdflatex
header-includes:
- \usepackage[fontsize=7.8pt]{scrextend}
- \usepackage{color}
- \usepackage{booktabs}
- \usepackage[table]{xcolor}
fontfamily: arev
always_allow_html: yes
params:
PN: 'NULL' 
CN: 'NULL'
Tab_Reference: 'NULL'
Stats_Table_Fullscale: 'NULL'
Entered_Scores_Df: 'NULL'
Cutoff_Names: 'NULL'
Item_Df: 'NULL'
subtitle: '**Patient:** `r PN` **|** **Clinician:** `r CN`'
---

```{r,echo = FALSE,warning=FALSE,comment = NA}
knitr::opts_chunk$set(fig.width=7,fig.height=3) 

```

#SIAS Total Scale 

##Response Summary

```{r,echo=FALSE,warning=FALSE,comment=NA}
Scores_Table<- Entered_Scores_Df[,c(1,2,3,4,5,6,7)]
names(Scores_Table)<- c("Date", "Score", "Change", "Predicted Score", "Standard Error", "CI Upper Limit", "CI Lower Limit")
kable(Scores_Table, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T)
```


##Data Employed in Reliable Change Analyses

```{r,echo=FALSE,warning=FALSE,comment=NA}

Stats_Table_Fullscale<- kable(Stats_Table_Fullscale, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T) %>% row_spec(0, bold = T)

add_footnote(Stats_Table_Fullscale, c(paste("Source of Reference Population Mean and Sd:", Tab_Reference), paste("Source of Test-Retest Reliability: Stangier, Heidenreich, Berardi, Golbs & Hoyer (1999)")), notation = "number")
```


##Trend

```{r,echo=FALSE,warning=FALSE,comment=FALSE,message=FALSE, fig.width=9}
 p1<- ggplot(Entered_Scores_Df, aes(x=factor(Entered_Scores_Df$Date, levels = Entered_Scores_Df$Date), y=Entered_Scores_Df$Score, group = 1)) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_1[1], linetype = paste(Cutoff_Names$Cutoff_Name_1[1],":",Entered_Scores_Df$Cutoff_Score_1[1])), color = "#827717", size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_2[1], linetype = paste(Cutoff_Names$Cutoff_Name_2[1],":",Entered_Scores_Df$Cutoff_Score_2[1])), color = "#827717", size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_3[1], linetype = paste(Cutoff_Names$Cutoff_Name_3[1],":",Entered_Scores_Df$Cutoff_Score_3[1])), color = "#827717", size = 0.4) + geom_label_repel(aes(label = paste0(Entered_Scores_Df$Score)), size = 3, family = "AvantGarde", face = "bold") + scale_linetype_manual(guide = guide_legend(reverse = TRUE), name = "Cut-Off Scores", values = c("dotted", "longdash", "solid"), limits = c(paste(Cutoff_Names$Cutoff_Name_1[1],":",Entered_Scores_Df$Cutoff_Score_1[1]),
  paste(Cutoff_Names$Cutoff_Name_2[1],":",Entered_Scores_Df$Cutoff_Score_2[1]),
  paste(Cutoff_Names$Cutoff_Name_3[1],":",Entered_Scores_Df$Cutoff_Score_3[1])))  +
  geom_errorbar(aes(ymin=Entered_Scores_Df$CI_Lower_Lim, ymax=Entered_Scores_Df$CI_Upper_Lim), width=.2, size = 0.6,
                 position=position_dodge(0.05), color = "#d35400") + geom_line(color = "#00004c", size = 1) + geom_point(shape=23, fill="#00004c", color="#00004c", size=1.5) + geom_label_repel(aes(label = paste0("Change =", Entered_Scores_Df$Change)), y = -10, segment.color = 'transparent', size = 3, family = "AvantGarde", face = "bold") 

p1<- p1+labs(x="Date", y = "Total SIAS Score") +
theme_bw() + theme(panel.background = element_rect("#f1f1f1"), panel.grid.major = element_blank(), panel.grid.major.y = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + scale_y_continuous(limits = c(-10, 70), breaks = c(0,6,12,18,24,30,36,42,48,54,60), labels = c('Min 0','6','12','18','24','30','36','42','48','54','Max 60')) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=12, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=12, family = "AvantGarde", face = "bold"), legend.title=element_text(size=10, family = "AvantGarde"), legend.text=element_text(size=9, family = "AvantGarde"), text=element_text(size=12, family="AvantGarde")) 
print(p1) 
```

##Score Differences Between All Pairs of Timepoints 
#####Statistically reliable change is indicated by ** 
```{r, echo = FALSE, warning = FALSE,comment=NA, message=FALSE}

if(length(Entered_Scores_Df$Date) == 2) {  

Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score[2] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[2] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2], "**")
      } else if(Rep_Df$Score[2] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[2] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2])
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df2<- data.frame(Time1, SigChange2)
      names(Change_Rep_Df2)[2]<- paste0(Rep_Df$Date[2])  
  

kable(Change_Rep_Df2, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
  
} 
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 3) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score[2] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[2] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2], "**")
      } else if(Rep_Df$Score[2] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[2] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2])
      }
      
      if(Rep_Df$Score[3] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[3] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange3<- paste((Rep_Df$Score[3] - Rep_Df$Score[1]), "**")
      } else if(Rep_Df$Score[3] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[3] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange3<- paste((Rep_Df$Score[3] - Rep_Df$Score[1]))
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df3<- data.frame(Time1, SigChange2, SigChange3)
      names(Change_Rep_Df3)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df3)[3]<- paste0(Rep_Df$Date[3])  
  
  
kable(Change_Rep_Df3, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 3) {

 if(Rep_Df$Score[3] > Rep_Df$CI_Upper_Lim[2] | Rep_Df$Score[3] < Rep_Df$CI_Lower_Lim[2]) {
        SigChange3a<- paste(Rep_Df$Change[3], "**")
      } else if(Rep_Df$Score[3] < Rep_Df$CI_Upper_Lim[2] & Rep_Df$Score[3] > Rep_Df$CI_Lower_Lim[2]) {
        SigChange3a<- paste(Rep_Df$Change[3])
      }
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df3a<- data.frame(Time2, SigChange3a)
      names(Change_Rep_Df3a)[2]<- paste0(Rep_Df$Date[3])  
  
  
kable(Change_Rep_Df3a, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)

}
  
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score[2] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[2] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2], "**")
      } else if(Rep_Df$Score[2] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[2] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2])
      }
      
      if(Rep_Df$Score[3] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[3] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange3<- paste((Rep_Df$Score[3] - Rep_Df$Score[1]), "**")
      } else if(Rep_Df$Score[3] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[3] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange3<- paste((Rep_Df$Score[3] - Rep_Df$Score[1]))
      }
      
      if(Rep_Df$Score[4] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[4] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange4<- paste((Rep_Df$Score[4] - Rep_Df$Score[1]), "**")
      } else if(Rep_Df$Score[4] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[4] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange4<- paste((Rep_Df$Score[4] - Rep_Df$Score[1]))
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df4<- data.frame(Time1, SigChange2, SigChange3, SigChange4)
      names(Change_Rep_Df4)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df4)[3]<- paste0(Rep_Df$Date[3])
      names(Change_Rep_Df4)[4]<- paste0(Rep_Df$Date[4])
      
  
kable(Change_Rep_Df4, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
if(Rep_Df$Score[3] > Rep_Df$CI_Upper_Lim[2] | Rep_Df$Score[3] < Rep_Df$CI_Lower_Lim[2]) {
        SigChange4a<- paste(Rep_Df$Change[3], "**")
      } else if(Rep_Df$Score[3] < Rep_Df$CI_Upper_Lim[2] & Rep_Df$Score[3] > Rep_Df$CI_Lower_Lim[2]) {
        SigChange4a<- paste(Rep_Df$Change[3])
      }
      
      if(Rep_Df$Score[4] > Rep_Df$CI_Upper_Lim[2] | Rep_Df$Score[4] < Rep_Df$CI_Lower_Lim[2]) {
        SigChange4b<- paste((Rep_Df$Score[4] - Rep_Df$Score[2]), "**")
      } else if(Rep_Df$Score[4] < Rep_Df$CI_Upper_Lim[2] & Rep_Df$Score[4] > Rep_Df$CI_Lower_Lim[2]) {
        SigChange4b<- paste((Rep_Df$Score[4] - Rep_Df$Score[2]))
      }
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df4a<- data.frame(Time2, SigChange4a, SigChange4b)
      names(Change_Rep_Df4a)[2]<- paste0(Rep_Df$Date[3])  
      names(Change_Rep_Df4a)[3]<- paste0(Rep_Df$Date[4])   
  
kable(Change_Rep_Df4a, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
    if(Rep_Df$Score[4] > Rep_Df$CI_Upper_Lim[3] | Rep_Df$Score[4] < Rep_Df$CI_Lower_Lim[3]) {
        SigChange4c<- paste(Rep_Df$Change[4], "**")
      } else if(Rep_Df$Score[4] < Rep_Df$CI_Upper_Lim[3] & Rep_Df$Score[4] > Rep_Df$CI_Lower_Lim[3]) {
        SigChange4c<- paste(Rep_Df$Change[4])
      }
      
      Time3<- paste0(Rep_Df$Date[3])
      Change_Rep_Df4b<- data.frame(Time3, SigChange4c)
      names(Change_Rep_Df4b)[2]<- paste0(Rep_Df$Date[4])    
  
  
kable(Change_Rep_Df4b, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE, comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score[2] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[2] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2], "**")
      } else if(Rep_Df$Score[2] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[2] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2])
      }
      
      if(Rep_Df$Score[3] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[3] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange3<- paste((Rep_Df$Score[3] - Rep_Df$Score[1]), "**")
      } else if(Rep_Df$Score[3] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[3] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange3<- paste((Rep_Df$Score[3] - Rep_Df$Score[1]))
      }
      
      if(Rep_Df$Score[4] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[4] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange4<- paste((Rep_Df$Score[4] - Rep_Df$Score[1]), "**")
      } else if(Rep_Df$Score[4] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[4] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange4<- paste((Rep_Df$Score[4] - Rep_Df$Score[1]))
      }
      
      if(Rep_Df$Score[5] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[5] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange5<- paste((Rep_Df$Score[5] - Rep_Df$Score[1]), "**")
      } else if(Rep_Df$Score[5] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[5] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange5<- paste((Rep_Df$Score[5] - Rep_Df$Score[1]))
      }
      
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df5<- data.frame(Time1, SigChange2, SigChange3, SigChange4, SigChange5)
      names(Change_Rep_Df5)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df5)[3]<- paste0(Rep_Df$Date[3])
      names(Change_Rep_Df5)[4]<- paste0(Rep_Df$Date[4])
      names(Change_Rep_Df5)[5]<- paste0(Rep_Df$Date[5])  
  
  
kable(Change_Rep_Df5, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
 if(Rep_Df$Score[3] > Rep_Df$CI_Upper_Lim[2] | Rep_Df$Score[3] < Rep_Df$CI_Lower_Lim[2]) {
        SigChange5a<- paste(Rep_Df$Change[3], "**")
      } else if(Rep_Df$Score[3] < Rep_Df$CI_Upper_Lim[2] & Rep_Df$Score[3] > Rep_Df$CI_Lower_Lim[2]) {
        SigChange5a<- paste(Rep_Df$Change[3])
      }
      
      if(Rep_Df$Score[4] > Rep_Df$CI_Upper_Lim[2] | Rep_Df$Score[4] < Rep_Df$CI_Lower_Lim[2]) {
        SigChange5b<- paste((Rep_Df$Score[4] - Rep_Df$Score[2]), "**")
      } else if(Rep_Df$Score[4] < Rep_Df$CI_Upper_Lim[2] & Rep_Df$Score[4] > Rep_Df$CI_Lower_Lim[2]) {
        SigChange5b<- paste((Rep_Df$Score[4] - Rep_Df$Score[2]))
      }
      
      if(Rep_Df$Score[5] > Rep_Df$CI_Upper_Lim[2] | Rep_Df$Score[5] < Rep_Df$CI_Lower_Lim[2]) {
        SigChange5c<- paste((Rep_Df$Score[5] - Rep_Df$Score[2]), "**")
      } else if(Rep_Df$Score[5] < Rep_Df$CI_Upper_Lim[2] & Rep_Df$Score[5] > Rep_Df$CI_Lower_Lim[2]) {
        SigChange5c<- paste((Rep_Df$Score[5] - Rep_Df$Score[2]))
      }
      
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df5a<- data.frame(Time2, SigChange5a, SigChange5b, SigChange5c)
      names(Change_Rep_Df5a)[2]<- paste0(Rep_Df$Date[3])  
      names(Change_Rep_Df5a)[3]<- paste0(Rep_Df$Date[4]) 
      names(Change_Rep_Df5a)[4]<- paste0(Rep_Df$Date[5])   
  
kable(Change_Rep_Df5a, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
if(Rep_Df$Score[4] > Rep_Df$CI_Upper_Lim[3] | Rep_Df$Score[4] < Rep_Df$CI_Lower_Lim[3]) {
        SigChange5d<- paste(Rep_Df$Change[4], "**")
      } else if(Rep_Df$Score[4] < Rep_Df$CI_Upper_Lim[3] & Rep_Df$Score[4] > Rep_Df$CI_Lower_Lim[3]) {
        SigChange5d<- paste(Rep_Df$Change[4])
      }
      
      if(Rep_Df$Score[5] > Rep_Df$CI_Upper_Lim[3] | Rep_Df$Score[5] < Rep_Df$CI_Lower_Lim[3]) {
        SigChange5e<- paste((Rep_Df$Score[5] - Rep_Df$Score[3]), "**")
      } else if(Rep_Df$Score[5] < Rep_Df$CI_Upper_Lim[3] & Rep_Df$Score[5] > Rep_Df$CI_Lower_Lim[3]) {
        SigChange5e<- paste((Rep_Df$Score[5] - Rep_Df$Score[3]))
      }
      
      
      Time3<- paste0(Rep_Df$Date[3])
      Change_Rep_Df5b<- data.frame(Time3, SigChange5d, SigChange5e)
      names(Change_Rep_Df5b)[2]<- paste0(Rep_Df$Date[4])  
      names(Change_Rep_Df5b)[3]<- paste0(Rep_Df$Date[5])    
  
kable(Change_Rep_Df5b, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
 if(Rep_Df$Score[5] > Rep_Df$CI_Upper_Lim[4] | Rep_Df$Score[5] < Rep_Df$CI_Lower_Lim[4]) {
        SigChange5f<- paste(Rep_Df$Change[5], "**")
      } else if(Rep_Df$Score[5] < Rep_Df$CI_Upper_Lim[4] & Rep_Df$Score[5] > Rep_Df$CI_Lower_Lim[4]) {
        SigChange5f<- paste(Rep_Df$Change[5])
      }
      
      Time4<- paste0(Rep_Df$Date[4])
      Change_Rep_Df5c<- data.frame(Time4, SigChange5f)
      names(Change_Rep_Df5c)[2]<- paste0(Rep_Df$Date[5])   
  
kable(Change_Rep_Df5c, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

\newpage

#Most Recent Item Scores

#`r Scores_Table[nrow(Scores_Table),1]`

```{r,echo=FALSE,warning=FALSE,comment=NA}

kable(Item_Df, format = "latex", booktabs = T) %>% kable_styling(position = "left", full_width = T, font_size = 12, latex_options = "striped") %>% row_spec(0, bold = T)
```

\newpage

\begingroup\Large

\begin{center} \textbf{Information About the Social Interaction Anxiety Scale (SIAS)} \end{center} 

#What it Measures: 

* Anxiety about initiating and maintaining social interactions.


* Concerns about being inarticulate, sounding boring or stupid, appearing awkward, not knowing what to say or how to respond, and being ignored.


* **Does not** assess fear of scrutiny when performing a task or being observed by others.


* **Does not** assess avoidance behaviours.


#What Higher Scores Mean:

* Greater anxiety about starting and continuing social interactions with individuals and groups. 


* Stronger perception that one lacks the skills needed to begin and uphold social interactions.


* Higher likelihood of meeting criteria for Social Anxiety Disorder. But note that the SIAS is **not** a diagnostic instrument.


* Some authors have argued that the SIAS should not be used to measure a subtype of social anxiety (i.e. anxiety about having social interactions; Gomez & Watson, 2017). They argue instead that the SIAS should be administered alongside the Social Phobia Scale (SPS), with the combined scores on both scales being used to assess the level of social anxiety in a general sense.


#Scale Quality:

* In a systematic review of social anxiety self-report measures, the SIAS was one of two scales to receive the highest number of positive ratings (Modini, Abbot & Hunt, 2015). 


#Scale Structure:

* Contains 20 items.


* 5-Point Likert scale.


* Respondents rate to what extent (0 = "Not at all"; 4 = "Extremely") each item is characteristic of them (e.g. "I worry about expressing myself in case I appear awkward").


* Items have been shown to load on a single factor (Mörtberg et al., 2017) and also on a general factor (when items are combined with those of the SPS; Gomez & Watson, 2017).

\endgroup
