---
title: "PTSD Checklist for DSM-5 (PCL-5)"
author: "Report generated by PsychlytX"
date: "`r format(Sys.time(), '%d %B, %Y')`"
geometry: "left=2cm,right=2cm,top=1.5cm,bottom=1.2cm"
output:
  pdf_document:
    latex_engine: pdflatex
header-includes:
- \usepackage[fontsize=7.8pt]{scrextend}
- \usepackage{color}
- \usepackage{booktabs}
- \usepackage[table]{xcolor}
fontfamily: arev
always_allow_html: yes
params:
PN: 'NULL' 
CN: 'NULL'
Tab_Reference: 'NULL'
Stats_Table_Fullscale: 'NULL'
Stats_Table_Intrusion: 'NULL'
Stats_Table_NACM: 'NULL'
Stats_Table_Hyperarousal: 'NULL'
Stats_Table_Avoidance: 'NULL'
Entered_Scores_Df: 'NULL'
Cutoff_Names: 'NULL'
Item_Df: 'NULL'
subtitle: '**Patient:** `r PN` **|** **Clinician:** `r CN`'
---

```{r,echo = FALSE,warning=FALSE,comment = NA}
knitr::opts_chunk$set(fig.width=7,fig.height=3) 

```

#PCL-5 Total Scale 

##Response Summary

```{r,echo=FALSE,warning=FALSE,comment=NA}
Scores_Table<- Entered_Scores_Df[,c(1,2,3,4,5,6,7)]
names(Scores_Table)<- c("Date", "Score", "Change", "Predicted Score", "Standard Error", "CI Upper Limit", "CI Lower Limit")
kable(Scores_Table, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T)
```


##Data Employed in Reliable Change Analyses

```{r,echo=FALSE,warning=FALSE,comment=NA}

Stats_Table_Fullscale<- kable(Stats_Table_Fullscale, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T) %>% row_spec(0, bold = T)

add_footnote(Stats_Table_Fullscale, c(paste("Source of Reference Population Mean and Sd:", Tab_Reference), paste("Source of Test-Retest Reliability: Ashbaugh, Houle-Johnson, El-Hage & Brunet (2016)")), notation = "number")
```


##Trend

```{r,echo=FALSE,warning=FALSE,comment=FALSE,message=FALSE, fig.width=9}
 p1<- ggplot(Entered_Scores_Df, aes(x=factor(Entered_Scores_Df$Date, levels = Entered_Scores_Df$Date), y=Entered_Scores_Df$Score, group = 1)) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_1[1], linetype = paste(Cutoff_Names$Cutoff_Name_1[1],":",Entered_Scores_Df$Cutoff_Score_1[1])), color = "#827717", 
size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_2[1], linetype = paste(Cutoff_Names$Cutoff_Name_2[1],":",Entered_Scores_Df$Cutoff_Score_2[1])), color = "#827717", size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_3[1], linetype = paste(Cutoff_Names$Cutoff_Name_3[1],":",Entered_Scores_Df$Cutoff_Score_3[1])), color = "#827717", size = 0.4) + scale_linetype_manual(guide = guide_legend(reverse = TRUE), name = "Cut-Off Scores", values = c("dotted", "longdash", "solid"), limits = c(paste(Cutoff_Names$Cutoff_Name_1[1],":",Entered_Scores_Df$Cutoff_Score_1[1]),
                                                   paste(Cutoff_Names$Cutoff_Name_2[1],":",Entered_Scores_Df$Cutoff_Score_2[1]),
                                                   paste(Cutoff_Names$Cutoff_Name_3[1],":",Entered_Scores_Df$Cutoff_Score_3[1]))) +
  geom_errorbar(aes(ymin=Entered_Scores_Df$CI_Lower_Lim, ymax=Entered_Scores_Df$CI_Upper_Lim), width=.2, size = 0.6,
                 position=position_dodge(0.05), color = "#d35400") + geom_line(color = "#00004c", size = 1) + geom_point(shape=23, fill="#00004c", color="#00004c", size=1.5) + geom_label_repel(aes(label = paste0("Change = ", Entered_Scores_Df$Change)), y = -10, segment.color = 'transparent', size = 3, family = "AvantGarde", face = "bold") + geom_label_repel(aes(label = paste0(Entered_Scores_Df$Score)), size = 3, family = "AvantGarde", face = "bold")
                        
p1<- p1+labs(x="Date", y = "Total PCL-5 Score") +
theme_bw() + theme(panel.background = element_rect("#f1f1f1"), panel.grid.major = element_blank(), panel.grid.major.y = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + scale_y_continuous(limits = c(-10, 90), breaks = c(0,8,16,24,32,40,48,56,64,72,80), labels = c('0 Min', '8','16','24','32','40','48', '56','64','72','80 Max')) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=12, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=12, family = "AvantGarde", face = "bold"), legend.title=element_text(size=10, family = "AvantGarde"), legend.text=element_text(size=9, family = "AvantGarde"), text=element_text(size=12, family="AvantGarde"))
print(p1) 
```

##Score Differences Between All Pairs of Timepoints 
#####Statistically reliable change is indicated by ** 
```{r, echo = FALSE, warning = FALSE,comment=NA, message=FALSE}

if(length(Entered_Scores_Df$Date) == 2) {  

Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score[2] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[2] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2], "**")
      } else if(Rep_Df$Score[2] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[2] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2])
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df2<- data.frame(Time1, SigChange2)
      names(Change_Rep_Df2)[2]<- paste0(Rep_Df$Date[2])  
  

kable(Change_Rep_Df2, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
  
} 
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 3) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score[2] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[2] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2], "**")
      } else if(Rep_Df$Score[2] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[2] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2])
      }
      
      if(Rep_Df$Score[3] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[3] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange3<- paste((Rep_Df$Score[3] - Rep_Df$Score[1]), "**")
      } else if(Rep_Df$Score[3] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[3] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange3<- paste((Rep_Df$Score[3] - Rep_Df$Score[1]))
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df3<- data.frame(Time1, SigChange2, SigChange3)
      names(Change_Rep_Df3)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df3)[3]<- paste0(Rep_Df$Date[3])  
  
  
kable(Change_Rep_Df3, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 3) {

 if(Rep_Df$Score[3] > Rep_Df$CI_Upper_Lim[2] | Rep_Df$Score[3] < Rep_Df$CI_Lower_Lim[2]) {
        SigChange3a<- paste(Rep_Df$Change[3], "**")
      } else if(Rep_Df$Score[3] < Rep_Df$CI_Upper_Lim[2] & Rep_Df$Score[3] > Rep_Df$CI_Lower_Lim[2]) {
        SigChange3a<- paste(Rep_Df$Change[3])
      }
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df3a<- data.frame(Time2, SigChange3a)
      names(Change_Rep_Df3a)[2]<- paste0(Rep_Df$Date[3])  
  
  
kable(Change_Rep_Df3a, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)

}
  
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score[2] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[2] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2], "**")
      } else if(Rep_Df$Score[2] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[2] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2])
      }
      
      if(Rep_Df$Score[3] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[3] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange3<- paste((Rep_Df$Score[3] - Rep_Df$Score[1]), "**")
      } else if(Rep_Df$Score[3] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[3] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange3<- paste((Rep_Df$Score[3] - Rep_Df$Score[1]))
      }
      
      if(Rep_Df$Score[4] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[4] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange4<- paste((Rep_Df$Score[4] - Rep_Df$Score[1]), "**")
      } else if(Rep_Df$Score[4] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[4] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange4<- paste((Rep_Df$Score[4] - Rep_Df$Score[1]))
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df4<- data.frame(Time1, SigChange2, SigChange3, SigChange4)
      names(Change_Rep_Df4)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df4)[3]<- paste0(Rep_Df$Date[3])
      names(Change_Rep_Df4)[4]<- paste0(Rep_Df$Date[4])
      
  
kable(Change_Rep_Df4, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
if(Rep_Df$Score[3] > Rep_Df$CI_Upper_Lim[2] | Rep_Df$Score[3] < Rep_Df$CI_Lower_Lim[2]) {
        SigChange4a<- paste(Rep_Df$Change[3], "**")
      } else if(Rep_Df$Score[3] < Rep_Df$CI_Upper_Lim[2] & Rep_Df$Score[3] > Rep_Df$CI_Lower_Lim[2]) {
        SigChange4a<- paste(Rep_Df$Change[3])
      }
      
      if(Rep_Df$Score[4] > Rep_Df$CI_Upper_Lim[2] | Rep_Df$Score[4] < Rep_Df$CI_Lower_Lim[2]) {
        SigChange4b<- paste((Rep_Df$Score[4] - Rep_Df$Score[2]), "**")
      } else if(Rep_Df$Score[4] < Rep_Df$CI_Upper_Lim[2] & Rep_Df$Score[4] > Rep_Df$CI_Lower_Lim[2]) {
        SigChange4b<- paste((Rep_Df$Score[4] - Rep_Df$Score[2]))
      }
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df4a<- data.frame(Time2, SigChange4a, SigChange4b)
      names(Change_Rep_Df4a)[2]<- paste0(Rep_Df$Date[3])  
      names(Change_Rep_Df4a)[3]<- paste0(Rep_Df$Date[4])   
  
kable(Change_Rep_Df4a, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
    if(Rep_Df$Score[4] > Rep_Df$CI_Upper_Lim[3] | Rep_Df$Score[4] < Rep_Df$CI_Lower_Lim[3]) {
        SigChange4c<- paste(Rep_Df$Change[4], "**")
      } else if(Rep_Df$Score[4] < Rep_Df$CI_Upper_Lim[3] & Rep_Df$Score[4] > Rep_Df$CI_Lower_Lim[3]) {
        SigChange4c<- paste(Rep_Df$Change[4])
      }
      
      Time3<- paste0(Rep_Df$Date[3])
      Change_Rep_Df4b<- data.frame(Time3, SigChange4c)
      names(Change_Rep_Df4b)[2]<- paste0(Rep_Df$Date[4])    
  
  
kable(Change_Rep_Df4b, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE, comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score[2] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[2] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2], "**")
      } else if(Rep_Df$Score[2] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[2] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2])
      }
      
      if(Rep_Df$Score[3] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[3] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange3<- paste((Rep_Df$Score[3] - Rep_Df$Score[1]), "**")
      } else if(Rep_Df$Score[3] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[3] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange3<- paste((Rep_Df$Score[3] - Rep_Df$Score[1]))
      }
      
      if(Rep_Df$Score[4] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[4] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange4<- paste((Rep_Df$Score[4] - Rep_Df$Score[1]), "**")
      } else if(Rep_Df$Score[4] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[4] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange4<- paste((Rep_Df$Score[4] - Rep_Df$Score[1]))
      }
      
      if(Rep_Df$Score[5] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[5] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange5<- paste((Rep_Df$Score[5] - Rep_Df$Score[1]), "**")
      } else if(Rep_Df$Score[5] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[5] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange5<- paste((Rep_Df$Score[5] - Rep_Df$Score[1]))
      }
      
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df5<- data.frame(Time1, SigChange2, SigChange3, SigChange4, SigChange5)
      names(Change_Rep_Df5)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df5)[3]<- paste0(Rep_Df$Date[3])
      names(Change_Rep_Df5)[4]<- paste0(Rep_Df$Date[4])
      names(Change_Rep_Df5)[5]<- paste0(Rep_Df$Date[5])  
  
  
kable(Change_Rep_Df5, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
 if(Rep_Df$Score[3] > Rep_Df$CI_Upper_Lim[2] | Rep_Df$Score[3] < Rep_Df$CI_Lower_Lim[2]) {
        SigChange5a<- paste(Rep_Df$Change[3], "**")
      } else if(Rep_Df$Score[3] < Rep_Df$CI_Upper_Lim[2] & Rep_Df$Score[3] > Rep_Df$CI_Lower_Lim[2]) {
        SigChange5a<- paste(Rep_Df$Change[3])
      }
      
      if(Rep_Df$Score[4] > Rep_Df$CI_Upper_Lim[2] | Rep_Df$Score[4] < Rep_Df$CI_Lower_Lim[2]) {
        SigChange5b<- paste((Rep_Df$Score[4] - Rep_Df$Score[2]), "**")
      } else if(Rep_Df$Score[4] < Rep_Df$CI_Upper_Lim[2] & Rep_Df$Score[4] > Rep_Df$CI_Lower_Lim[2]) {
        SigChange5b<- paste((Rep_Df$Score[4] - Rep_Df$Score[2]))
      }
      
      if(Rep_Df$Score[5] > Rep_Df$CI_Upper_Lim[2] | Rep_Df$Score[5] < Rep_Df$CI_Lower_Lim[2]) {
        SigChange5c<- paste((Rep_Df$Score[5] - Rep_Df$Score[2]), "**")
      } else if(Rep_Df$Score[5] < Rep_Df$CI_Upper_Lim[2] & Rep_Df$Score[5] > Rep_Df$CI_Lower_Lim[2]) {
        SigChange5c<- paste((Rep_Df$Score[5] - Rep_Df$Score[2]))
      }
      
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df5a<- data.frame(Time2, SigChange5a, SigChange5b, SigChange5c)
      names(Change_Rep_Df5a)[2]<- paste0(Rep_Df$Date[3])  
      names(Change_Rep_Df5a)[3]<- paste0(Rep_Df$Date[4]) 
      names(Change_Rep_Df5a)[4]<- paste0(Rep_Df$Date[5])   
  
kable(Change_Rep_Df5a, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
if(Rep_Df$Score[4] > Rep_Df$CI_Upper_Lim[3] | Rep_Df$Score[4] < Rep_Df$CI_Lower_Lim[3]) {
        SigChange5d<- paste(Rep_Df$Change[4], "**")
      } else if(Rep_Df$Score[4] < Rep_Df$CI_Upper_Lim[3] & Rep_Df$Score[4] > Rep_Df$CI_Lower_Lim[3]) {
        SigChange5d<- paste(Rep_Df$Change[4])
      }
      
      if(Rep_Df$Score[5] > Rep_Df$CI_Upper_Lim[3] | Rep_Df$Score[5] < Rep_Df$CI_Lower_Lim[3]) {
        SigChange5e<- paste((Rep_Df$Score[5] - Rep_Df$Score[3]), "**")
      } else if(Rep_Df$Score[5] < Rep_Df$CI_Upper_Lim[3] & Rep_Df$Score[5] > Rep_Df$CI_Lower_Lim[3]) {
        SigChange5e<- paste((Rep_Df$Score[5] - Rep_Df$Score[3]))
      }
      
      
      Time3<- paste0(Rep_Df$Date[3])
      Change_Rep_Df5b<- data.frame(Time3, SigChange5d, SigChange5e)
      names(Change_Rep_Df5b)[2]<- paste0(Rep_Df$Date[4])  
      names(Change_Rep_Df5b)[3]<- paste0(Rep_Df$Date[5])    
  
kable(Change_Rep_Df5b, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
 if(Rep_Df$Score[5] > Rep_Df$CI_Upper_Lim[4] | Rep_Df$Score[5] < Rep_Df$CI_Lower_Lim[4]) {
        SigChange5f<- paste(Rep_Df$Change[5], "**")
      } else if(Rep_Df$Score[5] < Rep_Df$CI_Upper_Lim[4] & Rep_Df$Score[5] > Rep_Df$CI_Lower_Lim[4]) {
        SigChange5f<- paste(Rep_Df$Change[5])
      }
      
      Time4<- paste0(Rep_Df$Date[4])
      Change_Rep_Df5c<- data.frame(Time4, SigChange5f)
      names(Change_Rep_Df5c)[2]<- paste0(Rep_Df$Date[5])   
  
kable(Change_Rep_Df5c, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

\newpage

#Intrusion Subscale

##Response Summary

```{r, echo = FALSE, warning = FALSE, comment=NA}

Scores_Table_Intrusion<- Entered_Scores_Df[,c(1,11,12,13,14,15,16)]
names(Scores_Table_Intrusion)<-  c("Date", "Score", "Change", "Predicted Score", "Standard Error", "CI Upper Limit", "CI Lower Limit")
kable(Scores_Table_Intrusion, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T)
```

##Data Employed in Reliable Change Analyses

```{r, echo = FALSE, warning = FALSE, comment=NA}

Stats_Table_Intrusion<- kable(Stats_Table_Intrusion, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T) %>% row_spec(0, bold = T)

add_footnote(Stats_Table_Intrusion, c(paste("Source of Reference Population Mean and Sd:", Tab_Reference), paste("Source of Test-Retest Reliability: Ashbaugh, Houle-Johnson, El-Hage & Brunet (2016)")), notation = "number")
```

##Trend

```{r, echo = FALSE, warning=FALSE, comment=FALSE, message=FALSE, fig.width=9}

 p2<- ggplot(Entered_Scores_Df, aes(x=factor(Entered_Scores_Df$Date, levels = Entered_Scores_Df$Date), y=Entered_Scores_Df$Score_Intrusion, group = 1)) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Intrusion_1[1], linetype = paste(Cutoff_Names$Cutoff_Name_Intrusion_1[1],":",Entered_Scores_Df$Cutoff_Score_Intrusion_1[1])),  color = "#827717", 
size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Intrusion_2[1], linetype = paste(Cutoff_Names$Cutoff_Name_Intrusion_2[1],":",Entered_Scores_Df$Cutoff_Score_Intrusion_2[1])), color = "#827717", size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Intrusion_3[1], linetype = paste(Cutoff_Names$Cutoff_Name_Intrusion_3[1],":",Entered_Scores_Df$Cutoff_Score_Intrusion_3[1])), color = "#827717", size = 0.4) +
  scale_linetype_manual(guide = guide_legend(reverse = TRUE), name = "Cut-Off Scores", values = c("dotted", "longdash", "solid"),
limits = c(paste(Cutoff_Names$Cutoff_Name_Intrusion_1[1],":",Entered_Scores_Df$Cutoff_Score_Intrusion_1[1]),                                                   paste(Cutoff_Names$Cutoff_Name_Intrusion_2[1],":",Entered_Scores_Df$Cutoff_Score_Intrusion_2[1]),                                  paste(Cutoff_Names$Cutoff_Name_Intrusion_3[1],":",Entered_Scores_Df$Cutoff_Score_Intrusion_3[1]))) +
  geom_errorbar(aes(ymin=Entered_Scores_Df$CI_Lower_Lim_Intrusion, ymax=Entered_Scores_Df$CI_Upper_Lim_Intrusion), width=.2, size = 0.6,
                 position=position_dodge(0.05), color = "#d35400") + geom_line(color = "#00004c", size = 1) + geom_point(shape=23, fill="#00004c", color="#00004c", size=1.5) + geom_label_repel(aes(label = paste0("Change = ", Entered_Scores_Df$Change_Intrusion)), y = -10, segment.color = 'transparent', size = 3, family = "AvantGarde") + geom_label_repel(aes(label = paste0(Entered_Scores_Df$Score_Intrusion)), size = 3, family = "AvantGarde") 
  
p2<- p2+labs(x="Date", y = "Intrusion Score") +
theme_bw() + theme(panel.background = element_rect("#f1f1f1"), panel.grid.major = element_blank(), panel.grid.major.y = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + scale_y_continuous(limits = c(-10, 30), breaks = c(0,2,4,6,8,10,12,14,16,18,20), labels = c('0 Min', '2','4','6','8','10','12','14','16','18','20 Max')) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=12, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=12, family = "AvantGarde", face = "bold"), legend.title=element_text(size=10, family = "AvantGarde"), legend.text=element_text(size=9, family = "AvantGarde"), text=element_text(size=12, family="AvantGarde")) 
print(p2)
```



##Score Differences Between All Pairs of Timepoints 
#####Statistically reliable change is indicated by **

```{r, echo = FALSE, warning = FALSE, comment=NA}


if(length(Entered_Scores_Df$Date) == 2) {  
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Intrusion[2] > Rep_Df$CI_Upper_Lim_Intrusion[1] | Rep_Df$Score_Intrusion[2] < Rep_Df$CI_Lower_Lim_Intrusion[1]) {
        SigChange2_Intrusion<- paste(Rep_Df$Change_Intrusion[2], "**")
      } else if(Rep_Df$Score_Intrusion[2] < Rep_Df$CI_Upper_Lim_Intrusion[1] & Rep_Df$Score_Intrusion[2] > Rep_Df$CI_Lower_Lim_Intrusion[1]) {
        SigChange2_Intrusion<- paste(Rep_Df$Change_Intrusion[2])
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df2_Intrusion<- data.frame(Time1, SigChange2_Intrusion)
      names(Change_Rep_Df2_Intrusion)[2]<- paste0(Rep_Df$Date[2])  
  

kable(Change_Rep_Df2_Intrusion, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
  
} 
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 3) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Intrusion[2] > Rep_Df$CI_Upper_Lim_Intrusion[1] | Rep_Df$Score_Intrusion[2] < Rep_Df$CI_Lower_Lim_Intrusion[1]) {
        SigChange2_Intrusion<- paste(Rep_Df$Change_Intrusion[2], "**")
      } else if(Rep_Df$Score_Intrusion[2] < Rep_Df$CI_Upper_Lim_Intrusion[1] & Rep_Df$Score_Intrusion[2] > Rep_Df$CI_Lower_Lim_Intrusion[1]) {
        SigChange2_Intrusion<- paste(Rep_Df$Change_Intrusion[2])
      }
      
      if(Rep_Df$Score_Intrusion[3] > Rep_Df$CI_Upper_Lim_Intrusion[1] | Rep_Df$Score_Intrusion[3] < Rep_Df$CI_Lower_Lim_Intrusion[1]) {
        SigChange3_Intrusion<- paste((Rep_Df$Score_Intrusion[3] - Rep_Df$Score_Intrusion[1]), "**")
      } else if(Rep_Df$Score_Intrusion[3] < Rep_Df$CI_Upper_Lim_Intrusion[1] & Rep_Df$Score_Intrusion[3] > Rep_Df$CI_Lower_Lim_Intrusion[1]) {
        SigChange3_Intrusion<- paste((Rep_Df$Score_Intrusion[3] - Rep_Df$Score_Intrusion[1]))
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df3_Intrusion<- data.frame(Time1, SigChange2, SigChange3)
      names(Change_Rep_Df3_Intrusion)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df3_Intrusion)[3]<- paste0(Rep_Df$Date[3])  
  
  
kable(Change_Rep_Df3_Intrusion, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 3) {

 if(Rep_Df$Score_Intrusion[3] > Rep_Df$CI_Upper_Lim_Intrusion[2] | Rep_Df$Score_Intrusion[3] < Rep_Df$CI_Lower_Lim_Intrusion[2]) {
        SigChange3a_Intrusion<- paste(Rep_Df$Change_Intrusion[3], "**")
      } else if(Rep_Df$Score_Intrusion[3] < Rep_Df$CI_Upper_Lim_Intrusion[2] & Rep_Df$Score_Intrusion[3] > Rep_Df$CI_Lower_Lim_Intrusion[2]) {
        SigChange3a_Intrusion<- paste(Rep_Df$Change_Intrusion[3])
      }
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df3a_Intrusion<- data.frame(Time2, SigChange3a_Intrusion)
      names(Change_Rep_Df3a_Intrusion)[2]<- paste0(Rep_Df$Date[3])  
  
  
kable(Change_Rep_Df3a_Intrusion, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)

}
  
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Intrusion[2] > Rep_Df$CI_Upper_Lim_Intrusion[1] | Rep_Df$Score_Intrusion[2] < Rep_Df$CI_Lower_Lim_Intrusion[1]) {
        SigChange2_Intrusion<- paste(Rep_Df$Change_Intrusion[2], "**")
      } else if(Rep_Df$Score_Intrusion[2] < Rep_Df$CI_Upper_Lim_Intrusion[1] & Rep_Df$Score_Intrusion[2] > Rep_Df$CI_Lower_Lim_Intrusion[1]) {
        SigChange2_Intrusion<- paste(Rep_Df$Change_Intrusion[2])
      }
      
      if(Rep_Df$Score_Intrusion[3] > Rep_Df$CI_Upper_Lim_Intrusion[1] | Rep_Df$Score_Intrusion[3] < Rep_Df$CI_Lower_Lim_Intrusion[1]) {
        SigChange3_Intrusion<- paste((Rep_Df$Score_Intrusion[3] - Rep_Df$Score_Intrusion[1]), "**")
      } else if(Rep_Df$Score_Intrusion[3] < Rep_Df$CI_Upper_Lim_Intrusion[1] & Rep_Df$Score_Intrusion[3] > Rep_Df$CI_Lower_Lim_Intrusion[1]) {
        SigChange3_Intrusion<- paste((Rep_Df$Score_Intrusion[3] - Rep_Df$Score_Intrusion[1]))
      }
      
      if(Rep_Df$Score_Intrusion[4] > Rep_Df$CI_Upper_Lim_Intrusion[1] | Rep_Df$Score_Intrusion[4] < Rep_Df$CI_Lower_Lim_Intrusion[1]) {
        SigChange4_Intrusion<- paste((Rep_Df$Score_Intrusion[4] - Rep_Df$Score_Intrusion[1]), "**")
      } else if(Rep_Df$Score_Intrusion[4] < Rep_Df$CI_Upper_Lim_Intrusion[1] & Rep_Df$Score_Intrusion[4] > Rep_Df$CI_Lower_Lim_Intrusion[1]) {
        SigChange4_Intrusion<- paste((Rep_Df$Score_Intrusion[4] - Rep_Df$Score_Intrusion[1]))
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df4_Intrusion<- data.frame(Time1, SigChange2_Intrusion, SigChange3_Intrusion, SigChange4_Intrusion)
      names(Change_Rep_Df4_Intrusion)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df4_Intrusion)[3]<- paste0(Rep_Df$Date[3])
      names(Change_Rep_Df4_Intrusion)[4]<- paste0(Rep_Df$Date[4])
      
  
kable(Change_Rep_Df4_Intrusion, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
if(Rep_Df$Score_Intrusion[3] > Rep_Df$CI_Upper_Lim_Intrusion[2] | Rep_Df$Score_Intrusion[3] < Rep_Df$CI_Lower_Lim_Intrusion[2]) {
        SigChange4a_Intrusion<- paste(Rep_Df$Change_Intrusion[3], "**")
      } else if(Rep_Df$Score_Intrusion[3] < Rep_Df$CI_Upper_Lim_Intrusion[2] & Rep_Df$Score_Intrusion[3] > Rep_Df$CI_Lower_Lim_Intrusion[2]) {
        SigChange4a_Intrusion<- paste(Rep_Df$Change_Intrusion[3])
      }
      
      if(Rep_Df$Score_Intrusion[4] > Rep_Df$CI_Upper_Lim_Intrusion[2] | Rep_Df$Score_Intrusion[4] < Rep_Df$CI_Lower_Lim_Intrusion[2]) {
        SigChange4b_Intrusion<- paste((Rep_Df$Score_Intrusion[4] - Rep_Df$Score_Intrusion[2]), "**")
      } else if(Rep_Df$Score_Intrusion[4] < Rep_Df$CI_Upper_Lim_Intrusion[2] & Rep_Df$Score_Intrusion[4] > Rep_Df$CI_Lower_Lim_Intrusion[2]) {
        SigChange4b_Intrusion<- paste((Rep_Df$Score_Intrusion[4] - Rep_Df$Score_Intrusion[2]))
      }
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df4a_Intrusion<- data.frame(Time2, SigChange4a_Intrusion, SigChange4b_Intrusion)
      names(Change_Rep_Df4a_Intrusion)[2]<- paste0(Rep_Df$Date[3])  
      names(Change_Rep_Df4a_Intrusion)[3]<- paste0(Rep_Df$Date[4])   
  
kable(Change_Rep_Df4a_Intrusion, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
    if(Rep_Df$Score_Intrusion[4] > Rep_Df$CI_Upper_Lim_Intrusion[3] | Rep_Df$Score_Intrusion[4] < Rep_Df$CI_Lower_Lim_Intrusion[3]) {
        SigChange4c_Intrusion<- paste(Rep_Df$Change_Intrusion[4], "**")
      } else if(Rep_Df$Score_Intrusion[4] < Rep_Df$CI_Upper_Lim_Intrusion[3] & Rep_Df$Score_Intrusion[4] > Rep_Df$CI_Lower_Lim_Intrusion[3]) {
        SigChange4c_Intrusion<- paste(Rep_Df$Change_Intrusion[4])
      }
      
      Time3<- paste0(Rep_Df$Date[3])
      Change_Rep_Df4b_Intrusion<- data.frame(Time3, SigChange4c_Intrusion)
      names(Change_Rep_Df4b_Intrusion)[2]<- paste0(Rep_Df$Date[4])    
  
  
kable(Change_Rep_Df4b_Intrusion, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Intrusion[2] > Rep_Df$CI_Upper_Lim_Intrusion[1] | Rep_Df$Score_Intrusion[2] < Rep_Df$CI_Lower_Lim_Intrusion[1]) {
        SigChange2_Intrusion<- paste(Rep_Df$Change_Intrusion[2], "**")
      } else if(Rep_Df$Score_Intrusion[2] < Rep_Df$CI_Upper_Lim_Intrusion[1] & Rep_Df$Score_Intrusion[2] > Rep_Df$CI_Lower_Lim_Intrusion[1]) {
        SigChange2_Intrusion<- paste(Rep_Df$Change_Intrusion[2])
      }
      
      if(Rep_Df$Score_Intrusion[3] > Rep_Df$CI_Upper_Lim_Intrusion[1] | Rep_Df$Score_Intrusion[3] < Rep_Df$CI_Lower_Lim_Intrusion[1]) {
        SigChange3_Intrusion<- paste((Rep_Df$Score_Intrusion[3] - Rep_Df$Score_Intrusion[1]), "**")
      } else if(Rep_Df$Score_Intrusion[3] < Rep_Df$CI_Upper_Lim_Intrusion[1] & Rep_Df$Score_Intrusion[3] > Rep_Df$CI_Lower_Lim_Intrusion[1]) {
        SigChange3_Intrusion<- paste((Rep_Df$Score_Intrusion[3] - Rep_Df$Score_Intrusion[1]))
      }
      
      if(Rep_Df$Score_Intrusion[4] > Rep_Df$CI_Upper_Lim_Intrusion[1] | Rep_Df$Score_Intrusion[4] < Rep_Df$CI_Lower_Lim_Intrusion[1]) {
        SigChange4_Intrusion<- paste((Rep_Df$Score_Intrusion[4] - Rep_Df$Score_Intrusion[1]), "**")
      } else if(Rep_Df$Score_Intrusion[4] < Rep_Df$CI_Upper_Lim_Intrusion[1] & Rep_Df$Score_Intrusion[4] > Rep_Df$CI_Lower_Lim_Intrusion[1]) {
        SigChange4_Intrusion<- paste((Rep_Df$Score_Intrusion[4] - Rep_Df$Score_Intrusion[1]))
      }
      
      if(Rep_Df$Score_Intrusion[5] > Rep_Df$CI_Upper_Lim_Intrusion[1] | Rep_Df$Score_Intrusion[5] < Rep_Df$CI_Lower_Lim_Intrusion[1]) {
        SigChange5_Intrusion<- paste((Rep_Df$Score_Intrusion[5] - Rep_Df$Score_Intrusion[1]), "**")
      } else if(Rep_Df$Score_Intrusion[5] < Rep_Df$CI_Upper_Lim_Intrusion[1] & Rep_Df$Score_Intrusion[5] > Rep_Df$CI_Lower_Lim_Intrusion[1]) {
        SigChange5_Intrusion<- paste((Rep_Df$Score_Intrusion[5] - Rep_Df$Score_Intrusion[1]))
      }
      
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df5_Intrusion<- data.frame(Time1, SigChange2_Intrusion, SigChange3_Intrusion, SigChange4_Intrusion, SigChange5_Intrusion)
      names(Change_Rep_Df5_Intrusion)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df5_Intrusion)[3]<- paste0(Rep_Df$Date[3])
      names(Change_Rep_Df5_Intrusion)[4]<- paste0(Rep_Df$Date[4])
      names(Change_Rep_Df5_Intrusion)[5]<- paste0(Rep_Df$Date[5])  
  
  
kable(Change_Rep_Df5_Intrusion, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
 if(Rep_Df$Score_Intrusion[3] > Rep_Df$CI_Upper_Lim_Intrusion[2] | Rep_Df$Score_Intrusion[3] < Rep_Df$CI_Lower_Lim_Intrusion[2]) {
        SigChange5a_Intrusion<- paste(Rep_Df$Change_Intrusion[3], "**")
      } else if(Rep_Df$Score_Intrusion[3] < Rep_Df$CI_Upper_Lim_Intrusion[2] & Rep_Df$Score_Intrusion[3] > Rep_Df$CI_Lower_Lim_Intrusion[2]) {
        SigChange5a_Intrusion<- paste(Rep_Df$Change_Intrusion[3])
      }
      
      if(Rep_Df$Score_Intrusion[4] > Rep_Df$CI_Upper_Lim_Intrusion[2] | Rep_Df$Score_Intrusion[4] < Rep_Df$CI_Lower_Lim_Intrusion[2]) {
        SigChange5b_Intrusion<- paste((Rep_Df$Score_Intrusion[4] - Rep_Df$Score_Intrusion[2]), "**")
      } else if(Rep_Df$Score_Intrusion[4] < Rep_Df$CI_Upper_Lim_Intrusion[2] & Rep_Df$Score_Intrusion[4] > Rep_Df$CI_Lower_Lim_Intrusion[2]) {
        SigChange5b_Intrusion<- paste((Rep_Df$Score_Intrusion[4] - Rep_Df$Score_Intrusion[2]))
      }
      
      if(Rep_Df$Score_Intrusion[5] > Rep_Df$CI_Upper_Lim_Intrusion[2] | Rep_Df$Score_Intrusion[5] < Rep_Df$CI_Lower_Lim_Intrusion[2]) {
        SigChange5c_Intrusion<- paste((Rep_Df$Score_Intrusion[5] - Rep_Df$Score_Intrusion[2]), "**")
      } else if(Rep_Df$Score_Intrusion[5] < Rep_Df$CI_Upper_Lim_Intrusion[2] & Rep_Df$Score_Intrusion[5] > Rep_Df$CI_Lower_Lim_Intrusion[2]) {
        SigChange5c_Intrusion<- paste((Rep_Df$Score_Intrusion[5] - Rep_Df$Score_Intrusion[2]))
      }
      
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df5a_Intrusion<- data.frame(Time2, SigChange5a_Intrusion, SigChange5b_Intrusion, SigChange5c_Intrusion)
      names(Change_Rep_Df5a_Intrusion)[2]<- paste0(Rep_Df$Date[3])  
      names(Change_Rep_Df5a_Intrusion)[3]<- paste0(Rep_Df$Date[4]) 
      names(Change_Rep_Df5a_Intrusion)[4]<- paste0(Rep_Df$Date[5])   
  
kable(Change_Rep_Df5a_Intrusion, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
if(Rep_Df$Score_Intrusion[4] > Rep_Df$CI_Upper_Lim_Intrusion[3] | Rep_Df$Score_Intrusion[4] < Rep_Df$CI_Lower_Lim_Intrusion[3]) {
        SigChange5d_Intrusion<- paste(Rep_Df$Change_Intrusion[4], "**")
      } else if(Rep_Df$Score_Intrusion[4] < Rep_Df$CI_Upper_Lim_Intrusion[3] & Rep_Df$Score_Intrusion[4] > Rep_Df$CI_Lower_Lim_Intrusion[3]) {
        SigChange5d_Intrusion<- paste(Rep_Df$Change_Intrusion[4])
      }
      
      if(Rep_Df$Score_Intrusion[5] > Rep_Df$CI_Upper_Lim_Intrusion[3] | Rep_Df$Score_Intrusion[5] < Rep_Df$CI_Lower_Lim_Intrusion[3]) {
        SigChange5e_Intrusion<- paste((Rep_Df$Score_Intrusion[5] - Rep_Df$Score_Intrusion[3]), "**")
      } else if(Rep_Df$Score_Intrusion[5] < Rep_Df$CI_Upper_Lim_Intrusion[3] & Rep_Df$Score_Intrusion[5] > Rep_Df$CI_Lower_Lim_Intrusion[3]) {
        SigChange5e_Intrusion<- paste((Rep_Df$Score_Intrusion[5] - Rep_Df$Score_Intrusion[3]))
      }
      
      
      Time3<- paste0(Rep_Df$Date[3])
      Change_Rep_Df5b_Intrusion<- data.frame(Time3, SigChange5d_Intrusion, SigChange5e_Intrusion)
      names(Change_Rep_Df5b_Intrusion)[2]<- paste0(Rep_Df$Date[4])  
      names(Change_Rep_Df5b_Intrusion)[3]<- paste0(Rep_Df$Date[5])    
  
kable(Change_Rep_Df5b_Intrusion, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
 if(Rep_Df$Score_Intrusion[5] > Rep_Df$CI_Upper_Lim_Intrusion[4] | Rep_Df$Score_Intrusion[5] < Rep_Df$CI_Lower_Lim_Intrusion[4]) {
        SigChange5f_Intrusion<- paste(Rep_Df$Change_Intrusion[5], "**")
      } else if(Rep_Df$Score_Intrusion[5] < Rep_Df$CI_Upper_Lim_Intrusion[4] & Rep_Df$Score_Intrusion[5] > Rep_Df$CI_Lower_Lim_Intrusion[4]) {
        SigChange5f_Intrusion<- paste(Rep_Df$Change_Intrusion[5])
      }
      
      Time4<- paste0(Rep_Df$Date[4])
      Change_Rep_Df5c_Intrusion<- data.frame(Time4, SigChange5f_Intrusion)
      names(Change_Rep_Df5c_Intrusion)[2]<- paste0(Rep_Df$Date[5])   
  
kable(Change_Rep_Df5c_Intrusion, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```


\newpage

#Negative Alteration in Cognition & Mood (NACM) Subscale

##Response Summary
```{r, echo = FALSE, warning = FALSE, , comment=NA}

Scores_Table_NACM<- Entered_Scores_Df[,c(1,20,21,22,23,24,25)]
names(Scores_Table_NACM)<-  c("Date", "Score", "Change", "Predicted Score", "Standard Error", "CI Upper Limit", "CI Lower Limit")

kable(Scores_Table_NACM, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T)
```

##Data Employed in Reliable Change Analyses
```{r, echo = FALSE, warning = FALSE, , comment=NA}

Stats_Table_NACM<- kable(Stats_Table_NACM, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T) %>% row_spec(0, bold = T)

add_footnote(Stats_Table_NACM, c(paste("Source of Reference Population Mean and Sd:", Tab_Reference), paste("Source of Test-Retest Reliability: Ashbaugh, Houle-Johnson, El-Hage & Brunet (2016)")), notation = "number")
```

##Trend
```{r, echo = FALSE, warning=FALSE, comment=FALSE, message=FALSE, fig.width=9}

 p3<- ggplot(Entered_Scores_Df, aes(x=factor(Entered_Scores_Df$Date, levels = Entered_Scores_Df$Date), y=Entered_Scores_Df$Score_NACM, group = 1)) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_NACM_1[1], linetype = paste(Cutoff_Names$Cutoff_Name_NACM_1[1],":",Entered_Scores_Df$Cutoff_Score_NACM_1[1])), color = "#827717", 
size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_NACM_2[1], linetype = paste(Cutoff_Names$Cutoff_Name_NACM_2[1],":",Entered_Scores_Df$Cutoff_Score_NACM_2[1])), color = "#827717", size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_NACM_3[1], linetype = paste(Cutoff_Names$Cutoff_Name_NACM_3[1],":",Entered_Scores_Df$Cutoff_Score_NACM_3[1])), color = "#827717", size = 0.4) + scale_linetype_manual(guide = guide_legend(reverse = TRUE), name = "Cut-Off Scores", values = c("dotted", "longdash", "solid"), limits = c(paste(Cutoff_Names$Cutoff_Name_NACM_1[1],":",Entered_Scores_Df$Cutoff_Score_NACM_1[1]),                                           paste(Cutoff_Names$Cutoff_Name_NACM_2[1],":",Entered_Scores_Df$Cutoff_Score_NACM_2[1]),                                            paste(Cutoff_Names$Cutoff_Name_NACM_3[1],":",Entered_Scores_Df$Cutoff_Score_NACM_3[1]))) +
  geom_errorbar(aes(ymin=Entered_Scores_Df$CI_Lower_Lim_NACM, ymax=Entered_Scores_Df$CI_Upper_Lim_NACM), width=.2, size = 0.6,
                 position=position_dodge(0.05), color = "#d35400") + geom_line(color = "#00004c", size = 1) + geom_point(shape=23, fill="#00004c", color="#00004c", size=1.5) + geom_label_repel(aes(label = paste0("Change = ", Entered_Scores_Df$Change_NACM)), y = -10, segment.color = 'transparent', size = 3, family = "AvantGarde") + geom_label_repel(aes(label = paste0(Entered_Scores_Df$Score_NACM)), size = 3, family = "AvantGarde") 
  
p3<- p3+labs(x="Date", y = "NACM Score") +
theme_bw() + theme(panel.background = element_rect("#f1f1f1"), panel.grid.major = element_blank(), panel.grid.major.y = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + scale_y_continuous(limits = c(-10, 38), breaks = c(0,4,8,12,16,20,24,28),
                             labels = c('0 Min','4','8','12','16','20','24','28 Max')) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=12, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=12, family = "AvantGarde", face = "bold"), legend.title=element_text(size=10, family = "AvantGarde"), legend.text=element_text(size=9, family = "AvantGarde"), text=element_text(size=12, family="AvantGarde")) 
print(p3)
```


##Score Differences Between All Pairs of Timepoints 
#####Statistically reliable change is indicated by **
```{r, echo = FALSE, warning = FALSE,comment=NA}


if(length(Entered_Scores_Df$Date) == 2) {  
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_NACM[2] > Rep_Df$CI_Upper_Lim_NACM[1] | Rep_Df$Score_NACM[2] < Rep_Df$CI_Lower_Lim_NACM[1]) {
        SigChange2_NACM<- paste(Rep_Df$Change_NACM[2], "**")
      } else if(Rep_Df$Score_NACM[2] < Rep_Df$CI_Upper_Lim_NACM[1] & Rep_Df$Score_NACM[2] > Rep_Df$CI_Lower_Lim_NACM[1]) {
        SigChange2_NACM<- paste(Rep_Df$Change_NACM[2])
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df2_NACM<- data.frame(Time1, SigChange2_NACM)
      names(Change_Rep_Df2_NACM)[2]<- paste0(Rep_Df$Date[2])  
  

kable(Change_Rep_Df2_NACM, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
  
} 
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 3) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_NACM[2] > Rep_Df$CI_Upper_Lim_NACM[1] | Rep_Df$Score_NACM[2] < Rep_Df$CI_Lower_Lim_NACM[1]) {
        SigChange2_NACM<- paste(Rep_Df$Change_NACM[2], "**")
      } else if(Rep_Df$Score_NACM[2] < Rep_Df$CI_Upper_Lim_NACM[1] & Rep_Df$Score_NACM[2] > Rep_Df$CI_Lower_Lim_NACM[1]) {
        SigChange2_NACM<- paste(Rep_Df$Change_NACM[2])
      }
      
      if(Rep_Df$Score_NACM[3] > Rep_Df$CI_Upper_Lim_NACM[1] | Rep_Df$Score_NACM[3] < Rep_Df$CI_Lower_Lim_NACM[1]) {
        SigChange3_NACM<- paste((Rep_Df$Score_NACM[3] - Rep_Df$Score_NACM[1]), "**")
      } else if(Rep_Df$Score_NACM[3] < Rep_Df$CI_Upper_Lim_NACM[1] & Rep_Df$Score_NACM[3] > Rep_Df$CI_Lower_Lim_NACM[1]) {
        SigChange3_NACM<- paste((Rep_Df$Score_NACM[3] - Rep_Df$Score_NACM[1]))
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df3_NACM<- data.frame(Time1, SigChange2, SigChange3)
      names(Change_Rep_Df3_NACM)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df3_NACM)[3]<- paste0(Rep_Df$Date[3])  
  
  
kable(Change_Rep_Df3_NACM, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 3) {

 if(Rep_Df$Score_NACM[3] > Rep_Df$CI_Upper_Lim_NACM[2] | Rep_Df$Score_NACM[3] < Rep_Df$CI_Lower_Lim_NACM[2]) {
        SigChange3a_NACM<- paste(Rep_Df$Change_NACM[3], "**")
      } else if(Rep_Df$Score_NACM[3] < Rep_Df$CI_Upper_Lim_NACM[2] & Rep_Df$Score_NACM[3] > Rep_Df$CI_Lower_Lim_NACM[2]) {
        SigChange3a_NACM<- paste(Rep_Df$Change_NACM[3])
      }
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df3a_NACM<- data.frame(Time2, SigChange3a_NACM)
      names(Change_Rep_Df3a_NACM)[2]<- paste0(Rep_Df$Date[3])  
  
  
kable(Change_Rep_Df3a_NACM, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)

}
  
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_NACM[2] > Rep_Df$CI_Upper_Lim_NACM[1] | Rep_Df$Score_NACM[2] < Rep_Df$CI_Lower_Lim_NACM[1]) {
        SigChange2_NACM<- paste(Rep_Df$Change_NACM[2], "**")
      } else if(Rep_Df$Score_NACM[2] < Rep_Df$CI_Upper_Lim_NACM[1] & Rep_Df$Score_NACM[2] > Rep_Df$CI_Lower_Lim_NACM[1]) {
        SigChange2_NACM<- paste(Rep_Df$Change_NACM[2])
      }
      
      if(Rep_Df$Score_NACM[3] > Rep_Df$CI_Upper_Lim_NACM[1] | Rep_Df$Score_NACM[3] < Rep_Df$CI_Lower_Lim_NACM[1]) {
        SigChange3_NACM<- paste((Rep_Df$Score_NACM[3] - Rep_Df$Score_NACM[1]), "**")
      } else if(Rep_Df$Score_NACM[3] < Rep_Df$CI_Upper_Lim_NACM[1] & Rep_Df$Score_NACM[3] > Rep_Df$CI_Lower_Lim_NACM[1]) {
        SigChange3_NACM<- paste((Rep_Df$Score_NACM[3] - Rep_Df$Score_NACM[1]))
      }
      
      if(Rep_Df$Score_NACM[4] > Rep_Df$CI_Upper_Lim_NACM[1] | Rep_Df$Score_NACM[4] < Rep_Df$CI_Lower_Lim_NACM[1]) {
        SigChange4_NACM<- paste((Rep_Df$Score_NACM[4] - Rep_Df$Score_NACM[1]), "**")
      } else if(Rep_Df$Score_NACM[4] < Rep_Df$CI_Upper_Lim_NACM[1] & Rep_Df$Score_NACM[4] > Rep_Df$CI_Lower_Lim_NACM[1]) {
        SigChange4_NACM<- paste((Rep_Df$Score_NACM[4] - Rep_Df$Score_NACM[1]))
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df4_NACM<- data.frame(Time1, SigChange2_NACM, SigChange3_NACM, SigChange4_NACM)
      names(Change_Rep_Df4_NACM)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df4_NACM)[3]<- paste0(Rep_Df$Date[3])
      names(Change_Rep_Df4_NACM)[4]<- paste0(Rep_Df$Date[4])
      
  
kable(Change_Rep_Df4_NACM, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
if(Rep_Df$Score_NACM[3] > Rep_Df$CI_Upper_Lim_NACM[2] | Rep_Df$Score_NACM[3] < Rep_Df$CI_Lower_Lim_NACM[2]) {
        SigChange4a_NACM<- paste(Rep_Df$Change_NACM[3], "**")
      } else if(Rep_Df$Score_NACM[3] < Rep_Df$CI_Upper_Lim_NACM[2] & Rep_Df$Score_NACM[3] > Rep_Df$CI_Lower_Lim_NACM[2]) {
        SigChange4a_NACM<- paste(Rep_Df$Change_NACM[3])
      }
      
      if(Rep_Df$Score_NACM[4] > Rep_Df$CI_Upper_Lim_NACM[2] | Rep_Df$Score_NACM[4] < Rep_Df$CI_Lower_Lim_NACM[2]) {
        SigChange4b_NACM<- paste((Rep_Df$Score_NACM[4] - Rep_Df$Score_NACM[2]), "**")
      } else if(Rep_Df$Score_NACM[4] < Rep_Df$CI_Upper_Lim_NACM[2] & Rep_Df$Score_NACM[4] > Rep_Df$CI_Lower_Lim_NACM[2]) {
        SigChange4b_NACM<- paste((Rep_Df$Score_NACM[4] - Rep_Df$Score_NACM[2]))
      }
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df4a_NACM<- data.frame(Time2, SigChange4a_NACM, SigChange4b_NACM)
      names(Change_Rep_Df4a_NACM)[2]<- paste0(Rep_Df$Date[3])  
      names(Change_Rep_Df4a_NACM)[3]<- paste0(Rep_Df$Date[4])   
  
  
kable(Change_Rep_Df4a_NACM, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
    if(Rep_Df$Score_NACM[4] > Rep_Df$CI_Upper_Lim_NACM[3] | Rep_Df$Score_NACM[4] < Rep_Df$CI_Lower_Lim_NACM[3]) {
        SigChange4c_NACM<- paste(Rep_Df$Change_NACM[4], "**")
      } else if(Rep_Df$Score_NACM[4] < Rep_Df$CI_Upper_Lim_NACM[3] & Rep_Df$Score_NACM[4] > Rep_Df$CI_Lower_Lim_NACM[3]) {
        SigChange4c_NACM<- paste(Rep_Df$Change_NACM[4])
      }
      
      Time3<- paste0(Rep_Df$Date[3])
      Change_Rep_Df4b_NACM<- data.frame(Time3, SigChange4c_NACM)
      names(Change_Rep_Df4b_NACM)[2]<- paste0(Rep_Df$Date[4])    
  
  
  
kable(Change_Rep_Df4b_NACM, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_NACM[2] > Rep_Df$CI_Upper_Lim_NACM[1] | Rep_Df$Score_NACM[2] < Rep_Df$CI_Lower_Lim_NACM[1]) {
        SigChange2_NACM<- paste(Rep_Df$Change[2], "**")
      } else if(Rep_Df$Score_NACM[2] < Rep_Df$CI_Upper_Lim_NACM[1] & Rep_Df$Score_NACM[2] > Rep_Df$CI_Lower_Lim_NACM[1]) {
        SigChange2_NACM<- paste(Rep_Df$Change[2])
      }
      
      if(Rep_Df$Score_NACM[3] > Rep_Df$CI_Upper_Lim_NACM[1] | Rep_Df$Score_NACM[3] < Rep_Df$CI_Lower_Lim_NACM[1]) {
        SigChange3_NACM<- paste((Rep_Df$Score_NACM[3] - Rep_Df$Score_NACM[1]), "**")
      } else if(Rep_Df$Score_NACM[3] < Rep_Df$CI_Upper_Lim_NACM[1] & Rep_Df$Score_NACM[3] > Rep_Df$CI_Lower_Lim_NACM[1]) {
        SigChange3_NACM<- paste((Rep_Df$Score_NACM[3] - Rep_Df$Score_NACM[1]))
      }
      
      if(Rep_Df$Score_NACM[4] > Rep_Df$CI_Upper_Lim_NACM[1] | Rep_Df$Score_NACM[4] < Rep_Df$CI_Lower_Lim_NACM[1]) {
        SigChange4_NACM<- paste((Rep_Df$Score_NACM[4] - Rep_Df$Score_NACM[1]), "**")
      } else if(Rep_Df$Score_NACM[4] < Rep_Df$CI_Upper_Lim_NACM[1] & Rep_Df$Score_NACM[4] > Rep_Df$CI_Lower_Lim_NACM[1]) {
        SigChange4_NACM<- paste((Rep_Df$Score_NACM[4] - Rep_Df$Score_NACM[1]))
      }
      
      if(Rep_Df$Score_NACM[5] > Rep_Df$CI_Upper_Lim_NACM[1] | Rep_Df$Score_NACM[5] < Rep_Df$CI_Lower_Lim_NACM[1]) {
        SigChange5_NACM<- paste((Rep_Df$Score_NACM[5] - Rep_Df$Score_NACM[1]), "**")
      } else if(Rep_Df$Score_NACM[5] < Rep_Df$CI_Upper_Lim_NACM[1] & Rep_Df$Score_NACM[5] > Rep_Df$CI_Lower_Lim_NACM[1]) {
        SigChange5_NACM<- paste((Rep_Df$Score_NACM[5] - Rep_Df$Score_NACM[1]))
      }
      
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df5_NACM<- data.frame(Time1, SigChange2_NACM, SigChange3_NACM, SigChange4_NACM, SigChange5_NACM)
      names(Change_Rep_Df5_NACM)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df5_NACM)[3]<- paste0(Rep_Df$Date[3])
      names(Change_Rep_Df5_NACM)[4]<- paste0(Rep_Df$Date[4])
      names(Change_Rep_Df5_NACM)[5]<- paste0(Rep_Df$Date[5])  
  
  
kable(Change_Rep_Df5_NACM, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
 if(Rep_Df$Score_NACM[3] > Rep_Df$CI_Upper_Lim_NACM[2] | Rep_Df$Score_NACM[3] < Rep_Df$CI_Lower_Lim_NACM[2]) {
        SigChange5a_NACM<- paste(Rep_Df$Change_NACM[3], "**")
      } else if(Rep_Df$Score_NACM[3] < Rep_Df$CI_Upper_Lim_NACM[2] & Rep_Df$Score_NACM[3] > Rep_Df$CI_Lower_Lim_NACM[2]) {
        SigChange5a_NACM<- paste(Rep_Df$Change_NACM[3])
      }
      
      if(Rep_Df$Score_NACM[4] > Rep_Df$CI_Upper_Lim_NACM[2] | Rep_Df$Score_NACM[4] < Rep_Df$CI_Lower_Lim_NACM[2]) {
        SigChange5b_NACM<- paste((Rep_Df$Score_NACM[4] - Rep_Df$Score_NACM[2]), "**")
      } else if(Rep_Df$Score_NACM[4] < Rep_Df$CI_Upper_Lim_NACM[2] & Rep_Df$Score_NACM[4] > Rep_Df$CI_Lower_Lim_NACM[2]) {
        SigChange5b_NACM<- paste((Rep_Df$Score_NACM[4] - Rep_Df$Score_NACM[2]))
      }
      
      if(Rep_Df$Score_NACM[5] > Rep_Df$CI_Upper_Lim_NACM[2] | Rep_Df$Score_NACM[5] < Rep_Df$CI_Lower_Lim_NACM[2]) {
        SigChange5c_NACM<- paste((Rep_Df$Score_NACM[5] - Rep_Df$Score_NACM[2]), "**")
      } else if(Rep_Df$Score_NACM[5] < Rep_Df$CI_Upper_Lim_NACM[2] & Rep_Df$Score_NACM[5] > Rep_Df$CI_Lower_Lim_NACM[2]) {
        SigChange5c_NACM<- paste((Rep_Df$Score_NACM[5] - Rep_Df$Score_NACM[2]))
      }
      
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df5a_NACM<- data.frame(Time2, SigChange5a_NACM, SigChange5b_NACM, SigChange5c_NACM)
      names(Change_Rep_Df5a_NACM)[2]<- paste0(Rep_Df$Date[3])  
      names(Change_Rep_Df5a_NACM)[3]<- paste0(Rep_Df$Date[4]) 
      names(Change_Rep_Df5a_NACM)[4]<- paste0(Rep_Df$Date[5])   
  
kable(Change_Rep_Df5a_NACM, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
if(Rep_Df$Score_NACM[4] > Rep_Df$CI_Upper_Lim_NACM[3] | Rep_Df$Score_NACM[4] < Rep_Df$CI_Lower_Lim_NACM[3]) {
        SigChange5d_NACM<- paste(Rep_Df$Change_NACM[4], "**")
      } else if(Rep_Df$Score_NACM[4] < Rep_Df$CI_Upper_Lim_NACM[3] & Rep_Df$Score_NACM[4] > Rep_Df$CI_Lower_Lim_NACM[3]) {
        SigChange5d_NACM<- paste(Rep_Df$Change_NACM[4])
      }
      
      if(Rep_Df$Score_NACM[5] > Rep_Df$CI_Upper_Lim_NACM[3] | Rep_Df$Score_NACM[5] < Rep_Df$CI_Lower_Lim_NACM[3]) {
        SigChange5e_NACM<- paste((Rep_Df$Score_NACM[5] - Rep_Df$Score_NACM[3]), "**")
      } else if(Rep_Df$Score_NACM[5] < Rep_Df$CI_Upper_Lim_NACM[3] & Rep_Df$Score_NACM[5] > Rep_Df$CI_Lower_Lim_NACM[3]) {
        SigChange5e_NACM<- paste((Rep_Df$Score_NACM[5] - Rep_Df$Score_NACM[3]))
      }
      
      
      Time3<- paste0(Rep_Df$Date[3])
      Change_Rep_Df5b_NACM<- data.frame(Time3, SigChange5d_NACM, SigChange5e_NACM)
      names(Change_Rep_Df5b_NACM)[2]<- paste0(Rep_Df$Date[4])  
      names(Change_Rep_Df5b_NACM)[3]<- paste0(Rep_Df$Date[5])    
  
kable(Change_Rep_Df5b_NACM, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
 if(Rep_Df$Score_NACM[5] > Rep_Df$CI_Upper_Lim_NACM[4] | Rep_Df$Score_NACM[5] < Rep_Df$CI_Lower_Lim_NACM[4]) {
        SigChange5f_NACM<- paste(Rep_Df$Change_NACM[5], "**")
      } else if(Rep_Df$Score_NACM[5] < Rep_Df$CI_Upper_Lim_NACM[4] & Rep_Df$Score_NACM[5] > Rep_Df$CI_Lower_Lim_NACM[4]) {
        SigChange5f_NACM<- paste(Rep_Df$Change_NACM[5])
      }
      
      Time4<- paste0(Rep_Df$Date[4])
      Change_Rep_Df5c_NACM<- data.frame(Time4, SigChange5f_NACM)
      names(Change_Rep_Df5c_NACM)[2]<- paste0(Rep_Df$Date[5])   
  
kable(Change_Rep_Df5c_NACM, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

\newpage 

#Hyperarousal Subscale

##Response Summary

```{r, echo = FALSE, warning = FALSE, comment=NA}

Scores_Table_Hyperarousal<- Entered_Scores_Df[,c(1,29,30,31,32,33,34)]
names(Scores_Table_Hyperarousal)<-  c("Date", "Score", "Change", "Predicted Score", "Standard Error", "CI Upper Limit", "CI Lower Limit")
kable(Scores_Table_Hyperarousal, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T)
```

##Data Employed in Reliable Change Analyses

```{r, echo = FALSE, warning = FALSE, comment=NA}

Stats_Table_Hyperarousal<- kable(Stats_Table_Hyperarousal, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T) %>% row_spec(0, bold = T)

add_footnote(Stats_Table_Hyperarousal, c(paste("Source of Reference Population Mean and Sd:", Tab_Reference), paste("Source of Test-Retest Reliability: Ashbaugh, Houle-Johnson, El-Hage & Brunet (2016)")), notation = "number")
```

##Trend

```{r, echo = FALSE, warning=FALSE, comment=FALSE, message=FALSE, fig.width=9}

 p2<- ggplot(Entered_Scores_Df, aes(x=factor(Entered_Scores_Df$Date, levels = Entered_Scores_Df$Date), y=Entered_Scores_Df$Score_Hyperarousal, group = 1)) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Hyperarousal_1[1], linetype = paste(Cutoff_Names$Cutoff_Name_Hyperarousal_1[1],":",Entered_Scores_Df$Cutoff_Score_Hyperarousal_1[1])), color = "#827717", 
size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Hyperarousal_2[1], linetype = paste(Cutoff_Names$Cutoff_Name_Hyperarousal_2[1],":",Entered_Scores_Df$Cutoff_Score_Hyperarousal_2[1])), color = "#827717", size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Hyperarousal_3[1], linetype = paste(Cutoff_Names$Cutoff_Name_Hyperarousal_3[1],":",Entered_Scores_Df$Cutoff_Score_Hyperarousal_3[1])), color = "#827717", size = 0.4) + scale_linetype_manual(guide = guide_legend(reverse = TRUE), name = "Cut-Off Scores", values = c("dotted", "longdash", "solid"), limits = c(paste(Cutoff_Names$Cutoff_Name_Hyperarousal_1[1],":",Entered_Scores_Df$Cutoff_Score_Hyperarousal_1[1]),                                           paste(Cutoff_Names$Cutoff_Name_Hyperarousal_2[1],":",Entered_Scores_Df$Cutoff_Score_Hyperarousal_2[1]),                            paste(Cutoff_Names$Cutoff_Name_Hyperarousal_3[1],":",Entered_Scores_Df$Cutoff_Score_Hyperarousal_3[1]))) +
  geom_errorbar(aes(ymin=Entered_Scores_Df$CI_Lower_Lim_Hyperarousal, ymax=Entered_Scores_Df$CI_Upper_Lim_Hyperarousal), width=.2, size = 0.6,
                 position=position_dodge(0.05), color = "#d35400") + geom_line(color = "#00004c", size = 1) + geom_point(shape=23, fill="#00004c", color="#00004c", size=1.5) + geom_label_repel(aes(label = paste0("Change = ", Entered_Scores_Df$Change_Hyperarousal)), y = -10, segment.color = 'transparent', size = 3, family = "AvantGarde") + geom_label_repel(aes(label = paste0(Entered_Scores_Df$Score_Hyperarousal)), size = 3, family = "AvantGarde") 
  
p2<- p2+labs(x="Date", y = "Hyperarousal Score") +
theme_bw() + theme(panel.background = element_rect("#f1f1f1"), panel.grid.major = element_blank(), panel.grid.major.y = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + scale_y_continuous(limits = c(-10, 34), breaks = c(0,3,6,9,12,15,18,21,24), labels = c('0 Min','3','6','9','12','15','18','21','24 Max')) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=12, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=12, family = "AvantGarde", face = "bold"), legend.title=element_text(size=10, family = "AvantGarde"), legend.text=element_text(size=9, family = "AvantGarde"), text=element_text(size=12, family="AvantGarde")) 
print(p2)
```



##Score Differences Between All Pairs of Timepoints 
#####Statistically reliable change is indicated by **

```{r, echo = FALSE, warning = FALSE, comment=NA}


if(length(Entered_Scores_Df$Date) == 2) {  
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Hyperarousal[2] > Rep_Df$CI_Upper_Lim_Hyperarousal[1] | Rep_Df$Score_Hyperarousal[2] < Rep_Df$CI_Lower_Lim_Hyperarousal[1]) {
        SigChange2_Hyperarousal<- paste(Rep_Df$Change_Hyperarousal[2], "**")
      } else if(Rep_Df$Score_Hyperarousal[2] < Rep_Df$CI_Upper_Lim_Hyperarousal[1] & Rep_Df$Score_Hyperarousal[2] > Rep_Df$CI_Lower_Lim_Hyperarousal[1]) {
        SigChange2_Hyperarousal<- paste(Rep_Df$Change_Hyperarousal[2])
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df2_Hyperarousal<- data.frame(Time1, SigChange2_Hyperarousal)
      names(Change_Rep_Df2_Hyperarousal)[2]<- paste0(Rep_Df$Date[2])  
  

kable(Change_Rep_Df2_Hyperarousal, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
  
} 
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 3) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Hyperarousal[2] > Rep_Df$CI_Upper_Lim_Hyperarousal[1] | Rep_Df$Score_Hyperarousal[2] < Rep_Df$CI_Lower_Lim_Hyperarousal[1]) {
        SigChange2_Hyperarousal<- paste(Rep_Df$Change_Hyperarousal[2], "**")
      } else if(Rep_Df$Score_Hyperarousal[2] < Rep_Df$CI_Upper_Lim_Hyperarousal[1] & Rep_Df$Score_Hyperarousal[2] > Rep_Df$CI_Lower_Lim_Hyperarousal[1]) {
        SigChange2_Hyperarousal<- paste(Rep_Df$Change_Hyperarousal[2])
      }
      
      if(Rep_Df$Score_Hyperarousal[3] > Rep_Df$CI_Upper_Lim_Hyperarousal[1] | Rep_Df$Score_Hyperarousal[3] < Rep_Df$CI_Lower_Lim_Hyperarousal[1]) {
        SigChange3_Hyperarousal<- paste((Rep_Df$Score_Hyperarousal[3] - Rep_Df$Score_Hyperarousal[1]), "**")
      } else if(Rep_Df$Score_Hyperarousal[3] < Rep_Df$CI_Upper_Lim_Hyperarousal[1] & Rep_Df$Score_Hyperarousal[3] > Rep_Df$CI_Lower_Lim_Hyperarousal[1]) {
        SigChange3_Hyperarousal<- paste((Rep_Df$Score_Hyperarousal[3] - Rep_Df$Score_Hyperarousal[1]))
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df3_Hyperarousal<- data.frame(Time1, SigChange2, SigChange3)
      names(Change_Rep_Df3_Hyperarousal)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df3_Hyperarousal)[3]<- paste0(Rep_Df$Date[3])  
  
  
kable(Change_Rep_Df3_Hyperarousal, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 3) {

 if(Rep_Df$Score_Hyperarousal[3] > Rep_Df$CI_Upper_Lim_Hyperarousal[2] | Rep_Df$Score_Hyperarousal[3] < Rep_Df$CI_Lower_Lim_Hyperarousal[2]) {
        SigChange3a_Hyperarousal<- paste(Rep_Df$Change_Hyperarousal[3], "**")
      } else if(Rep_Df$Score_Hyperarousal[3] < Rep_Df$CI_Upper_Lim_Hyperarousal[2] & Rep_Df$Score_Hyperarousal[3] > Rep_Df$CI_Lower_Lim_Hyperarousal[2]) {
        SigChange3a_Hyperarousal<- paste(Rep_Df$Change_Hyperarousal[3])
      }
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df3a_Hyperarousal<- data.frame(Time2, SigChange3a_Hyperarousal)
      names(Change_Rep_Df3a_Hyperarousal)[2]<- paste0(Rep_Df$Date[3])  
  
  
kable(Change_Rep_Df3a_Hyperarousal, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)

}
  
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Hyperarousal[2] > Rep_Df$CI_Upper_Lim_Hyperarousal[1] | Rep_Df$Score_Hyperarousal[2] < Rep_Df$CI_Lower_Lim_Hyperarousal[1]) {
        SigChange2_Hyperarousal<- paste(Rep_Df$Change_Hyperarousal[2], "**")
      } else if(Rep_Df$Score_Hyperarousal[2] < Rep_Df$CI_Upper_Lim_Hyperarousal[1] & Rep_Df$Score_Hyperarousal[2] > Rep_Df$CI_Lower_Lim_Hyperarousal[1]) {
        SigChange2_Hyperarousal<- paste(Rep_Df$Change_Hyperarousal[2])
      }
      
      if(Rep_Df$Score_Hyperarousal[3] > Rep_Df$CI_Upper_Lim_Hyperarousal[1] | Rep_Df$Score_Hyperarousal[3] < Rep_Df$CI_Lower_Lim_Hyperarousal[1]) {
        SigChange3_Hyperarousal<- paste((Rep_Df$Score_Hyperarousal[3] - Rep_Df$Score_Hyperarousal[1]), "**")
      } else if(Rep_Df$Score_Hyperarousal[3] < Rep_Df$CI_Upper_Lim_Hyperarousal[1] & Rep_Df$Score_Hyperarousal[3] > Rep_Df$CI_Lower_Lim_Hyperarousal[1]) {
        SigChange3_Hyperarousal<- paste((Rep_Df$Score_Hyperarousal[3] - Rep_Df$Score_Hyperarousal[1]))
      }
      
      if(Rep_Df$Score_Hyperarousal[4] > Rep_Df$CI_Upper_Lim_Hyperarousal[1] | Rep_Df$Score_Hyperarousal[4] < Rep_Df$CI_Lower_Lim_Hyperarousal[1]) {
        SigChange4_Hyperarousal<- paste((Rep_Df$Score_Hyperarousal[4] - Rep_Df$Score_Hyperarousal[1]), "**")
      } else if(Rep_Df$Score_Hyperarousal[4] < Rep_Df$CI_Upper_Lim_Hyperarousal[1] & Rep_Df$Score_Hyperarousal[4] > Rep_Df$CI_Lower_Lim_Hyperarousal[1]) {
        SigChange4_Hyperarousal<- paste((Rep_Df$Score_Hyperarousal[4] - Rep_Df$Score_Hyperarousal[1]))
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df4_Hyperarousal<- data.frame(Time1, SigChange2_Hyperarousal, SigChange3_Hyperarousal, SigChange4_Hyperarousal)
      names(Change_Rep_Df4_Hyperarousal)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df4_Hyperarousal)[3]<- paste0(Rep_Df$Date[3])
      names(Change_Rep_Df4_Hyperarousal)[4]<- paste0(Rep_Df$Date[4])
      
  
kable(Change_Rep_Df4_Hyperarousal, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
if(Rep_Df$Score_Hyperarousal[3] > Rep_Df$CI_Upper_Lim_Hyperarousal[2] | Rep_Df$Score_Hyperarousal[3] < Rep_Df$CI_Lower_Lim_Hyperarousal[2]) {
        SigChange4a_Hyperarousal<- paste(Rep_Df$Change_Hyperarousal[3], "**")
      } else if(Rep_Df$Score_Hyperarousal[3] < Rep_Df$CI_Upper_Lim_Hyperarousal[2] & Rep_Df$Score_Hyperarousal[3] > Rep_Df$CI_Lower_Lim_Hyperarousal[2]) {
        SigChange4a_Hyperarousal<- paste(Rep_Df$Change_Hyperarousal[3])
      }
      
      if(Rep_Df$Score_Hyperarousal[4] > Rep_Df$CI_Upper_Lim_Hyperarousal[2] | Rep_Df$Score_Hyperarousal[4] < Rep_Df$CI_Lower_Lim_Hyperarousal[2]) {
        SigChange4b_Hyperarousal<- paste((Rep_Df$Score_Hyperarousal[4] - Rep_Df$Score_Hyperarousal[2]), "**")
      } else if(Rep_Df$Score_Hyperarousal[4] < Rep_Df$CI_Upper_Lim_Hyperarousal[2] & Rep_Df$Score_Hyperarousal[4] > Rep_Df$CI_Lower_Lim_Hyperarousal[2]) {
        SigChange4b_Hyperarousal<- paste((Rep_Df$Score_Hyperarousal[4] - Rep_Df$Score_Hyperarousal[2]))
      }
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df4a_Hyperarousal<- data.frame(Time2, SigChange4a_Hyperarousal, SigChange4b_Hyperarousal)
      names(Change_Rep_Df4a_Hyperarousal)[2]<- paste0(Rep_Df$Date[3])  
      names(Change_Rep_Df4a_Hyperarousal)[3]<- paste0(Rep_Df$Date[4])   
  
kable(Change_Rep_Df4a_Hyperarousal, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
    if(Rep_Df$Score_Hyperarousal[4] > Rep_Df$CI_Upper_Lim_Hyperarousal[3] | Rep_Df$Score_Hyperarousal[4] < Rep_Df$CI_Lower_Lim_Hyperarousal[3]) {
        SigChange4c_Hyperarousal<- paste(Rep_Df$Change_Hyperarousal[4], "**")
      } else if(Rep_Df$Score_Hyperarousal[4] < Rep_Df$CI_Upper_Lim_Hyperarousal[3] & Rep_Df$Score_Hyperarousal[4] > Rep_Df$CI_Lower_Lim_Hyperarousal[3]) {
        SigChange4c_Hyperarousal<- paste(Rep_Df$Change_Hyperarousal[4])
      }
      
      Time3<- paste0(Rep_Df$Date[3])
      Change_Rep_Df4b_Hyperarousal<- data.frame(Time3, SigChange4c_Hyperarousal)
      names(Change_Rep_Df4b_Hyperarousal)[2]<- paste0(Rep_Df$Date[4])    
  
  
kable(Change_Rep_Df4b_Hyperarousal, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Hyperarousal[2] > Rep_Df$CI_Upper_Lim_Hyperarousal[1] | Rep_Df$Score_Hyperarousal[2] < Rep_Df$CI_Lower_Lim_Hyperarousal[1]) {
        SigChange2_Hyperarousal<- paste(Rep_Df$Change_Hyperarousal[2], "**")
      } else if(Rep_Df$Score_Hyperarousal[2] < Rep_Df$CI_Upper_Lim_Hyperarousal[1] & Rep_Df$Score_Hyperarousal[2] > Rep_Df$CI_Lower_Lim_Hyperarousal[1]) {
        SigChange2_Hyperarousal<- paste(Rep_Df$Change_Hyperarousal[2])
      }
      
      if(Rep_Df$Score_Hyperarousal[3] > Rep_Df$CI_Upper_Lim_Hyperarousal[1] | Rep_Df$Score_Hyperarousal[3] < Rep_Df$CI_Lower_Lim_Hyperarousal[1]) {
        SigChange3_Hyperarousal<- paste((Rep_Df$Score_Hyperarousal[3] - Rep_Df$Score_Hyperarousal[1]), "**")
      } else if(Rep_Df$Score_Hyperarousal[3] < Rep_Df$CI_Upper_Lim_Hyperarousal[1] & Rep_Df$Score_Hyperarousal[3] > Rep_Df$CI_Lower_Lim_Hyperarousal[1]) {
        SigChange3_Hyperarousal<- paste((Rep_Df$Score_Hyperarousal[3] - Rep_Df$Score_Hyperarousal[1]))
      }
      
      if(Rep_Df$Score_Hyperarousal[4] > Rep_Df$CI_Upper_Lim_Hyperarousal[1] | Rep_Df$Score_Hyperarousal[4] < Rep_Df$CI_Lower_Lim_Hyperarousal[1]) {
        SigChange4_Hyperarousal<- paste((Rep_Df$Score_Hyperarousal[4] - Rep_Df$Score_Hyperarousal[1]), "**")
      } else if(Rep_Df$Score_Hyperarousal[4] < Rep_Df$CI_Upper_Lim_Hyperarousal[1] & Rep_Df$Score_Hyperarousal[4] > Rep_Df$CI_Lower_Lim_Hyperarousal[1]) {
        SigChange4_Hyperarousal<- paste((Rep_Df$Score_Hyperarousal[4] - Rep_Df$Score_Hyperarousal[1]))
      }
      
      if(Rep_Df$Score_Hyperarousal[5] > Rep_Df$CI_Upper_Lim_Hyperarousal[1] | Rep_Df$Score_Hyperarousal[5] < Rep_Df$CI_Lower_Lim_Hyperarousal[1]) {
        SigChange5_Hyperarousal<- paste((Rep_Df$Score_Hyperarousal[5] - Rep_Df$Score_Hyperarousal[1]), "**")
      } else if(Rep_Df$Score_Hyperarousal[5] < Rep_Df$CI_Upper_Lim_Hyperarousal[1] & Rep_Df$Score_Hyperarousal[5] > Rep_Df$CI_Lower_Lim_Hyperarousal[1]) {
        SigChange5_Hyperarousal<- paste((Rep_Df$Score_Hyperarousal[5] - Rep_Df$Score_Hyperarousal[1]))
      }
      
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df5_Hyperarousal<- data.frame(Time1, SigChange2_Hyperarousal, SigChange3_Hyperarousal, SigChange4_Hyperarousal, SigChange5_Hyperarousal)
      names(Change_Rep_Df5_Hyperarousal)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df5_Hyperarousal)[3]<- paste0(Rep_Df$Date[3])
      names(Change_Rep_Df5_Hyperarousal)[4]<- paste0(Rep_Df$Date[4])
      names(Change_Rep_Df5_Hyperarousal)[5]<- paste0(Rep_Df$Date[5])  
  
  
kable(Change_Rep_Df5_Hyperarousal, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
 if(Rep_Df$Score_Hyperarousal[3] > Rep_Df$CI_Upper_Lim_Hyperarousal[2] | Rep_Df$Score_Hyperarousal[3] < Rep_Df$CI_Lower_Lim_Hyperarousal[2]) {
        SigChange5a_Hyperarousal<- paste(Rep_Df$Change_Hyperarousal[3], "**")
      } else if(Rep_Df$Score_Hyperarousal[3] < Rep_Df$CI_Upper_Lim_Hyperarousal[2] & Rep_Df$Score_Hyperarousal[3] > Rep_Df$CI_Lower_Lim_Hyperarousal[2]) {
        SigChange5a_Hyperarousal<- paste(Rep_Df$Change_Hyperarousal[3])
      }
      
      if(Rep_Df$Score_Hyperarousal[4] > Rep_Df$CI_Upper_Lim_Hyperarousal[2] | Rep_Df$Score_Hyperarousal[4] < Rep_Df$CI_Lower_Lim_Hyperarousal[2]) {
        SigChange5b_Hyperarousal<- paste((Rep_Df$Score_Hyperarousal[4] - Rep_Df$Score_Hyperarousal[2]), "**")
      } else if(Rep_Df$Score_Hyperarousal[4] < Rep_Df$CI_Upper_Lim_Hyperarousal[2] & Rep_Df$Score_Hyperarousal[4] > Rep_Df$CI_Lower_Lim_Hyperarousal[2]) {
        SigChange5b_Hyperarousal<- paste((Rep_Df$Score_Hyperarousal[4] - Rep_Df$Score_Hyperarousal[2]))
      }
      
      if(Rep_Df$Score_Hyperarousal[5] > Rep_Df$CI_Upper_Lim_Hyperarousal[2] | Rep_Df$Score_Hyperarousal[5] < Rep_Df$CI_Lower_Lim_Hyperarousal[2]) {
        SigChange5c_Hyperarousal<- paste((Rep_Df$Score_Hyperarousal[5] - Rep_Df$Score_Hyperarousal[2]), "**")
      } else if(Rep_Df$Score_Hyperarousal[5] < Rep_Df$CI_Upper_Lim_Hyperarousal[2] & Rep_Df$Score_Hyperarousal[5] > Rep_Df$CI_Lower_Lim_Hyperarousal[2]) {
        SigChange5c_Hyperarousal<- paste((Rep_Df$Score_Hyperarousal[5] - Rep_Df$Score_Hyperarousal[2]))
      }
      
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df5a_Hyperarousal<- data.frame(Time2, SigChange5a_Hyperarousal, SigChange5b_Hyperarousal, SigChange5c_Hyperarousal)
      names(Change_Rep_Df5a_Hyperarousal)[2]<- paste0(Rep_Df$Date[3])  
      names(Change_Rep_Df5a_Hyperarousal)[3]<- paste0(Rep_Df$Date[4]) 
      names(Change_Rep_Df5a_Hyperarousal)[4]<- paste0(Rep_Df$Date[5])   
  
kable(Change_Rep_Df5a_Hyperarousal, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
if(Rep_Df$Score_Hyperarousal[4] > Rep_Df$CI_Upper_Lim_Hyperarousal[3] | Rep_Df$Score_Hyperarousal[4] < Rep_Df$CI_Lower_Lim_Hyperarousal[3]) {
        SigChange5d_Hyperarousal<- paste(Rep_Df$Change_Hyperarousal[4], "**")
      } else if(Rep_Df$Score_Hyperarousal[4] < Rep_Df$CI_Upper_Lim_Hyperarousal[3] & Rep_Df$Score_Hyperarousal[4] > Rep_Df$CI_Lower_Lim_Hyperarousal[3]) {
        SigChange5d_Hyperarousal<- paste(Rep_Df$Change_Hyperarousal[4])
      }
      
      if(Rep_Df$Score_Hyperarousal[5] > Rep_Df$CI_Upper_Lim_Hyperarousal[3] | Rep_Df$Score_Hyperarousal[5] < Rep_Df$CI_Lower_Lim_Hyperarousal[3]) {
        SigChange5e_Hyperarousal<- paste((Rep_Df$Score_Hyperarousal[5] - Rep_Df$Score_Hyperarousal[3]), "**")
      } else if(Rep_Df$Score_Hyperarousal[5] < Rep_Df$CI_Upper_Lim_Hyperarousal[3] & Rep_Df$Score_Hyperarousal[5] > Rep_Df$CI_Lower_Lim_Hyperarousal[3]) {
        SigChange5e_Hyperarousal<- paste((Rep_Df$Score_Hyperarousal[5] - Rep_Df$Score_Hyperarousal[3]))
      }
      
      
      Time3<- paste0(Rep_Df$Date[3])
      Change_Rep_Df5b_Hyperarousal<- data.frame(Time3, SigChange5d_Hyperarousal, SigChange5e_Hyperarousal)
      names(Change_Rep_Df5b_Hyperarousal)[2]<- paste0(Rep_Df$Date[4])  
      names(Change_Rep_Df5b_Hyperarousal)[3]<- paste0(Rep_Df$Date[5])    
  
kable(Change_Rep_Df5b_Hyperarousal, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
 if(Rep_Df$Score_Hyperarousal[5] > Rep_Df$CI_Upper_Lim_Hyperarousal[4] | Rep_Df$Score_Hyperarousal[5] < Rep_Df$CI_Lower_Lim_Hyperarousal[4]) {
        SigChange5f_Hyperarousal<- paste(Rep_Df$Change_Hyperarousal[5], "**")
      } else if(Rep_Df$Score_Hyperarousal[5] < Rep_Df$CI_Upper_Lim_Hyperarousal[4] & Rep_Df$Score_Hyperarousal[5] > Rep_Df$CI_Lower_Lim_Hyperarousal[4]) {
        SigChange5f_Hyperarousal<- paste(Rep_Df$Change_Hyperarousal[5])
      }
      
      Time4<- paste0(Rep_Df$Date[4])
      Change_Rep_Df5c_Hyperarousal<- data.frame(Time4, SigChange5f_Hyperarousal)
      names(Change_Rep_Df5c_Hyperarousal)[2]<- paste0(Rep_Df$Date[5])   
  
kable(Change_Rep_Df5c_Hyperarousal, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```


\newpage


#Avoidance Subscale

##Response Summary

```{r, echo = FALSE, warning = FALSE, comment=NA}

Scores_Table_Avoidance<- Entered_Scores_Df[,c(1,38,39,40,41,42,43)]
names(Scores_Table_Avoidance)<-  c("Date", "Score", "Change", "Predicted Score", "Standard Error", "CI Upper Limit", "CI Lower Limit")
kable(Scores_Table_Avoidance, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T)
```

##Data Employed in Reliable Change Analyses

```{r, echo = FALSE, warning = FALSE, comment=NA}

Stats_Table_Avoidance<- kable(Stats_Table_Avoidance, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T) %>% row_spec(0, bold = T)

add_footnote(Stats_Table_Avoidance, c(paste("Source of Reference Population Mean and Sd:", Tab_Reference), paste("Source of Test-Retest Reliability: Ashbaugh, Houle-Johnson, El-Hage & Brunet (2016)")), notation = "number")
```

##Trend

```{r, echo = FALSE, warning=FALSE, comment=FALSE, message=FALSE, fig.width=9}

 p2<- ggplot(Entered_Scores_Df, aes(x=factor(Entered_Scores_Df$Date, levels = Entered_Scores_Df$Date), y=Entered_Scores_Df$Score_Avoidance, group = 1)) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Avoidance_1[1], linetype = paste(Cutoff_Names$Cutoff_Name_Avoidance_1[1],":",Entered_Scores_Df$Cutoff_Score_Avoidance_1[1])), color = "#827717", 
size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Avoidance_2[1], linetype = paste(Cutoff_Names$Cutoff_Name_Avoidance_2[1],":",Entered_Scores_Df$Cutoff_Score_Avoidance_2[1])), color = "#827717", size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Avoidance_3[1], linetype = paste(Cutoff_Names$Cutoff_Name_Avoidance_3[1],":",Entered_Scores_Df$Cutoff_Score_Avoidance_3[1])), color = "#827717", size = 0.4) +
  scale_linetype_manual(guide = guide_legend(reverse = TRUE), name = "Cut-Off Scores", values = c("dotted", "longdash", "solid"), limits = c(paste(Cutoff_Names$Cutoff_Name_Avoidance_1[1],":",Entered_Scores_Df$Cutoff_Score_Avoidance_1[1]),                                  paste(Cutoff_Names$Cutoff_Name_Avoidance_2[1],":",Entered_Scores_Df$Cutoff_Score_Avoidance_2[1]),                                  paste(Cutoff_Names$Cutoff_Name_Avoidance_3[1],":",Entered_Scores_Df$Cutoff_Score_Avoidance_3[1]))) +
  geom_errorbar(aes(ymin=Entered_Scores_Df$CI_Lower_Lim_Avoidance, ymax=Entered_Scores_Df$CI_Upper_Lim_Avoidance), width=.2, size = 0.6,
                 position=position_dodge(0.05), color = "#d35400") + geom_line(color = "#00004c", size = 1) + geom_point(shape=23, fill="#00004c", color="#00004c", size=1.5) + geom_label_repel(aes(label = paste0("Change = ", Entered_Scores_Df$Change_Avoidance)), y = -10, segment.color = 'transparent', size = 3, family = "AvantGarde") + geom_label_repel(aes(label = paste0(Entered_Scores_Df$Score_Avoidance)), size = 3, family = "AvantGarde")
  
p2<- p2+labs(x="Date", y = "Avoidance Score") +
theme_bw() + theme(panel.background = element_rect("#f1f1f1"), panel.grid.major = element_blank(), panel.grid.major.y = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + scale_y_continuous(limits = c(-10, 18), breaks = c(0,2,4,6,8), labels = c('0 Min','2','4','6','8 Max')) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=12, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=12, family = "AvantGarde", face = "bold"), legend.title=element_text(size=10, family = "AvantGarde"), legend.text=element_text(size=9, family = "AvantGarde"), text=element_text(size=12, family="AvantGarde")) 
print(p2)
```



##Score Differences Between All Pairs of Timepoints 
#####Statistically reliable change is indicated by **

```{r, echo = FALSE, warning = FALSE, comment=NA}


if(length(Entered_Scores_Df$Date) == 2) {  
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Avoidance[2] > Rep_Df$CI_Upper_Lim_Avoidance[1] | Rep_Df$Score_Avoidance[2] < Rep_Df$CI_Lower_Lim_Avoidance[1]) {
        SigChange2_Avoidance<- paste(Rep_Df$Change_Avoidance[2], "**")
      } else if(Rep_Df$Score_Avoidance[2] < Rep_Df$CI_Upper_Lim_Avoidance[1] & Rep_Df$Score_Avoidance[2] > Rep_Df$CI_Lower_Lim_Avoidance[1]) {
        SigChange2_Avoidance<- paste(Rep_Df$Change_Avoidance[2])
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df2_Avoidance<- data.frame(Time1, SigChange2_Avoidance)
      names(Change_Rep_Df2_Avoidance)[2]<- paste0(Rep_Df$Date[2])  
  

kable(Change_Rep_Df2_Avoidance, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
  
} 
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 3) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Avoidance[2] > Rep_Df$CI_Upper_Lim_Avoidance[1] | Rep_Df$Score_Avoidance[2] < Rep_Df$CI_Lower_Lim_Avoidance[1]) {
        SigChange2_Avoidance<- paste(Rep_Df$Change_Avoidance[2], "**")
      } else if(Rep_Df$Score_Avoidance[2] < Rep_Df$CI_Upper_Lim_Avoidance[1] & Rep_Df$Score_Avoidance[2] > Rep_Df$CI_Lower_Lim_Avoidance[1]) {
        SigChange2_Avoidance<- paste(Rep_Df$Change_Avoidance[2])
      }
      
      if(Rep_Df$Score_Avoidance[3] > Rep_Df$CI_Upper_Lim_Avoidance[1] | Rep_Df$Score_Avoidance[3] < Rep_Df$CI_Lower_Lim_Avoidance[1]) {
        SigChange3_Avoidance<- paste((Rep_Df$Score_Avoidance[3] - Rep_Df$Score_Avoidance[1]), "**")
      } else if(Rep_Df$Score_Avoidance[3] < Rep_Df$CI_Upper_Lim_Avoidance[1] & Rep_Df$Score_Avoidance[3] > Rep_Df$CI_Lower_Lim_Avoidance[1]) {
        SigChange3_Avoidance<- paste((Rep_Df$Score_Avoidance[3] - Rep_Df$Score_Avoidance[1]))
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df3_Avoidance<- data.frame(Time1, SigChange2, SigChange3)
      names(Change_Rep_Df3_Avoidance)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df3_Avoidance)[3]<- paste0(Rep_Df$Date[3])  
  
  
kable(Change_Rep_Df3_Avoidance, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 3) {

 if(Rep_Df$Score_Avoidance[3] > Rep_Df$CI_Upper_Lim_Avoidance[2] | Rep_Df$Score_Avoidance[3] < Rep_Df$CI_Lower_Lim_Avoidance[2]) {
        SigChange3a_Avoidance<- paste(Rep_Df$Change_Avoidance[3], "**")
      } else if(Rep_Df$Score_Avoidance[3] < Rep_Df$CI_Upper_Lim_Avoidance[2] & Rep_Df$Score_Avoidance[3] > Rep_Df$CI_Lower_Lim_Avoidance[2]) {
        SigChange3a_Avoidance<- paste(Rep_Df$Change_Avoidance[3])
      }
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df3a_Avoidance<- data.frame(Time2, SigChange3a_Avoidance)
      names(Change_Rep_Df3a_Avoidance)[2]<- paste0(Rep_Df$Date[3])  
  
  
kable(Change_Rep_Df3a_Avoidance, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)

}
  
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Avoidance[2] > Rep_Df$CI_Upper_Lim_Avoidance[1] | Rep_Df$Score_Avoidance[2] < Rep_Df$CI_Lower_Lim_Avoidance[1]) {
        SigChange2_Avoidance<- paste(Rep_Df$Change_Avoidance[2], "**")
      } else if(Rep_Df$Score_Avoidance[2] < Rep_Df$CI_Upper_Lim_Avoidance[1] & Rep_Df$Score_Avoidance[2] > Rep_Df$CI_Lower_Lim_Avoidance[1]) {
        SigChange2_Avoidance<- paste(Rep_Df$Change_Avoidance[2])
      }
      
      if(Rep_Df$Score_Avoidance[3] > Rep_Df$CI_Upper_Lim_Avoidance[1] | Rep_Df$Score_Avoidance[3] < Rep_Df$CI_Lower_Lim_Avoidance[1]) {
        SigChange3_Avoidance<- paste((Rep_Df$Score_Avoidance[3] - Rep_Df$Score_Avoidance[1]), "**")
      } else if(Rep_Df$Score_Avoidance[3] < Rep_Df$CI_Upper_Lim_Avoidance[1] & Rep_Df$Score_Avoidance[3] > Rep_Df$CI_Lower_Lim_Avoidance[1]) {
        SigChange3_Avoidance<- paste((Rep_Df$Score_Avoidance[3] - Rep_Df$Score_Avoidance[1]))
      }
      
      if(Rep_Df$Score_Avoidance[4] > Rep_Df$CI_Upper_Lim_Avoidance[1] | Rep_Df$Score_Avoidance[4] < Rep_Df$CI_Lower_Lim_Avoidance[1]) {
        SigChange4_Avoidance<- paste((Rep_Df$Score_Avoidance[4] - Rep_Df$Score_Avoidance[1]), "**")
      } else if(Rep_Df$Score_Avoidance[4] < Rep_Df$CI_Upper_Lim_Avoidance[1] & Rep_Df$Score_Avoidance[4] > Rep_Df$CI_Lower_Lim_Avoidance[1]) {
        SigChange4_Avoidance<- paste((Rep_Df$Score_Avoidance[4] - Rep_Df$Score_Avoidance[1]))
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df4_Avoidance<- data.frame(Time1, SigChange2_Avoidance, SigChange3_Avoidance, SigChange4_Avoidance)
      names(Change_Rep_Df4_Avoidance)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df4_Avoidance)[3]<- paste0(Rep_Df$Date[3])
      names(Change_Rep_Df4_Avoidance)[4]<- paste0(Rep_Df$Date[4])
      
  
kable(Change_Rep_Df4_Avoidance, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
if(Rep_Df$Score_Avoidance[3] > Rep_Df$CI_Upper_Lim_Avoidance[2] | Rep_Df$Score_Avoidance[3] < Rep_Df$CI_Lower_Lim_Avoidance[2]) {
        SigChange4a_Avoidance<- paste(Rep_Df$Change_Avoidance[3], "**")
      } else if(Rep_Df$Score_Avoidance[3] < Rep_Df$CI_Upper_Lim_Avoidance[2] & Rep_Df$Score_Avoidance[3] > Rep_Df$CI_Lower_Lim_Avoidance[2]) {
        SigChange4a_Avoidance<- paste(Rep_Df$Change_Avoidance[3])
      }
      
      if(Rep_Df$Score_Avoidance[4] > Rep_Df$CI_Upper_Lim_Avoidance[2] | Rep_Df$Score_Avoidance[4] < Rep_Df$CI_Lower_Lim_Avoidance[2]) {
        SigChange4b_Avoidance<- paste((Rep_Df$Score_Avoidance[4] - Rep_Df$Score_Avoidance[2]), "**")
      } else if(Rep_Df$Score_Avoidance[4] < Rep_Df$CI_Upper_Lim_Avoidance[2] & Rep_Df$Score_Avoidance[4] > Rep_Df$CI_Lower_Lim_Avoidance[2]) {
        SigChange4b_Avoidance<- paste((Rep_Df$Score_Avoidance[4] - Rep_Df$Score_Avoidance[2]))
      }
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df4a_Avoidance<- data.frame(Time2, SigChange4a_Avoidance, SigChange4b_Avoidance)
      names(Change_Rep_Df4a_Avoidance)[2]<- paste0(Rep_Df$Date[3])  
      names(Change_Rep_Df4a_Avoidance)[3]<- paste0(Rep_Df$Date[4])   
  
kable(Change_Rep_Df4a_Avoidance, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
    if(Rep_Df$Score_Avoidance[4] > Rep_Df$CI_Upper_Lim_Avoidance[3] | Rep_Df$Score_Avoidance[4] < Rep_Df$CI_Lower_Lim_Avoidance[3]) {
        SigChange4c_Avoidance<- paste(Rep_Df$Change_Avoidance[4], "**")
      } else if(Rep_Df$Score_Avoidance[4] < Rep_Df$CI_Upper_Lim_Avoidance[3] & Rep_Df$Score_Avoidance[4] > Rep_Df$CI_Lower_Lim_Avoidance[3]) {
        SigChange4c_Avoidance<- paste(Rep_Df$Change_Avoidance[4])
      }
      
      Time3<- paste0(Rep_Df$Date[3])
      Change_Rep_Df4b_Avoidance<- data.frame(Time3, SigChange4c_Avoidance)
      names(Change_Rep_Df4b_Avoidance)[2]<- paste0(Rep_Df$Date[4])    
  
  
kable(Change_Rep_Df4b_Avoidance, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Avoidance[2] > Rep_Df$CI_Upper_Lim_Avoidance[1] | Rep_Df$Score_Avoidance[2] < Rep_Df$CI_Lower_Lim_Avoidance[1]) {
        SigChange2_Avoidance<- paste(Rep_Df$Change_Avoidance[2], "**")
      } else if(Rep_Df$Score_Avoidance[2] < Rep_Df$CI_Upper_Lim_Avoidance[1] & Rep_Df$Score_Avoidance[2] > Rep_Df$CI_Lower_Lim_Avoidance[1]) {
        SigChange2_Avoidance<- paste(Rep_Df$Change_Avoidance[2])
      }
      
      if(Rep_Df$Score_Avoidance[3] > Rep_Df$CI_Upper_Lim_Avoidance[1] | Rep_Df$Score_Avoidance[3] < Rep_Df$CI_Lower_Lim_Avoidance[1]) {
        SigChange3_Avoidance<- paste((Rep_Df$Score_Avoidance[3] - Rep_Df$Score_Avoidance[1]), "**")
      } else if(Rep_Df$Score_Avoidance[3] < Rep_Df$CI_Upper_Lim_Avoidance[1] & Rep_Df$Score_Avoidance[3] > Rep_Df$CI_Lower_Lim_Avoidance[1]) {
        SigChange3_Avoidance<- paste((Rep_Df$Score_Avoidance[3] - Rep_Df$Score_Avoidance[1]))
      }
      
      if(Rep_Df$Score_Avoidance[4] > Rep_Df$CI_Upper_Lim_Avoidance[1] | Rep_Df$Score_Avoidance[4] < Rep_Df$CI_Lower_Lim_Avoidance[1]) {
        SigChange4_Avoidance<- paste((Rep_Df$Score_Avoidance[4] - Rep_Df$Score_Avoidance[1]), "**")
      } else if(Rep_Df$Score_Avoidance[4] < Rep_Df$CI_Upper_Lim_Avoidance[1] & Rep_Df$Score_Avoidance[4] > Rep_Df$CI_Lower_Lim_Avoidance[1]) {
        SigChange4_Avoidance<- paste((Rep_Df$Score_Avoidance[4] - Rep_Df$Score_Avoidance[1]))
      }
      
      if(Rep_Df$Score_Avoidance[5] > Rep_Df$CI_Upper_Lim_Avoidance[1] | Rep_Df$Score_Avoidance[5] < Rep_Df$CI_Lower_Lim_Avoidance[1]) {
        SigChange5_Avoidance<- paste((Rep_Df$Score_Avoidance[5] - Rep_Df$Score_Avoidance[1]), "**")
      } else if(Rep_Df$Score_Avoidance[5] < Rep_Df$CI_Upper_Lim_Avoidance[1] & Rep_Df$Score_Avoidance[5] > Rep_Df$CI_Lower_Lim_Avoidance[1]) {
        SigChange5_Avoidance<- paste((Rep_Df$Score_Avoidance[5] - Rep_Df$Score_Avoidance[1]))
      }
      
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df5_Avoidance<- data.frame(Time1, SigChange2_Avoidance, SigChange3_Avoidance, SigChange4_Avoidance, SigChange5_Avoidance)
      names(Change_Rep_Df5_Avoidance)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df5_Avoidance)[3]<- paste0(Rep_Df$Date[3])
      names(Change_Rep_Df5_Avoidance)[4]<- paste0(Rep_Df$Date[4])
      names(Change_Rep_Df5_Avoidance)[5]<- paste0(Rep_Df$Date[5])  
  
  
kable(Change_Rep_Df5_Avoidance, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
 if(Rep_Df$Score_Avoidance[3] > Rep_Df$CI_Upper_Lim_Avoidance[2] | Rep_Df$Score_Avoidance[3] < Rep_Df$CI_Lower_Lim_Avoidance[2]) {
        SigChange5a_Avoidance<- paste(Rep_Df$Change_Avoidance[3], "**")
      } else if(Rep_Df$Score_Avoidance[3] < Rep_Df$CI_Upper_Lim_Avoidance[2] & Rep_Df$Score_Avoidance[3] > Rep_Df$CI_Lower_Lim_Avoidance[2]) {
        SigChange5a_Avoidance<- paste(Rep_Df$Change_Avoidance[3])
      }
      
      if(Rep_Df$Score_Avoidance[4] > Rep_Df$CI_Upper_Lim_Avoidance[2] | Rep_Df$Score_Avoidance[4] < Rep_Df$CI_Lower_Lim_Avoidance[2]) {
        SigChange5b_Avoidance<- paste((Rep_Df$Score_Avoidance[4] - Rep_Df$Score_Avoidance[2]), "**")
      } else if(Rep_Df$Score_Avoidance[4] < Rep_Df$CI_Upper_Lim_Avoidance[2] & Rep_Df$Score_Avoidance[4] > Rep_Df$CI_Lower_Lim_Avoidance[2]) {
        SigChange5b_Avoidance<- paste((Rep_Df$Score_Avoidance[4] - Rep_Df$Score_Avoidance[2]))
      }
      
      if(Rep_Df$Score_Avoidance[5] > Rep_Df$CI_Upper_Lim_Avoidance[2] | Rep_Df$Score_Avoidance[5] < Rep_Df$CI_Lower_Lim_Avoidance[2]) {
        SigChange5c_Avoidance<- paste((Rep_Df$Score_Avoidance[5] - Rep_Df$Score_Avoidance[2]), "**")
      } else if(Rep_Df$Score_Avoidance[5] < Rep_Df$CI_Upper_Lim_Avoidance[2] & Rep_Df$Score_Avoidance[5] > Rep_Df$CI_Lower_Lim_Avoidance[2]) {
        SigChange5c_Avoidance<- paste((Rep_Df$Score_Avoidance[5] - Rep_Df$Score_Avoidance[2]))
      }
      
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df5a_Avoidance<- data.frame(Time2, SigChange5a_Avoidance, SigChange5b_Avoidance, SigChange5c_Avoidance)
      names(Change_Rep_Df5a_Avoidance)[2]<- paste0(Rep_Df$Date[3])  
      names(Change_Rep_Df5a_Avoidance)[3]<- paste0(Rep_Df$Date[4]) 
      names(Change_Rep_Df5a_Avoidance)[4]<- paste0(Rep_Df$Date[5])   
  
kable(Change_Rep_Df5a_Avoidance, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
if(Rep_Df$Score_Avoidance[4] > Rep_Df$CI_Upper_Lim_Avoidance[3] | Rep_Df$Score_Avoidance[4] < Rep_Df$CI_Lower_Lim_Avoidance[3]) {
        SigChange5d_Avoidance<- paste(Rep_Df$Change_Avoidance[4], "**")
      } else if(Rep_Df$Score_Avoidance[4] < Rep_Df$CI_Upper_Lim_Avoidance[3] & Rep_Df$Score_Avoidance[4] > Rep_Df$CI_Lower_Lim_Avoidance[3]) {
        SigChange5d_Avoidance<- paste(Rep_Df$Change_Avoidance[4])
      }
      
      if(Rep_Df$Score_Avoidance[5] > Rep_Df$CI_Upper_Lim_Avoidance[3] | Rep_Df$Score_Avoidance[5] < Rep_Df$CI_Lower_Lim_Avoidance[3]) {
        SigChange5e_Avoidance<- paste((Rep_Df$Score_Avoidance[5] - Rep_Df$Score_Avoidance[3]), "**")
      } else if(Rep_Df$Score_Avoidance[5] < Rep_Df$CI_Upper_Lim_Avoidance[3] & Rep_Df$Score_Avoidance[5] > Rep_Df$CI_Lower_Lim_Avoidance[3]) {
        SigChange5e_Avoidance<- paste((Rep_Df$Score_Avoidance[5] - Rep_Df$Score_Avoidance[3]))
      }
      
      
      Time3<- paste0(Rep_Df$Date[3])
      Change_Rep_Df5b_Avoidance<- data.frame(Time3, SigChange5d_Avoidance, SigChange5e_Avoidance)
      names(Change_Rep_Df5b_Avoidance)[2]<- paste0(Rep_Df$Date[4])  
      names(Change_Rep_Df5b_Avoidance)[3]<- paste0(Rep_Df$Date[5])    
  
kable(Change_Rep_Df5b_Avoidance, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
 if(Rep_Df$Score_Avoidance[5] > Rep_Df$CI_Upper_Lim_Avoidance[4] | Rep_Df$Score_Avoidance[5] < Rep_Df$CI_Lower_Lim_Avoidance[4]) {
        SigChange5f_Avoidance<- paste(Rep_Df$Change_Avoidance[5], "**")
      } else if(Rep_Df$Score_Avoidance[5] < Rep_Df$CI_Upper_Lim_Avoidance[4] & Rep_Df$Score_Avoidance[5] > Rep_Df$CI_Lower_Lim_Avoidance[4]) {
        SigChange5f_Avoidance<- paste(Rep_Df$Change_Avoidance[5])
      }
      
      Time4<- paste0(Rep_Df$Date[4])
      Change_Rep_Df5c_Avoidance<- data.frame(Time4, SigChange5f_Avoidance)
      names(Change_Rep_Df5c_Avoidance)[2]<- paste0(Rep_Df$Date[5])   
  
kable(Change_Rep_Df5c_Avoidance, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```


\newpage


#Most Recent Item Scores

#`r Scores_Table[nrow(Scores_Table),1]`

```{r,echo=FALSE,warning=FALSE,comment=NA}

kable(Item_Df, format = "latex", booktabs = T) %>% kable_styling(position = "left", full_width = T, font_size = 12, latex_options = "striped") %>% row_spec(0, bold = T)
```

\newpage 

\begingroup\Large

\begin{center} \textbf{Information About The PTSD Checklist for DSM-5 (PCL-5)} \end{center} 

#What it Measures: 

* The 20 symptoms of Post-Traumatic Stress Disorder, as outlined in the Diagnostic & Statistical Manual of Psychological Disorders, 5th Edition (DSM-5).


* Re-experiencing symptoms, such as involuntary distressing dreams, memories, thoughts and feelings related to a traumatic event(s).


* Avoidance symptoms, such as efforts to avoid internal or external reminders of the traumatic event(s)


* Negative alterations in cognitions and mood, such as negative mood states, lack of positive emotions, and exaggerated negative beliefs about onself, the world, and others. 

* Hyperarousal symptoms, such as hypervigilance, exaggerated startle response, sleep difficulties, irritability and concentration problems.


#What Higher Scores Mean:

* More severe PTSD symptomatology. 


* A provisional diagnosis of PTSD may be made if scores are sufficiently elevated. The optimal cut-off score will vary according to the service and population. As a general guideline, cut-off scores of **38** (Weathers et al., 2013) and **33** (Bovin et al., 2015) have been endorsed as sufficient for a provisional PTSD diagnosis. 


#Scale Quality:

* The PCL-5 has undergone extensive psychometric validation, and is one of the most widely used self-report screening measures for PTSD (for a review see McDonald & Calhoun, 2010). 


#Scale Structure:

* 20 items.


* 5-point Likert Scale. 


* Respondents are asked to what extent (0 = "Not at all"; 4 = "Extremely") they have been bothered by each symptom during the past month (e.g. "Repeated, disturbing and unwanted memories of the stressful experience").


* Although the recommended PCL-5 method of scoring is based on a 4-factor structure (consistent with DSM-5 criteria), studies have consistently shown that a 6- or 7-factor solution provides a better fit to the data (Armour, Contractor, Shea, Elhai & Pietrzak, 2016; Ashbaugh, Houle-Johnson, Herbert, El-Hage & Brunet, 2016; Blevins, Weathers, Davis, Witte & Domino, 2015; Bovin et al., 2015; Clark et al., 2016, Seligowski & Orcutt, 2015). 

\endgroup
