---
title: "Depression Anxiety Stress Scales - 21 (DASS-21)"
author: "Report generated by PsychlytX"
date: "`r format(Sys.time(), '%d %B, %Y')`"
geometry: "left=2cm,right=2cm,top=1.5cm,bottom=1.2cm"
output:
  pdf_document:
    latex_engine: pdflatex
header-includes:
- \usepackage[fontsize=7.8pt]{scrextend}
- \usepackage{color}
- \usepackage{booktabs}
- \usepackage[table]{xcolor}
fontfamily: arev
always_allow_html: yes
params:
PN: 'NULL' 
CN: 'NULL'
Stats_Table_Fullscale: 'NULL'
Tab_Reference: 'NULL'
Stats_Table_Depression: 'NULL'
Stats_Table_Anxiety: 'NULL'
Stats_Table_Stress: 'NULL'
Entered_Scores_Df: 'NULL'
Cutoff_Names: 'NULL'
Item_Df: 'NULL'
subtitle: '**Patient:** `r PN` **|** **Clinician:** `r CN`'
---

```{r,echo = FALSE,warning=FALSE,comment = NA}
knitr::opts_chunk$set(fig.width=7,fig.height=3) 

```

#DASS-21 Total Scale: General Psychological Distress

##Response Summary

```{r,echo=FALSE,warning=FALSE,comment=NA}
Scores_Table<- Entered_Scores_Df[,c(1,2,3,4,5,6,7)]
names(Scores_Table)<- c("Date", "Score", "Change", "Predicted Score", "Standard Error", "CI Upper Limit", "CI Lower Limit")
kable(Scores_Table, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T)
```


##Data Employed in Reliable Change Analyses

```{r,echo=FALSE,warning=FALSE,comment=NA}

Stats_Table_Fullscale<- kable(Stats_Table_Fullscale, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T) %>% row_spec(0, bold = T)

add_footnote(Stats_Table_Fullscale, c(paste("Source of Reference Population Mean and Sd:", Tab_Reference), paste("Source of Reliability (value is Cronbach's Alpha not test-retest reliability): Crawford, Garthwaite, Lawrie, Henry, MacDonald, Sutherland & Sinha (2009)")), notation = "number")
```


##Trend

```{r,echo=FALSE,warning=FALSE,comment=FALSE,message=FALSE, fig.width=8}
 p1<- ggplot(Entered_Scores_Df, aes(x=factor(Entered_Scores_Df$Date, levels = Entered_Scores_Df$Date), y=Entered_Scores_Df$Score, group = 1)) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_1[1], linetype = paste(Cutoff_Names$Cutoff_Name_1[1],":",Entered_Scores_Df$Cutoff_Score_1[1])), color = "#827717", 
size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_2[1], linetype = paste(Cutoff_Names$Cutoff_Name_2[1],":",Entered_Scores_Df$Cutoff_Score_2[1])), color = "#827717", size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_3[1], linetype = paste(Cutoff_Names$Cutoff_Name_3[1],":",Entered_Scores_Df$Cutoff_Score_3[1])), color = "#827717", size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_4[1], linetype = paste(Cutoff_Names$Cutoff_Name_4[1],":",Entered_Scores_Df$Cutoff_Score_4[1])), color = "#827717", size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_5[1], linetype = paste(Cutoff_Names$Cutoff_Name_5[1],":",Entered_Scores_Df$Cutoff_Score_5[1])), color = "#827717", size = 0.4) + scale_linetype_manual(guide = guide_legend(reverse = TRUE), name = "Cut-Off Scores", values = c("ff","8f","1f","11","solid"), limits = c(paste(Cutoff_Names$Cutoff_Name_1[1],":",Entered_Scores_Df$Cutoff_Score_1[1]),
          paste(Cutoff_Names$Cutoff_Name_2[1],":",Entered_Scores_Df$Cutoff_Score_2[1]),
          paste(Cutoff_Names$Cutoff_Name_3[1],":",Entered_Scores_Df$Cutoff_Score_3[1]),
           paste(Cutoff_Names$Cutoff_Name_4[1],":",Entered_Scores_Df$Cutoff_Score_4[1]),
           paste(Cutoff_Names$Cutoff_Name_5[1],":",Entered_Scores_Df$Cutoff_Score_5[1])
          )) + geom_errorbar(aes(ymin=Entered_Scores_Df$CI_Lower_Lim, ymax=Entered_Scores_Df$CI_Upper_Lim), width=.2, size = 0.6,
                 position=position_dodge(0.05), color = "#d35400") + geom_line(color = "#00004c", size = 1) + geom_point(shape=23, fill="#00004c", color="#00004c", size=1.5) + geom_label_repel(aes(label = paste0("Change = ", Entered_Scores_Df$Change)), y = -10, segment.color = 'transparent', size = 3, family = "AvantGarde", face = "bold") + geom_label_repel(aes(label = paste0(Entered_Scores_Df$Score)), size = 3, family = "AvantGarde", face = "bold") 
                        
p1<- p1+labs(x="Date", y = "Total DASS-21 Distress Score") +
theme_bw() + theme(panel.background = element_rect("#f1f1f1"), panel.grid.major = element_blank(), panel.grid.major.y = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + scale_y_continuous(limits = c(-10, 73), breaks = c(0,7,14,21,28,35,42,49,56,63), labels = c('0 Min','7','14','21','28','35','42','49','56','63 Max')) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=12, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=12, family = "AvantGarde", face = "bold"), legend.title=element_text(size=10, family = "AvantGarde"), legend.text=element_text(size=9, family = "AvantGarde"), text=element_text(size=12, family="AvantGarde"))
print(p1) 
```

##Score Differences Between All Pairs of Timepoints 
#####Statistically reliable change is indicated by ** 
```{r, echo = FALSE, warning = FALSE,comment=NA, message=FALSE}

if(length(Entered_Scores_Df$Date) == 2) {  

Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score[2] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[2] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2], "**")
      } else if(Rep_Df$Score[2] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[2] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2])
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df2<- data.frame(Time1, SigChange2)
      names(Change_Rep_Df2)[2]<- paste0(Rep_Df$Date[2])  
  

kable(Change_Rep_Df2, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
  
} 
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 3) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score[2] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[2] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2], "**")
      } else if(Rep_Df$Score[2] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[2] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2])
      }
      
      if(Rep_Df$Score[3] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[3] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange3<- paste((Rep_Df$Score[3] - Rep_Df$Score[1]), "**")
      } else if(Rep_Df$Score[3] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[3] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange3<- paste((Rep_Df$Score[3] - Rep_Df$Score[1]))
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df3<- data.frame(Time1, SigChange2, SigChange3)
      names(Change_Rep_Df3)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df3)[3]<- paste0(Rep_Df$Date[3])  
  
  
kable(Change_Rep_Df3, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 3) {

 if(Rep_Df$Score[3] > Rep_Df$CI_Upper_Lim[2] | Rep_Df$Score[3] < Rep_Df$CI_Lower_Lim[2]) {
        SigChange3a<- paste(Rep_Df$Change[3], "**")
      } else if(Rep_Df$Score[3] < Rep_Df$CI_Upper_Lim[2] & Rep_Df$Score[3] > Rep_Df$CI_Lower_Lim[2]) {
        SigChange3a<- paste(Rep_Df$Change[3])
      }
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df3a<- data.frame(Time2, SigChange3a)
      names(Change_Rep_Df3a)[2]<- paste0(Rep_Df$Date[3])  
  
  
kable(Change_Rep_Df3a, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)

}
  
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score[2] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[2] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2], "**")
      } else if(Rep_Df$Score[2] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[2] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2])
      }
      
      if(Rep_Df$Score[3] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[3] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange3<- paste((Rep_Df$Score[3] - Rep_Df$Score[1]), "**")
      } else if(Rep_Df$Score[3] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[3] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange3<- paste((Rep_Df$Score[3] - Rep_Df$Score[1]))
      }
      
      if(Rep_Df$Score[4] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[4] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange4<- paste((Rep_Df$Score[4] - Rep_Df$Score[1]), "**")
      } else if(Rep_Df$Score[4] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[4] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange4<- paste((Rep_Df$Score[4] - Rep_Df$Score[1]))
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df4<- data.frame(Time1, SigChange2, SigChange3, SigChange4)
      names(Change_Rep_Df4)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df4)[3]<- paste0(Rep_Df$Date[3])
      names(Change_Rep_Df4)[4]<- paste0(Rep_Df$Date[4])
      
  
kable(Change_Rep_Df4, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
if(Rep_Df$Score[3] > Rep_Df$CI_Upper_Lim[2] | Rep_Df$Score[3] < Rep_Df$CI_Lower_Lim[2]) {
        SigChange4a<- paste(Rep_Df$Change[3], "**")
      } else if(Rep_Df$Score[3] < Rep_Df$CI_Upper_Lim[2] & Rep_Df$Score[3] > Rep_Df$CI_Lower_Lim[2]) {
        SigChange4a<- paste(Rep_Df$Change[3])
      }
      
      if(Rep_Df$Score[4] > Rep_Df$CI_Upper_Lim[2] | Rep_Df$Score[4] < Rep_Df$CI_Lower_Lim[2]) {
        SigChange4b<- paste((Rep_Df$Score[4] - Rep_Df$Score[2]), "**")
      } else if(Rep_Df$Score[4] < Rep_Df$CI_Upper_Lim[2] & Rep_Df$Score[4] > Rep_Df$CI_Lower_Lim[2]) {
        SigChange4b<- paste((Rep_Df$Score[4] - Rep_Df$Score[2]))
      }
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df4a<- data.frame(Time2, SigChange4a, SigChange4b)
      names(Change_Rep_Df4a)[2]<- paste0(Rep_Df$Date[3])  
      names(Change_Rep_Df4a)[3]<- paste0(Rep_Df$Date[4])   
  
kable(Change_Rep_Df4a, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
    if(Rep_Df$Score[4] > Rep_Df$CI_Upper_Lim[3] | Rep_Df$Score[4] < Rep_Df$CI_Lower_Lim[3]) {
        SigChange4c<- paste(Rep_Df$Change[4], "**")
      } else if(Rep_Df$Score[4] < Rep_Df$CI_Upper_Lim[3] & Rep_Df$Score[4] > Rep_Df$CI_Lower_Lim[3]) {
        SigChange4c<- paste(Rep_Df$Change[4])
      }
      
      Time3<- paste0(Rep_Df$Date[3])
      Change_Rep_Df4b<- data.frame(Time3, SigChange4c)
      names(Change_Rep_Df4b)[2]<- paste0(Rep_Df$Date[4])    
  
  
kable(Change_Rep_Df4b, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE, comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score[2] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[2] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2], "**")
      } else if(Rep_Df$Score[2] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[2] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange2<- paste(Rep_Df$Change[2])
      }
      
      if(Rep_Df$Score[3] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[3] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange3<- paste((Rep_Df$Score[3] - Rep_Df$Score[1]), "**")
      } else if(Rep_Df$Score[3] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[3] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange3<- paste((Rep_Df$Score[3] - Rep_Df$Score[1]))
      }
      
      if(Rep_Df$Score[4] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[4] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange4<- paste((Rep_Df$Score[4] - Rep_Df$Score[1]), "**")
      } else if(Rep_Df$Score[4] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[4] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange4<- paste((Rep_Df$Score[4] - Rep_Df$Score[1]))
      }
      
      if(Rep_Df$Score[5] > Rep_Df$CI_Upper_Lim[1] | Rep_Df$Score[5] < Rep_Df$CI_Lower_Lim[1]) {
        SigChange5<- paste((Rep_Df$Score[5] - Rep_Df$Score[1]), "**")
      } else if(Rep_Df$Score[5] < Rep_Df$CI_Upper_Lim[1] & Rep_Df$Score[5] > Rep_Df$CI_Lower_Lim[1]) {
        SigChange5<- paste((Rep_Df$Score[5] - Rep_Df$Score[1]))
      }
      
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df5<- data.frame(Time1, SigChange2, SigChange3, SigChange4, SigChange5)
      names(Change_Rep_Df5)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df5)[3]<- paste0(Rep_Df$Date[3])
      names(Change_Rep_Df5)[4]<- paste0(Rep_Df$Date[4])
      names(Change_Rep_Df5)[5]<- paste0(Rep_Df$Date[5])  
  
  
kable(Change_Rep_Df5, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
 if(Rep_Df$Score[3] > Rep_Df$CI_Upper_Lim[2] | Rep_Df$Score[3] < Rep_Df$CI_Lower_Lim[2]) {
        SigChange5a<- paste(Rep_Df$Change[3], "**")
      } else if(Rep_Df$Score[3] < Rep_Df$CI_Upper_Lim[2] & Rep_Df$Score[3] > Rep_Df$CI_Lower_Lim[2]) {
        SigChange5a<- paste(Rep_Df$Change[3])
      }
      
      if(Rep_Df$Score[4] > Rep_Df$CI_Upper_Lim[2] | Rep_Df$Score[4] < Rep_Df$CI_Lower_Lim[2]) {
        SigChange5b<- paste((Rep_Df$Score[4] - Rep_Df$Score[2]), "**")
      } else if(Rep_Df$Score[4] < Rep_Df$CI_Upper_Lim[2] & Rep_Df$Score[4] > Rep_Df$CI_Lower_Lim[2]) {
        SigChange5b<- paste((Rep_Df$Score[4] - Rep_Df$Score[2]))
      }
      
      if(Rep_Df$Score[5] > Rep_Df$CI_Upper_Lim[2] | Rep_Df$Score[5] < Rep_Df$CI_Lower_Lim[2]) {
        SigChange5c<- paste((Rep_Df$Score[5] - Rep_Df$Score[2]), "**")
      } else if(Rep_Df$Score[5] < Rep_Df$CI_Upper_Lim[2] & Rep_Df$Score[5] > Rep_Df$CI_Lower_Lim[2]) {
        SigChange5c<- paste((Rep_Df$Score[5] - Rep_Df$Score[2]))
      }
      
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df5a<- data.frame(Time2, SigChange5a, SigChange5b, SigChange5c)
      names(Change_Rep_Df5a)[2]<- paste0(Rep_Df$Date[3])  
      names(Change_Rep_Df5a)[3]<- paste0(Rep_Df$Date[4]) 
      names(Change_Rep_Df5a)[4]<- paste0(Rep_Df$Date[5])   
  
kable(Change_Rep_Df5a, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
if(Rep_Df$Score[4] > Rep_Df$CI_Upper_Lim[3] | Rep_Df$Score[4] < Rep_Df$CI_Lower_Lim[3]) {
        SigChange5d<- paste(Rep_Df$Change[4], "**")
      } else if(Rep_Df$Score[4] < Rep_Df$CI_Upper_Lim[3] & Rep_Df$Score[4] > Rep_Df$CI_Lower_Lim[3]) {
        SigChange5d<- paste(Rep_Df$Change[4])
      }
      
      if(Rep_Df$Score[5] > Rep_Df$CI_Upper_Lim[3] | Rep_Df$Score[5] < Rep_Df$CI_Lower_Lim[3]) {
        SigChange5e<- paste((Rep_Df$Score[5] - Rep_Df$Score[3]), "**")
      } else if(Rep_Df$Score[5] < Rep_Df$CI_Upper_Lim[3] & Rep_Df$Score[5] > Rep_Df$CI_Lower_Lim[3]) {
        SigChange5e<- paste((Rep_Df$Score[5] - Rep_Df$Score[3]))
      }
      
      
      Time3<- paste0(Rep_Df$Date[3])
      Change_Rep_Df5b<- data.frame(Time3, SigChange5d, SigChange5e)
      names(Change_Rep_Df5b)[2]<- paste0(Rep_Df$Date[4])  
      names(Change_Rep_Df5b)[3]<- paste0(Rep_Df$Date[5])    
  
kable(Change_Rep_Df5b, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
 if(Rep_Df$Score[5] > Rep_Df$CI_Upper_Lim[4] | Rep_Df$Score[5] < Rep_Df$CI_Lower_Lim[4]) {
        SigChange5f<- paste(Rep_Df$Change[5], "**")
      } else if(Rep_Df$Score[5] < Rep_Df$CI_Upper_Lim[4] & Rep_Df$Score[5] > Rep_Df$CI_Lower_Lim[4]) {
        SigChange5f<- paste(Rep_Df$Change[5])
      }
      
      Time4<- paste0(Rep_Df$Date[4])
      Change_Rep_Df5c<- data.frame(Time4, SigChange5f)
      names(Change_Rep_Df5c)[2]<- paste0(Rep_Df$Date[5])   
  
kable(Change_Rep_Df5c, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

\newpage

#Depression Subscale

##Response Summary

```{r, echo = FALSE, warning = FALSE, comment=NA}

Scores_Table_Depression<- Entered_Scores_Df[,c(1,13,14,15,16,17,18)]
names(Scores_Table_Depression)<-  c("Date", "Score", "Change", "Predicted Score", "Standard Error", "CI Upper Limit", "CI Lower Limit")
kable(Scores_Table_Depression, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T)
```

##Data Employed in Reliable Change Analyses

```{r, echo = FALSE, warning = FALSE, comment=NA}

Stats_Table_Depression<- kable(Stats_Table_Depression, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T) %>% row_spec(0, bold = T)

add_footnote(Stats_Table_Depression, c(paste("Source of Reference Population Mean and Sd:", Tab_Reference), paste("Source of Test-Retest Reliability: Asghari, Saed & Dibajnia (2008)")), notation = "number")
```

##Trend

```{r, echo = FALSE, warning=FALSE, comment=FALSE, message=FALSE, fig.width=8}

 p2<- ggplot(Entered_Scores_Df, aes(x=factor(Entered_Scores_Df$Date, levels = Entered_Scores_Df$Date), y=Entered_Scores_Df$Score_Depression, group = 1)) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Depression_1[1], linetype = paste(Cutoff_Names$Cutoff_Name_Depression_1[1],":",Entered_Scores_Df$Cutoff_Score_Depression_1[1])),  color = "#827717", 
size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Depression_2[1], linetype = paste(Cutoff_Names$Cutoff_Name_Depression_2[1],":",Entered_Scores_Df$Cutoff_Score_Depression_2[1])), color = "#827717", size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Depression_3[1], linetype = paste(Cutoff_Names$Cutoff_Name_Depression_3[1],":",Entered_Scores_Df$Cutoff_Score_Depression_3[1])), color = "#827717", size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Depression_4[1], linetype = paste(Cutoff_Names$Cutoff_Name_Depression_4[1],":",Entered_Scores_Df$Cutoff_Score_Depression_4[1])), color = "#827717", size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Depression_5[1], linetype = paste(Cutoff_Names$Cutoff_Name_Depression_5[1],":",Entered_Scores_Df$Cutoff_Score_Depression_5[1])), color = "#827717", size = 0.4) + scale_linetype_manual(guide = guide_legend(reverse = TRUE), name = "Cut-Off Scores", values = c("ff","8f","1f","11","solid"),
limits = c(paste(Cutoff_Names$Cutoff_Name_Depression_1[1],":",Entered_Scores_Df$Cutoff_Score_Depression_1[1]),                                                   paste(Cutoff_Names$Cutoff_Name_Depression_2[1],":",Entered_Scores_Df$Cutoff_Score_Depression_2[1]),                                  paste(Cutoff_Names$Cutoff_Name_Depression_3[1],":",Entered_Scores_Df$Cutoff_Score_Depression_3[1]),
paste(Cutoff_Names$Cutoff_Name_Depression_4[1],":",Entered_Scores_Df$Cutoff_Score_Depression_4[1]),
paste(Cutoff_Names$Cutoff_Name_Depression_5[1],":",Entered_Scores_Df$Cutoff_Score_Depression_5[1])
           )) + geom_errorbar(aes(ymin=Entered_Scores_Df$CI_Lower_Lim_Depression, ymax=Entered_Scores_Df$CI_Upper_Lim_Depression), width=.2, size = 0.6,
                 position=position_dodge(0.05), color = "#d35400") + geom_line(color = "#00004c", size = 1) + geom_point(shape=23, fill="#00004c", color="#00004c", size=1.5) + geom_label_repel(aes(label = paste0("Change = ", Entered_Scores_Df$Change_Depression)), y = -10, segment.color = 'transparent', size = 3, family = "AvantGarde") + geom_label_repel(aes(label = paste0(Entered_Scores_Df$Score_Depression)), size = 3, family = "AvantGarde") 
  
p2<- p2+labs(x="Date", y = "Depression Score") +
theme_bw() + theme(panel.background = element_rect("#f1f1f1"), panel.grid.major = element_blank(), panel.grid.major.y = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + scale_y_continuous(limits = c(-10, 31), breaks = c(0,3,6,9,12,15,18,21), labels = c('0 Min','3','6','9','12','15','18','21 Max')) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=12, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=12, family = "AvantGarde", face = "bold"), legend.title=element_text(size=10, family = "AvantGarde"), legend.text=element_text(size=9, family = "AvantGarde"), text=element_text(size=12, family="AvantGarde")) 
print(p2)
```



##Score Differences Between All Pairs of Timepoints 
#####Statistically reliable change is indicated by **

```{r, echo = FALSE, warning = FALSE, comment=NA}


if(length(Entered_Scores_Df$Date) == 2) {  
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Depression[2] > Rep_Df$CI_Upper_Lim_Depression[1] | Rep_Df$Score_Depression[2] < Rep_Df$CI_Lower_Lim_Depression[1]) {
        SigChange2_Depression<- paste(Rep_Df$Change_Depression[2], "**")
      } else if(Rep_Df$Score_Depression[2] < Rep_Df$CI_Upper_Lim_Depression[1] & Rep_Df$Score_Depression[2] > Rep_Df$CI_Lower_Lim_Depression[1]) {
        SigChange2_Depression<- paste(Rep_Df$Change_Depression[2])
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df2_Depression<- data.frame(Time1, SigChange2_Depression)
      names(Change_Rep_Df2_Depression)[2]<- paste0(Rep_Df$Date[2])  
  

kable(Change_Rep_Df2_Depression, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
  
} 
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 3) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Depression[2] > Rep_Df$CI_Upper_Lim_Depression[1] | Rep_Df$Score_Depression[2] < Rep_Df$CI_Lower_Lim_Depression[1]) {
        SigChange2_Depression<- paste(Rep_Df$Change_Depression[2], "**")
      } else if(Rep_Df$Score_Depression[2] < Rep_Df$CI_Upper_Lim_Depression[1] & Rep_Df$Score_Depression[2] > Rep_Df$CI_Lower_Lim_Depression[1]) {
        SigChange2_Depression<- paste(Rep_Df$Change_Depression[2])
      }
      
      if(Rep_Df$Score_Depression[3] > Rep_Df$CI_Upper_Lim_Depression[1] | Rep_Df$Score_Depression[3] < Rep_Df$CI_Lower_Lim_Depression[1]) {
        SigChange3_Depression<- paste((Rep_Df$Score_Depression[3] - Rep_Df$Score_Depression[1]), "**")
      } else if(Rep_Df$Score_Depression[3] < Rep_Df$CI_Upper_Lim_Depression[1] & Rep_Df$Score_Depression[3] > Rep_Df$CI_Lower_Lim_Depression[1]) {
        SigChange3_Depression<- paste((Rep_Df$Score_Depression[3] - Rep_Df$Score_Depression[1]))
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df3_Depression<- data.frame(Time1, SigChange2, SigChange3)
      names(Change_Rep_Df3_Depression)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df3_Depression)[3]<- paste0(Rep_Df$Date[3])  
  
  
kable(Change_Rep_Df3_Depression, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 3) {

 if(Rep_Df$Score_Depression[3] > Rep_Df$CI_Upper_Lim_Depression[2] | Rep_Df$Score_Depression[3] < Rep_Df$CI_Lower_Lim_Depression[2]) {
        SigChange3a_Depression<- paste(Rep_Df$Change_Depression[3], "**")
      } else if(Rep_Df$Score_Depression[3] < Rep_Df$CI_Upper_Lim_Depression[2] & Rep_Df$Score_Depression[3] > Rep_Df$CI_Lower_Lim_Depression[2]) {
        SigChange3a_Depression<- paste(Rep_Df$Change_Depression[3])
      }
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df3a_Depression<- data.frame(Time2, SigChange3a_Depression)
      names(Change_Rep_Df3a_Depression)[2]<- paste0(Rep_Df$Date[3])  
  
  
kable(Change_Rep_Df3a_Depression, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)

}
  
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Depression[2] > Rep_Df$CI_Upper_Lim_Depression[1] | Rep_Df$Score_Depression[2] < Rep_Df$CI_Lower_Lim_Depression[1]) {
        SigChange2_Depression<- paste(Rep_Df$Change_Depression[2], "**")
      } else if(Rep_Df$Score_Depression[2] < Rep_Df$CI_Upper_Lim_Depression[1] & Rep_Df$Score_Depression[2] > Rep_Df$CI_Lower_Lim_Depression[1]) {
        SigChange2_Depression<- paste(Rep_Df$Change_Depression[2])
      }
      
      if(Rep_Df$Score_Depression[3] > Rep_Df$CI_Upper_Lim_Depression[1] | Rep_Df$Score_Depression[3] < Rep_Df$CI_Lower_Lim_Depression[1]) {
        SigChange3_Depression<- paste((Rep_Df$Score_Depression[3] - Rep_Df$Score_Depression[1]), "**")
      } else if(Rep_Df$Score_Depression[3] < Rep_Df$CI_Upper_Lim_Depression[1] & Rep_Df$Score_Depression[3] > Rep_Df$CI_Lower_Lim_Depression[1]) {
        SigChange3_Depression<- paste((Rep_Df$Score_Depression[3] - Rep_Df$Score_Depression[1]))
      }
      
      if(Rep_Df$Score_Depression[4] > Rep_Df$CI_Upper_Lim_Depression[1] | Rep_Df$Score_Depression[4] < Rep_Df$CI_Lower_Lim_Depression[1]) {
        SigChange4_Depression<- paste((Rep_Df$Score_Depression[4] - Rep_Df$Score_Depression[1]), "**")
      } else if(Rep_Df$Score_Depression[4] < Rep_Df$CI_Upper_Lim_Depression[1] & Rep_Df$Score_Depression[4] > Rep_Df$CI_Lower_Lim_Depression[1]) {
        SigChange4_Depression<- paste((Rep_Df$Score_Depression[4] - Rep_Df$Score_Depression[1]))
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df4_Depression<- data.frame(Time1, SigChange2_Depression, SigChange3_Depression, SigChange4_Depression)
      names(Change_Rep_Df4_Depression)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df4_Depression)[3]<- paste0(Rep_Df$Date[3])
      names(Change_Rep_Df4_Depression)[4]<- paste0(Rep_Df$Date[4])
      
  
kable(Change_Rep_Df4_Depression, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
if(Rep_Df$Score_Depression[3] > Rep_Df$CI_Upper_Lim_Depression[2] | Rep_Df$Score_Depression[3] < Rep_Df$CI_Lower_Lim_Depression[2]) {
        SigChange4a_Depression<- paste(Rep_Df$Change_Depression[3], "**")
      } else if(Rep_Df$Score_Depression[3] < Rep_Df$CI_Upper_Lim_Depression[2] & Rep_Df$Score_Depression[3] > Rep_Df$CI_Lower_Lim_Depression[2]) {
        SigChange4a_Depression<- paste(Rep_Df$Change_Depression[3])
      }
      
      if(Rep_Df$Score_Depression[4] > Rep_Df$CI_Upper_Lim_Depression[2] | Rep_Df$Score_Depression[4] < Rep_Df$CI_Lower_Lim_Depression[2]) {
        SigChange4b_Depression<- paste((Rep_Df$Score_Depression[4] - Rep_Df$Score_Depression[2]), "**")
      } else if(Rep_Df$Score_Depression[4] < Rep_Df$CI_Upper_Lim_Depression[2] & Rep_Df$Score_Depression[4] > Rep_Df$CI_Lower_Lim_Depression[2]) {
        SigChange4b_Depression<- paste((Rep_Df$Score_Depression[4] - Rep_Df$Score_Depression[2]))
      }
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df4a_Depression<- data.frame(Time2, SigChange4a_Depression, SigChange4b_Depression)
      names(Change_Rep_Df4a_Depression)[2]<- paste0(Rep_Df$Date[3])  
      names(Change_Rep_Df4a_Depression)[3]<- paste0(Rep_Df$Date[4])   
  
kable(Change_Rep_Df4a_Depression, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
    if(Rep_Df$Score_Depression[4] > Rep_Df$CI_Upper_Lim_Depression[3] | Rep_Df$Score_Depression[4] < Rep_Df$CI_Lower_Lim_Depression[3]) {
        SigChange4c_Depression<- paste(Rep_Df$Change_Depression[4], "**")
      } else if(Rep_Df$Score_Depression[4] < Rep_Df$CI_Upper_Lim_Depression[3] & Rep_Df$Score_Depression[4] > Rep_Df$CI_Lower_Lim_Depression[3]) {
        SigChange4c_Depression<- paste(Rep_Df$Change_Depression[4])
      }
      
      Time3<- paste0(Rep_Df$Date[3])
      Change_Rep_Df4b_Depression<- data.frame(Time3, SigChange4c_Depression)
      names(Change_Rep_Df4b_Depression)[2]<- paste0(Rep_Df$Date[4])    
  
  
kable(Change_Rep_Df4b_Depression, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Depression[2] > Rep_Df$CI_Upper_Lim_Depression[1] | Rep_Df$Score_Depression[2] < Rep_Df$CI_Lower_Lim_Depression[1]) {
        SigChange2_Depression<- paste(Rep_Df$Change_Depression[2], "**")
      } else if(Rep_Df$Score_Depression[2] < Rep_Df$CI_Upper_Lim_Depression[1] & Rep_Df$Score_Depression[2] > Rep_Df$CI_Lower_Lim_Depression[1]) {
        SigChange2_Depression<- paste(Rep_Df$Change_Depression[2])
      }
      
      if(Rep_Df$Score_Depression[3] > Rep_Df$CI_Upper_Lim_Depression[1] | Rep_Df$Score_Depression[3] < Rep_Df$CI_Lower_Lim_Depression[1]) {
        SigChange3_Depression<- paste((Rep_Df$Score_Depression[3] - Rep_Df$Score_Depression[1]), "**")
      } else if(Rep_Df$Score_Depression[3] < Rep_Df$CI_Upper_Lim_Depression[1] & Rep_Df$Score_Depression[3] > Rep_Df$CI_Lower_Lim_Depression[1]) {
        SigChange3_Depression<- paste((Rep_Df$Score_Depression[3] - Rep_Df$Score_Depression[1]))
      }
      
      if(Rep_Df$Score_Depression[4] > Rep_Df$CI_Upper_Lim_Depression[1] | Rep_Df$Score_Depression[4] < Rep_Df$CI_Lower_Lim_Depression[1]) {
        SigChange4_Depression<- paste((Rep_Df$Score_Depression[4] - Rep_Df$Score_Depression[1]), "**")
      } else if(Rep_Df$Score_Depression[4] < Rep_Df$CI_Upper_Lim_Depression[1] & Rep_Df$Score_Depression[4] > Rep_Df$CI_Lower_Lim_Depression[1]) {
        SigChange4_Depression<- paste((Rep_Df$Score_Depression[4] - Rep_Df$Score_Depression[1]))
      }
      
      if(Rep_Df$Score_Depression[5] > Rep_Df$CI_Upper_Lim_Depression[1] | Rep_Df$Score_Depression[5] < Rep_Df$CI_Lower_Lim_Depression[1]) {
        SigChange5_Depression<- paste((Rep_Df$Score_Depression[5] - Rep_Df$Score_Depression[1]), "**")
      } else if(Rep_Df$Score_Depression[5] < Rep_Df$CI_Upper_Lim_Depression[1] & Rep_Df$Score_Depression[5] > Rep_Df$CI_Lower_Lim_Depression[1]) {
        SigChange5_Depression<- paste((Rep_Df$Score_Depression[5] - Rep_Df$Score_Depression[1]))
      }
      
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df5_Depression<- data.frame(Time1, SigChange2_Depression, SigChange3_Depression, SigChange4_Depression, SigChange5_Depression)
      names(Change_Rep_Df5_Depression)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df5_Depression)[3]<- paste0(Rep_Df$Date[3])
      names(Change_Rep_Df5_Depression)[4]<- paste0(Rep_Df$Date[4])
      names(Change_Rep_Df5_Depression)[5]<- paste0(Rep_Df$Date[5])  
  
  
kable(Change_Rep_Df5_Depression, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
 if(Rep_Df$Score_Depression[3] > Rep_Df$CI_Upper_Lim_Depression[2] | Rep_Df$Score_Depression[3] < Rep_Df$CI_Lower_Lim_Depression[2]) {
        SigChange5a_Depression<- paste(Rep_Df$Change_Depression[3], "**")
      } else if(Rep_Df$Score_Depression[3] < Rep_Df$CI_Upper_Lim_Depression[2] & Rep_Df$Score_Depression[3] > Rep_Df$CI_Lower_Lim_Depression[2]) {
        SigChange5a_Depression<- paste(Rep_Df$Change_Depression[3])
      }
      
      if(Rep_Df$Score_Depression[4] > Rep_Df$CI_Upper_Lim_Depression[2] | Rep_Df$Score_Depression[4] < Rep_Df$CI_Lower_Lim_Depression[2]) {
        SigChange5b_Depression<- paste((Rep_Df$Score_Depression[4] - Rep_Df$Score_Depression[2]), "**")
      } else if(Rep_Df$Score_Depression[4] < Rep_Df$CI_Upper_Lim_Depression[2] & Rep_Df$Score_Depression[4] > Rep_Df$CI_Lower_Lim_Depression[2]) {
        SigChange5b_Depression<- paste((Rep_Df$Score_Depression[4] - Rep_Df$Score_Depression[2]))
      }
      
      if(Rep_Df$Score_Depression[5] > Rep_Df$CI_Upper_Lim_Depression[2] | Rep_Df$Score_Depression[5] < Rep_Df$CI_Lower_Lim_Depression[2]) {
        SigChange5c_Depression<- paste((Rep_Df$Score_Depression[5] - Rep_Df$Score_Depression[2]), "**")
      } else if(Rep_Df$Score_Depression[5] < Rep_Df$CI_Upper_Lim_Depression[2] & Rep_Df$Score_Depression[5] > Rep_Df$CI_Lower_Lim_Depression[2]) {
        SigChange5c_Depression<- paste((Rep_Df$Score_Depression[5] - Rep_Df$Score_Depression[2]))
      }
      
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df5a_Depression<- data.frame(Time2, SigChange5a_Depression, SigChange5b_Depression, SigChange5c_Depression)
      names(Change_Rep_Df5a_Depression)[2]<- paste0(Rep_Df$Date[3])  
      names(Change_Rep_Df5a_Depression)[3]<- paste0(Rep_Df$Date[4]) 
      names(Change_Rep_Df5a_Depression)[4]<- paste0(Rep_Df$Date[5])   
  
kable(Change_Rep_Df5a_Depression, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
if(Rep_Df$Score_Depression[4] > Rep_Df$CI_Upper_Lim_Depression[3] | Rep_Df$Score_Depression[4] < Rep_Df$CI_Lower_Lim_Depression[3]) {
        SigChange5d_Depression<- paste(Rep_Df$Change_Depression[4], "**")
      } else if(Rep_Df$Score_Depression[4] < Rep_Df$CI_Upper_Lim_Depression[3] & Rep_Df$Score_Depression[4] > Rep_Df$CI_Lower_Lim_Depression[3]) {
        SigChange5d_Depression<- paste(Rep_Df$Change_Depression[4])
      }
      
      if(Rep_Df$Score_Depression[5] > Rep_Df$CI_Upper_Lim_Depression[3] | Rep_Df$Score_Depression[5] < Rep_Df$CI_Lower_Lim_Depression[3]) {
        SigChange5e_Depression<- paste((Rep_Df$Score_Depression[5] - Rep_Df$Score_Depression[3]), "**")
      } else if(Rep_Df$Score_Depression[5] < Rep_Df$CI_Upper_Lim_Depression[3] & Rep_Df$Score_Depression[5] > Rep_Df$CI_Lower_Lim_Depression[3]) {
        SigChange5e_Depression<- paste((Rep_Df$Score_Depression[5] - Rep_Df$Score_Depression[3]))
      }
      
      
      Time3<- paste0(Rep_Df$Date[3])
      Change_Rep_Df5b_Depression<- data.frame(Time3, SigChange5d_Depression, SigChange5e_Depression)
      names(Change_Rep_Df5b_Depression)[2]<- paste0(Rep_Df$Date[4])  
      names(Change_Rep_Df5b_Depression)[3]<- paste0(Rep_Df$Date[5])    
  
kable(Change_Rep_Df5b_Depression, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
 if(Rep_Df$Score_Depression[5] > Rep_Df$CI_Upper_Lim_Depression[4] | Rep_Df$Score_Depression[5] < Rep_Df$CI_Lower_Lim_Depression[4]) {
        SigChange5f_Depression<- paste(Rep_Df$Change_Depression[5], "**")
      } else if(Rep_Df$Score_Depression[5] < Rep_Df$CI_Upper_Lim_Depression[4] & Rep_Df$Score_Depression[5] > Rep_Df$CI_Lower_Lim_Depression[4]) {
        SigChange5f_Depression<- paste(Rep_Df$Change_Depression[5])
      }
      
      Time4<- paste0(Rep_Df$Date[4])
      Change_Rep_Df5c_Depression<- data.frame(Time4, SigChange5f_Depression)
      names(Change_Rep_Df5c_Depression)[2]<- paste0(Rep_Df$Date[5])   
  
kable(Change_Rep_Df5c_Depression, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```


\newpage

#Anxiety Subscale

##Response Summary
```{r, echo = FALSE, warning = FALSE, , comment=NA}

Scores_Table_Anxiety<- Entered_Scores_Df[,c(1,24,25,26,27,28,29)]
names(Scores_Table_Anxiety)<-  c("Date", "Score", "Change", "Predicted Score", "Standard Error", "CI Upper Limit", "CI Lower Limit")

kable(Scores_Table_Anxiety, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T)
```

##Data Employed in Reliable Change Analyses
```{r, echo = FALSE, warning = FALSE, , comment=NA}

Stats_Table_Anxiety<- kable(Stats_Table_Anxiety, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T) %>% row_spec(0, bold = T)

add_footnote(Stats_Table_Anxiety, c(paste("Source of Reference Population Mean and Sd:", Tab_Reference), paste("Source of Test-Retest Reliability: Asghari, Saed & Dibajnia (2008)")), notation = "number")
```

##Trend
```{r, echo = FALSE, warning=FALSE, comment=FALSE, message=FALSE, fig.width=8}

 p3<- ggplot(Entered_Scores_Df, aes(x=factor(Entered_Scores_Df$Date, levels = Entered_Scores_Df$Date), y=Entered_Scores_Df$Score_Anxiety, group = 1)) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Anxiety_1[1], linetype = paste(Cutoff_Names$Cutoff_Name_Anxiety_1[1],":",Entered_Scores_Df$Cutoff_Score_Anxiety_1[1])), color = "#827717", 
size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Anxiety_2[1], linetype = paste(Cutoff_Names$Cutoff_Name_Anxiety_2[1],":",Entered_Scores_Df$Cutoff_Score_Anxiety_2[1])), color = "#827717", size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Anxiety_3[1], linetype = paste(Cutoff_Names$Cutoff_Name_Anxiety_3[1],":",Entered_Scores_Df$Cutoff_Score_Anxiety_3[1])), color = "#827717", size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Anxiety_4[1], linetype = paste(Cutoff_Names$Cutoff_Name_Anxiety_4[1],":",Entered_Scores_Df$Cutoff_Score_Anxiety_4[1])), color = "#827717", size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Anxiety_5[1], linetype = paste(Cutoff_Names$Cutoff_Name_Anxiety_5[1],":",Entered_Scores_Df$Cutoff_Score_Anxiety_5[1])), color = "#827717", size = 0.4) + scale_linetype_manual(guide = guide_legend(reverse = TRUE), name = "Cut-Off Scores", values = c("ff","8f","1f","11","solid"), limits = c(paste(Cutoff_Names$Cutoff_Name_Anxiety_1[1],":",Entered_Scores_Df$Cutoff_Score_Anxiety_1[1]),                                           paste(Cutoff_Names$Cutoff_Name_Anxiety_2[1],":",Entered_Scores_Df$Cutoff_Score_Anxiety_2[1]),                                            paste(Cutoff_Names$Cutoff_Name_Anxiety_3[1],":",Entered_Scores_Df$Cutoff_Score_Anxiety_3[1]),
paste(Cutoff_Names$Cutoff_Name_Anxiety_4[1],":",Entered_Scores_Df$Cutoff_Score_Anxiety_4[1]),
paste(Cutoff_Names$Cutoff_Name_Anxiety_5[1],":",Entered_Scores_Df$Cutoff_Score_Anxiety_5[1])
)) + geom_errorbar(aes(ymin=Entered_Scores_Df$CI_Lower_Lim_Anxiety, ymax=Entered_Scores_Df$CI_Upper_Lim_Anxiety), width=.2, size = 0.6,
                 position=position_dodge(0.05), color = "#d35400") + geom_line(color = "#00004c", size = 1) + geom_point(shape=23, fill="#00004c", color="#00004c", size=1.5) + geom_label_repel(aes(label = paste0("Change = ", Entered_Scores_Df$Change_Anxiety)), y = -10, segment.color = 'transparent', size = 3, family = "AvantGarde") + geom_label_repel(aes(label = paste0(Entered_Scores_Df$Score_Anxiety)), size = 3, family = "AvantGarde") 
  
p3<- p3+labs(x="Date", y = "Anxiety Score") +
theme_bw() + theme(panel.background = element_rect("#f1f1f1"), panel.grid.major = element_blank(), panel.grid.major.y = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + scale_y_continuous(limits = c(-10, 31), breaks = c(0,3,6,9,12,15,18,21), labels = c('0 Min','3','6','9','12','15','18','21 Max')) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=12, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=12, family = "AvantGarde", face = "bold"), legend.title=element_text(size=10, family = "AvantGarde"), legend.text=element_text(size=9, family = "AvantGarde"), text=element_text(size=12, family="AvantGarde")) 
print(p3)
```


##Score Differences Between All Pairs of Timepoints 
#####Statistically reliable change is indicated by **
```{r, echo = FALSE, warning = FALSE,comment=NA}


if(length(Entered_Scores_Df$Date) == 2) {  
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Anxiety[2] > Rep_Df$CI_Upper_Lim_Anxiety[1] | Rep_Df$Score_Anxiety[2] < Rep_Df$CI_Lower_Lim_Anxiety[1]) {
        SigChange2_Anxiety<- paste(Rep_Df$Change_Anxiety[2], "**")
      } else if(Rep_Df$Score_Anxiety[2] < Rep_Df$CI_Upper_Lim_Anxiety[1] & Rep_Df$Score_Anxiety[2] > Rep_Df$CI_Lower_Lim_Anxiety[1]) {
        SigChange2_Anxiety<- paste(Rep_Df$Change_Anxiety[2])
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df2_Anxiety<- data.frame(Time1, SigChange2_Anxiety)
      names(Change_Rep_Df2_Anxiety)[2]<- paste0(Rep_Df$Date[2])  
  

kable(Change_Rep_Df2_Anxiety, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
  
} 
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 3) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Anxiety[2] > Rep_Df$CI_Upper_Lim_Anxiety[1] | Rep_Df$Score_Anxiety[2] < Rep_Df$CI_Lower_Lim_Anxiety[1]) {
        SigChange2_Anxiety<- paste(Rep_Df$Change_Anxiety[2], "**")
      } else if(Rep_Df$Score_Anxiety[2] < Rep_Df$CI_Upper_Lim_Anxiety[1] & Rep_Df$Score_Anxiety[2] > Rep_Df$CI_Lower_Lim_Anxiety[1]) {
        SigChange2_Anxiety<- paste(Rep_Df$Change_Anxiety[2])
      }
      
      if(Rep_Df$Score_Anxiety[3] > Rep_Df$CI_Upper_Lim_Anxiety[1] | Rep_Df$Score_Anxiety[3] < Rep_Df$CI_Lower_Lim_Anxiety[1]) {
        SigChange3_Anxiety<- paste((Rep_Df$Score_Anxiety[3] - Rep_Df$Score_Anxiety[1]), "**")
      } else if(Rep_Df$Score_Anxiety[3] < Rep_Df$CI_Upper_Lim_Anxiety[1] & Rep_Df$Score_Anxiety[3] > Rep_Df$CI_Lower_Lim_Anxiety[1]) {
        SigChange3_Anxiety<- paste((Rep_Df$Score_Anxiety[3] - Rep_Df$Score_Anxiety[1]))
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df3_Anxiety<- data.frame(Time1, SigChange2, SigChange3)
      names(Change_Rep_Df3_Anxiety)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df3_Anxiety)[3]<- paste0(Rep_Df$Date[3])  
  
  
kable(Change_Rep_Df3_Anxiety, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 3) {

 if(Rep_Df$Score_Anxiety[3] > Rep_Df$CI_Upper_Lim_Anxiety[2] | Rep_Df$Score_Anxiety[3] < Rep_Df$CI_Lower_Lim_Anxiety[2]) {
        SigChange3a_Anxiety<- paste(Rep_Df$Change_Anxiety[3], "**")
      } else if(Rep_Df$Score_Anxiety[3] < Rep_Df$CI_Upper_Lim_Anxiety[2] & Rep_Df$Score_Anxiety[3] > Rep_Df$CI_Lower_Lim_Anxiety[2]) {
        SigChange3a_Anxiety<- paste(Rep_Df$Change_Anxiety[3])
      }
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df3a_Anxiety<- data.frame(Time2, SigChange3a_Anxiety)
      names(Change_Rep_Df3a_Anxiety)[2]<- paste0(Rep_Df$Date[3])  
  
  
kable(Change_Rep_Df3a_Anxiety, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)

}
  
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Anxiety[2] > Rep_Df$CI_Upper_Lim_Anxiety[1] | Rep_Df$Score_Anxiety[2] < Rep_Df$CI_Lower_Lim_Anxiety[1]) {
        SigChange2_Anxiety<- paste(Rep_Df$Change_Anxiety[2], "**")
      } else if(Rep_Df$Score_Anxiety[2] < Rep_Df$CI_Upper_Lim_Anxiety[1] & Rep_Df$Score_Anxiety[2] > Rep_Df$CI_Lower_Lim_Anxiety[1]) {
        SigChange2_Anxiety<- paste(Rep_Df$Change_Anxiety[2])
      }
      
      if(Rep_Df$Score_Anxiety[3] > Rep_Df$CI_Upper_Lim_Anxiety[1] | Rep_Df$Score_Anxiety[3] < Rep_Df$CI_Lower_Lim_Anxiety[1]) {
        SigChange3_Anxiety<- paste((Rep_Df$Score_Anxiety[3] - Rep_Df$Score_Anxiety[1]), "**")
      } else if(Rep_Df$Score_Anxiety[3] < Rep_Df$CI_Upper_Lim_Anxiety[1] & Rep_Df$Score_Anxiety[3] > Rep_Df$CI_Lower_Lim_Anxiety[1]) {
        SigChange3_Anxiety<- paste((Rep_Df$Score_Anxiety[3] - Rep_Df$Score_Anxiety[1]))
      }
      
      if(Rep_Df$Score_Anxiety[4] > Rep_Df$CI_Upper_Lim_Anxiety[1] | Rep_Df$Score_Anxiety[4] < Rep_Df$CI_Lower_Lim_Anxiety[1]) {
        SigChange4_Anxiety<- paste((Rep_Df$Score_Anxiety[4] - Rep_Df$Score_Anxiety[1]), "**")
      } else if(Rep_Df$Score_Anxiety[4] < Rep_Df$CI_Upper_Lim_Anxiety[1] & Rep_Df$Score_Anxiety[4] > Rep_Df$CI_Lower_Lim_Anxiety[1]) {
        SigChange4_Anxiety<- paste((Rep_Df$Score_Anxiety[4] - Rep_Df$Score_Anxiety[1]))
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df4_Anxiety<- data.frame(Time1, SigChange2_Anxiety, SigChange3_Anxiety, SigChange4_Anxiety)
      names(Change_Rep_Df4_Anxiety)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df4_Anxiety)[3]<- paste0(Rep_Df$Date[3])
      names(Change_Rep_Df4_Anxiety)[4]<- paste0(Rep_Df$Date[4])
      
  
kable(Change_Rep_Df4_Anxiety, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
if(Rep_Df$Score_Anxiety[3] > Rep_Df$CI_Upper_Lim_Anxiety[2] | Rep_Df$Score_Anxiety[3] < Rep_Df$CI_Lower_Lim_Anxiety[2]) {
        SigChange4a_Anxiety<- paste(Rep_Df$Change_Anxiety[3], "**")
      } else if(Rep_Df$Score_Anxiety[3] < Rep_Df$CI_Upper_Lim_Anxiety[2] & Rep_Df$Score_Anxiety[3] > Rep_Df$CI_Lower_Lim_Anxiety[2]) {
        SigChange4a_Anxiety<- paste(Rep_Df$Change_Anxiety[3])
      }
      
      if(Rep_Df$Score_Anxiety[4] > Rep_Df$CI_Upper_Lim_Anxiety[2] | Rep_Df$Score_Anxiety[4] < Rep_Df$CI_Lower_Lim_Anxiety[2]) {
        SigChange4b_Anxiety<- paste((Rep_Df$Score_Anxiety[4] - Rep_Df$Score_Anxiety[2]), "**")
      } else if(Rep_Df$Score_Anxiety[4] < Rep_Df$CI_Upper_Lim_Anxiety[2] & Rep_Df$Score_Anxiety[4] > Rep_Df$CI_Lower_Lim_Anxiety[2]) {
        SigChange4b_Anxiety<- paste((Rep_Df$Score_Anxiety[4] - Rep_Df$Score_Anxiety[2]))
      }
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df4a_Anxiety<- data.frame(Time2, SigChange4a_Anxiety, SigChange4b_Anxiety)
      names(Change_Rep_Df4a_Anxiety)[2]<- paste0(Rep_Df$Date[3])  
      names(Change_Rep_Df4a_Anxiety)[3]<- paste0(Rep_Df$Date[4])   
  
  
kable(Change_Rep_Df4a_Anxiety, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
    if(Rep_Df$Score_Anxiety[4] > Rep_Df$CI_Upper_Lim_Anxiety[3] | Rep_Df$Score_Anxiety[4] < Rep_Df$CI_Lower_Lim_Anxiety[3]) {
        SigChange4c_Anxiety<- paste(Rep_Df$Change_Anxiety[4], "**")
      } else if(Rep_Df$Score_Anxiety[4] < Rep_Df$CI_Upper_Lim_Anxiety[3] & Rep_Df$Score_Anxiety[4] > Rep_Df$CI_Lower_Lim_Anxiety[3]) {
        SigChange4c_Anxiety<- paste(Rep_Df$Change_Anxiety[4])
      }
      
      Time3<- paste0(Rep_Df$Date[3])
      Change_Rep_Df4b_Anxiety<- data.frame(Time3, SigChange4c_Anxiety)
      names(Change_Rep_Df4b_Anxiety)[2]<- paste0(Rep_Df$Date[4])    
  
  
  
kable(Change_Rep_Df4b_Anxiety, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Anxiety[2] > Rep_Df$CI_Upper_Lim_Anxiety[1] | Rep_Df$Score_Anxiety[2] < Rep_Df$CI_Lower_Lim_Anxiety[1]) {
        SigChange2_Anxiety<- paste(Rep_Df$Change[2], "**")
      } else if(Rep_Df$Score_Anxiety[2] < Rep_Df$CI_Upper_Lim_Anxiety[1] & Rep_Df$Score_Anxiety[2] > Rep_Df$CI_Lower_Lim_Anxiety[1]) {
        SigChange2_Anxiety<- paste(Rep_Df$Change[2])
      }
      
      if(Rep_Df$Score_Anxiety[3] > Rep_Df$CI_Upper_Lim_Anxiety[1] | Rep_Df$Score_Anxiety[3] < Rep_Df$CI_Lower_Lim_Anxiety[1]) {
        SigChange3_Anxiety<- paste((Rep_Df$Score_Anxiety[3] - Rep_Df$Score_Anxiety[1]), "**")
      } else if(Rep_Df$Score_Anxiety[3] < Rep_Df$CI_Upper_Lim_Anxiety[1] & Rep_Df$Score_Anxiety[3] > Rep_Df$CI_Lower_Lim_Anxiety[1]) {
        SigChange3_Anxiety<- paste((Rep_Df$Score_Anxiety[3] - Rep_Df$Score_Anxiety[1]))
      }
      
      if(Rep_Df$Score_Anxiety[4] > Rep_Df$CI_Upper_Lim_Anxiety[1] | Rep_Df$Score_Anxiety[4] < Rep_Df$CI_Lower_Lim_Anxiety[1]) {
        SigChange4_Anxiety<- paste((Rep_Df$Score_Anxiety[4] - Rep_Df$Score_Anxiety[1]), "**")
      } else if(Rep_Df$Score_Anxiety[4] < Rep_Df$CI_Upper_Lim_Anxiety[1] & Rep_Df$Score_Anxiety[4] > Rep_Df$CI_Lower_Lim_Anxiety[1]) {
        SigChange4_Anxiety<- paste((Rep_Df$Score_Anxiety[4] - Rep_Df$Score_Anxiety[1]))
      }
      
      if(Rep_Df$Score_Anxiety[5] > Rep_Df$CI_Upper_Lim_Anxiety[1] | Rep_Df$Score_Anxiety[5] < Rep_Df$CI_Lower_Lim_Anxiety[1]) {
        SigChange5_Anxiety<- paste((Rep_Df$Score_Anxiety[5] - Rep_Df$Score_Anxiety[1]), "**")
      } else if(Rep_Df$Score_Anxiety[5] < Rep_Df$CI_Upper_Lim_Anxiety[1] & Rep_Df$Score_Anxiety[5] > Rep_Df$CI_Lower_Lim_Anxiety[1]) {
        SigChange5_Anxiety<- paste((Rep_Df$Score_Anxiety[5] - Rep_Df$Score_Anxiety[1]))
      }
      
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df5_Anxiety<- data.frame(Time1, SigChange2_Anxiety, SigChange3_Anxiety, SigChange4_Anxiety, SigChange5_Anxiety)
      names(Change_Rep_Df5_Anxiety)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df5_Anxiety)[3]<- paste0(Rep_Df$Date[3])
      names(Change_Rep_Df5_Anxiety)[4]<- paste0(Rep_Df$Date[4])
      names(Change_Rep_Df5_Anxiety)[5]<- paste0(Rep_Df$Date[5])  
  
  
kable(Change_Rep_Df5_Anxiety, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
 if(Rep_Df$Score_Anxiety[3] > Rep_Df$CI_Upper_Lim_Anxiety[2] | Rep_Df$Score_Anxiety[3] < Rep_Df$CI_Lower_Lim_Anxiety[2]) {
        SigChange5a_Anxiety<- paste(Rep_Df$Change_Anxiety[3], "**")
      } else if(Rep_Df$Score_Anxiety[3] < Rep_Df$CI_Upper_Lim_Anxiety[2] & Rep_Df$Score_Anxiety[3] > Rep_Df$CI_Lower_Lim_Anxiety[2]) {
        SigChange5a_Anxiety<- paste(Rep_Df$Change_Anxiety[3])
      }
      
      if(Rep_Df$Score_Anxiety[4] > Rep_Df$CI_Upper_Lim_Anxiety[2] | Rep_Df$Score_Anxiety[4] < Rep_Df$CI_Lower_Lim_Anxiety[2]) {
        SigChange5b_Anxiety<- paste((Rep_Df$Score_Anxiety[4] - Rep_Df$Score_Anxiety[2]), "**")
      } else if(Rep_Df$Score_Anxiety[4] < Rep_Df$CI_Upper_Lim_Anxiety[2] & Rep_Df$Score_Anxiety[4] > Rep_Df$CI_Lower_Lim_Anxiety[2]) {
        SigChange5b_Anxiety<- paste((Rep_Df$Score_Anxiety[4] - Rep_Df$Score_Anxiety[2]))
      }
      
      if(Rep_Df$Score_Anxiety[5] > Rep_Df$CI_Upper_Lim_Anxiety[2] | Rep_Df$Score_Anxiety[5] < Rep_Df$CI_Lower_Lim_Anxiety[2]) {
        SigChange5c_Anxiety<- paste((Rep_Df$Score_Anxiety[5] - Rep_Df$Score_Anxiety[2]), "**")
      } else if(Rep_Df$Score_Anxiety[5] < Rep_Df$CI_Upper_Lim_Anxiety[2] & Rep_Df$Score_Anxiety[5] > Rep_Df$CI_Lower_Lim_Anxiety[2]) {
        SigChange5c_Anxiety<- paste((Rep_Df$Score_Anxiety[5] - Rep_Df$Score_Anxiety[2]))
      }
      
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df5a_Anxiety<- data.frame(Time2, SigChange5a_Anxiety, SigChange5b_Anxiety, SigChange5c_Anxiety)
      names(Change_Rep_Df5a_Anxiety)[2]<- paste0(Rep_Df$Date[3])  
      names(Change_Rep_Df5a_Anxiety)[3]<- paste0(Rep_Df$Date[4]) 
      names(Change_Rep_Df5a_Anxiety)[4]<- paste0(Rep_Df$Date[5])   
  
kable(Change_Rep_Df5a_Anxiety, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
if(Rep_Df$Score_Anxiety[4] > Rep_Df$CI_Upper_Lim_Anxiety[3] | Rep_Df$Score_Anxiety[4] < Rep_Df$CI_Lower_Lim_Anxiety[3]) {
        SigChange5d_Anxiety<- paste(Rep_Df$Change_Anxiety[4], "**")
      } else if(Rep_Df$Score_Anxiety[4] < Rep_Df$CI_Upper_Lim_Anxiety[3] & Rep_Df$Score_Anxiety[4] > Rep_Df$CI_Lower_Lim_Anxiety[3]) {
        SigChange5d_Anxiety<- paste(Rep_Df$Change_Anxiety[4])
      }
      
      if(Rep_Df$Score_Anxiety[5] > Rep_Df$CI_Upper_Lim_Anxiety[3] | Rep_Df$Score_Anxiety[5] < Rep_Df$CI_Lower_Lim_Anxiety[3]) {
        SigChange5e_Anxiety<- paste((Rep_Df$Score_Anxiety[5] - Rep_Df$Score_Anxiety[3]), "**")
      } else if(Rep_Df$Score_Anxiety[5] < Rep_Df$CI_Upper_Lim_Anxiety[3] & Rep_Df$Score_Anxiety[5] > Rep_Df$CI_Lower_Lim_Anxiety[3]) {
        SigChange5e_Anxiety<- paste((Rep_Df$Score_Anxiety[5] - Rep_Df$Score_Anxiety[3]))
      }
      
      
      Time3<- paste0(Rep_Df$Date[3])
      Change_Rep_Df5b_Anxiety<- data.frame(Time3, SigChange5d_Anxiety, SigChange5e_Anxiety)
      names(Change_Rep_Df5b_Anxiety)[2]<- paste0(Rep_Df$Date[4])  
      names(Change_Rep_Df5b_Anxiety)[3]<- paste0(Rep_Df$Date[5])    
  
kable(Change_Rep_Df5b_Anxiety, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
 if(Rep_Df$Score_Anxiety[5] > Rep_Df$CI_Upper_Lim_Anxiety[4] | Rep_Df$Score_Anxiety[5] < Rep_Df$CI_Lower_Lim_Anxiety[4]) {
        SigChange5f_Anxiety<- paste(Rep_Df$Change_Anxiety[5], "**")
      } else if(Rep_Df$Score_Anxiety[5] < Rep_Df$CI_Upper_Lim_Anxiety[4] & Rep_Df$Score_Anxiety[5] > Rep_Df$CI_Lower_Lim_Anxiety[4]) {
        SigChange5f_Anxiety<- paste(Rep_Df$Change_Anxiety[5])
      }
      
      Time4<- paste0(Rep_Df$Date[4])
      Change_Rep_Df5c_Anxiety<- data.frame(Time4, SigChange5f_Anxiety)
      names(Change_Rep_Df5c_Anxiety)[2]<- paste0(Rep_Df$Date[5])   
  
kable(Change_Rep_Df5c_Anxiety, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

\newpage 

#Stress Subscale

##Response Summary

```{r, echo = FALSE, warning = FALSE, comment=NA}

Scores_Table_Stress<- Entered_Scores_Df[,c(1,35,36,37,38,39,40)]
names(Scores_Table_Stress)<-  c("Date", "Score", "Change", "Predicted Score", "Standard Error", "CI Upper Limit", "CI Lower Limit")
kable(Scores_Table_Stress, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T, latex_options = "striped") %>% row_spec(0, bold = T)
```

##Data Employed in Reliable Change Analyses

```{r, echo = FALSE, warning = FALSE, comment=NA}

Stats_Table_Stress<- kable(Stats_Table_Stress, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = T) %>% row_spec(0, bold = T)

add_footnote(Stats_Table_Stress, c(paste("Source of Reference Population Mean and Sd:", Tab_Reference), paste("Source of Test-Retest Reliability: Asghari, Saed & Dibajnia (2008)")), notation = "number")
```

##Trend

```{r, echo = FALSE, warning=FALSE, comment=FALSE, message=FALSE, fig.width=8}

 p2<- ggplot(Entered_Scores_Df, aes(x=factor(Entered_Scores_Df$Date, levels = Entered_Scores_Df$Date), y=Entered_Scores_Df$Score_Stress, group = 1)) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Stress_1[1], linetype = paste(Cutoff_Names$Cutoff_Name_Stress_1[1],":",Entered_Scores_Df$Cutoff_Score_Stress_1[1])), color = "#827717", 
size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Stress_2[1], linetype = paste(Cutoff_Names$Cutoff_Name_Stress_2[1],":",Entered_Scores_Df$Cutoff_Score_Stress_2[1])), color = "#827717", size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Stress_3[1], linetype = paste(Cutoff_Names$Cutoff_Name_Stress_3[1],":",Entered_Scores_Df$Cutoff_Score_Stress_3[1])), color = "#827717", size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Stress_4[1], linetype = paste(Cutoff_Names$Cutoff_Name_Stress_4[1],":",Entered_Scores_Df$Cutoff_Score_Stress_4[1])), color = "#827717", size = 0.4) + geom_hline(aes(yintercept = Entered_Scores_Df$Cutoff_Score_Stress_5[1], linetype = paste(Cutoff_Names$Cutoff_Name_Stress_5[1],":",Entered_Scores_Df$Cutoff_Score_Stress_5[1])), color = "#827717", size = 0.4) + scale_linetype_manual(guide = guide_legend(reverse = TRUE), name = "Cut-Off Scores", values = c("ff","8f","1f","11","solid"), limits = c(paste(Cutoff_Names$Cutoff_Name_Stress_1[1],":",Entered_Scores_Df$Cutoff_Score_Stress_1[1]),                                           paste(Cutoff_Names$Cutoff_Name_Stress_2[1],":",Entered_Scores_Df$Cutoff_Score_Stress_2[1]),                            paste(Cutoff_Names$Cutoff_Name_Stress_3[1],":",Entered_Scores_Df$Cutoff_Score_Stress_3[1]),
paste(Cutoff_Names$Cutoff_Name_Stress_4[1],":",Entered_Scores_Df$Cutoff_Score_Stress_4[1]),
paste(Cutoff_Names$Cutoff_Name_Stress_5[1],":",Entered_Scores_Df$Cutoff_Score_Stress_5[1])                                                                                 )) + geom_errorbar(aes(ymin=Entered_Scores_Df$CI_Lower_Lim_Stress, ymax=Entered_Scores_Df$CI_Upper_Lim_Stress), width=.2, size = 0.6,
                 position=position_dodge(0.05), color = "#d35400") + geom_line(color = "#00004c", size = 1) + geom_point(shape=23, fill="#00004c", color="#00004c", size=1.5) + geom_label_repel(aes(label = paste0("Change = ", Entered_Scores_Df$Change_Stress)), y = -10, segment.color = 'transparent', size = 3, family = "AvantGarde") + geom_label_repel(aes(label = paste0(Entered_Scores_Df$Score_Stress)), size = 3, family = "AvantGarde") 
  
p2<- p2+labs(x="Date", y = "Stress Score") +
theme_bw() + theme(panel.background = element_rect("#f1f1f1"), panel.grid.major = element_blank(), panel.grid.major.y = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), panel.border = element_rect(colour = "#00004c", fill=NA, size=3)) + scale_y_continuous(limits = c(-10, 31), breaks = c(0,3,6,9,12,15,18,21), labels = c('0 Min','3','6','9','12','15','18','21 Max')) + theme(axis.text.x =  element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.text.y = element_text(size=9, family = "AvantGarde", color = "black", face = "bold"), axis.title.x = element_text(size=12, family = "AvantGarde", face = "bold"), axis.title.y = element_text(size=12, family = "AvantGarde", face = "bold"), legend.title=element_text(size=10, family = "AvantGarde"), legend.text=element_text(size=9, family = "AvantGarde"), text=element_text(size=12, family="AvantGarde")) 
print(p2)
```



##Score Differences Between All Pairs of Timepoints 
#####Statistically reliable change is indicated by **

```{r, echo = FALSE, warning = FALSE, comment=NA}


if(length(Entered_Scores_Df$Date) == 2) {  
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Stress[2] > Rep_Df$CI_Upper_Lim_Stress[1] | Rep_Df$Score_Stress[2] < Rep_Df$CI_Lower_Lim_Stress[1]) {
        SigChange2_Stress<- paste(Rep_Df$Change_Stress[2], "**")
      } else if(Rep_Df$Score_Stress[2] < Rep_Df$CI_Upper_Lim_Stress[1] & Rep_Df$Score_Stress[2] > Rep_Df$CI_Lower_Lim_Stress[1]) {
        SigChange2_Stress<- paste(Rep_Df$Change_Stress[2])
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df2_Stress<- data.frame(Time1, SigChange2_Stress)
      names(Change_Rep_Df2_Stress)[2]<- paste0(Rep_Df$Date[2])  
  

kable(Change_Rep_Df2_Stress, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
  
} 
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 3) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Stress[2] > Rep_Df$CI_Upper_Lim_Stress[1] | Rep_Df$Score_Stress[2] < Rep_Df$CI_Lower_Lim_Stress[1]) {
        SigChange2_Stress<- paste(Rep_Df$Change_Stress[2], "**")
      } else if(Rep_Df$Score_Stress[2] < Rep_Df$CI_Upper_Lim_Stress[1] & Rep_Df$Score_Stress[2] > Rep_Df$CI_Lower_Lim_Stress[1]) {
        SigChange2_Stress<- paste(Rep_Df$Change_Stress[2])
      }
      
      if(Rep_Df$Score_Stress[3] > Rep_Df$CI_Upper_Lim_Stress[1] | Rep_Df$Score_Stress[3] < Rep_Df$CI_Lower_Lim_Stress[1]) {
        SigChange3_Stress<- paste((Rep_Df$Score_Stress[3] - Rep_Df$Score_Stress[1]), "**")
      } else if(Rep_Df$Score_Stress[3] < Rep_Df$CI_Upper_Lim_Stress[1] & Rep_Df$Score_Stress[3] > Rep_Df$CI_Lower_Lim_Stress[1]) {
        SigChange3_Stress<- paste((Rep_Df$Score_Stress[3] - Rep_Df$Score_Stress[1]))
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df3_Stress<- data.frame(Time1, SigChange2, SigChange3)
      names(Change_Rep_Df3_Stress)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df3_Stress)[3]<- paste0(Rep_Df$Date[3])  
  
  
kable(Change_Rep_Df3_Stress, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 3) {

 if(Rep_Df$Score_Stress[3] > Rep_Df$CI_Upper_Lim_Stress[2] | Rep_Df$Score_Stress[3] < Rep_Df$CI_Lower_Lim_Stress[2]) {
        SigChange3a_Stress<- paste(Rep_Df$Change_Stress[3], "**")
      } else if(Rep_Df$Score_Stress[3] < Rep_Df$CI_Upper_Lim_Stress[2] & Rep_Df$Score_Stress[3] > Rep_Df$CI_Lower_Lim_Stress[2]) {
        SigChange3a_Stress<- paste(Rep_Df$Change_Stress[3])
      }
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df3a_Stress<- data.frame(Time2, SigChange3a_Stress)
      names(Change_Rep_Df3a_Stress)[2]<- paste0(Rep_Df$Date[3])  
  
  
kable(Change_Rep_Df3a_Stress, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)

}
  
```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Stress[2] > Rep_Df$CI_Upper_Lim_Stress[1] | Rep_Df$Score_Stress[2] < Rep_Df$CI_Lower_Lim_Stress[1]) {
        SigChange2_Stress<- paste(Rep_Df$Change_Stress[2], "**")
      } else if(Rep_Df$Score_Stress[2] < Rep_Df$CI_Upper_Lim_Stress[1] & Rep_Df$Score_Stress[2] > Rep_Df$CI_Lower_Lim_Stress[1]) {
        SigChange2_Stress<- paste(Rep_Df$Change_Stress[2])
      }
      
      if(Rep_Df$Score_Stress[3] > Rep_Df$CI_Upper_Lim_Stress[1] | Rep_Df$Score_Stress[3] < Rep_Df$CI_Lower_Lim_Stress[1]) {
        SigChange3_Stress<- paste((Rep_Df$Score_Stress[3] - Rep_Df$Score_Stress[1]), "**")
      } else if(Rep_Df$Score_Stress[3] < Rep_Df$CI_Upper_Lim_Stress[1] & Rep_Df$Score_Stress[3] > Rep_Df$CI_Lower_Lim_Stress[1]) {
        SigChange3_Stress<- paste((Rep_Df$Score_Stress[3] - Rep_Df$Score_Stress[1]))
      }
      
      if(Rep_Df$Score_Stress[4] > Rep_Df$CI_Upper_Lim_Stress[1] | Rep_Df$Score_Stress[4] < Rep_Df$CI_Lower_Lim_Stress[1]) {
        SigChange4_Stress<- paste((Rep_Df$Score_Stress[4] - Rep_Df$Score_Stress[1]), "**")
      } else if(Rep_Df$Score_Stress[4] < Rep_Df$CI_Upper_Lim_Stress[1] & Rep_Df$Score_Stress[4] > Rep_Df$CI_Lower_Lim_Stress[1]) {
        SigChange4_Stress<- paste((Rep_Df$Score_Stress[4] - Rep_Df$Score_Stress[1]))
      }
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df4_Stress<- data.frame(Time1, SigChange2_Stress, SigChange3_Stress, SigChange4_Stress)
      names(Change_Rep_Df4_Stress)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df4_Stress)[3]<- paste0(Rep_Df$Date[3])
      names(Change_Rep_Df4_Stress)[4]<- paste0(Rep_Df$Date[4])
      
  
kable(Change_Rep_Df4_Stress, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
if(Rep_Df$Score_Stress[3] > Rep_Df$CI_Upper_Lim_Stress[2] | Rep_Df$Score_Stress[3] < Rep_Df$CI_Lower_Lim_Stress[2]) {
        SigChange4a_Stress<- paste(Rep_Df$Change_Stress[3], "**")
      } else if(Rep_Df$Score_Stress[3] < Rep_Df$CI_Upper_Lim_Stress[2] & Rep_Df$Score_Stress[3] > Rep_Df$CI_Lower_Lim_Stress[2]) {
        SigChange4a_Stress<- paste(Rep_Df$Change_Stress[3])
      }
      
      if(Rep_Df$Score_Stress[4] > Rep_Df$CI_Upper_Lim_Stress[2] | Rep_Df$Score_Stress[4] < Rep_Df$CI_Lower_Lim_Stress[2]) {
        SigChange4b_Stress<- paste((Rep_Df$Score_Stress[4] - Rep_Df$Score_Stress[2]), "**")
      } else if(Rep_Df$Score_Stress[4] < Rep_Df$CI_Upper_Lim_Stress[2] & Rep_Df$Score_Stress[4] > Rep_Df$CI_Lower_Lim_Stress[2]) {
        SigChange4b_Stress<- paste((Rep_Df$Score_Stress[4] - Rep_Df$Score_Stress[2]))
      }
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df4a_Stress<- data.frame(Time2, SigChange4a_Stress, SigChange4b_Stress)
      names(Change_Rep_Df4a_Stress)[2]<- paste0(Rep_Df$Date[3])  
      names(Change_Rep_Df4a_Stress)[3]<- paste0(Rep_Df$Date[4])   
  
kable(Change_Rep_Df4a_Stress, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 4) {
  
    if(Rep_Df$Score_Stress[4] > Rep_Df$CI_Upper_Lim_Stress[3] | Rep_Df$Score_Stress[4] < Rep_Df$CI_Lower_Lim_Stress[3]) {
        SigChange4c_Stress<- paste(Rep_Df$Change_Stress[4], "**")
      } else if(Rep_Df$Score_Stress[4] < Rep_Df$CI_Upper_Lim_Stress[3] & Rep_Df$Score_Stress[4] > Rep_Df$CI_Lower_Lim_Stress[3]) {
        SigChange4c_Stress<- paste(Rep_Df$Change_Stress[4])
      }
      
      Time3<- paste0(Rep_Df$Date[3])
      Change_Rep_Df4b_Stress<- data.frame(Time3, SigChange4c_Stress)
      names(Change_Rep_Df4b_Stress)[2]<- paste0(Rep_Df$Date[4])    
  
  
kable(Change_Rep_Df4b_Stress, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
Rep_Df<- Entered_Scores_Df
      if(Rep_Df$Score_Stress[2] > Rep_Df$CI_Upper_Lim_Stress[1] | Rep_Df$Score_Stress[2] < Rep_Df$CI_Lower_Lim_Stress[1]) {
        SigChange2_Stress<- paste(Rep_Df$Change_Stress[2], "**")
      } else if(Rep_Df$Score_Stress[2] < Rep_Df$CI_Upper_Lim_Stress[1] & Rep_Df$Score_Stress[2] > Rep_Df$CI_Lower_Lim_Stress[1]) {
        SigChange2_Stress<- paste(Rep_Df$Change_Stress[2])
      }
      
      if(Rep_Df$Score_Stress[3] > Rep_Df$CI_Upper_Lim_Stress[1] | Rep_Df$Score_Stress[3] < Rep_Df$CI_Lower_Lim_Stress[1]) {
        SigChange3_Stress<- paste((Rep_Df$Score_Stress[3] - Rep_Df$Score_Stress[1]), "**")
      } else if(Rep_Df$Score_Stress[3] < Rep_Df$CI_Upper_Lim_Stress[1] & Rep_Df$Score_Stress[3] > Rep_Df$CI_Lower_Lim_Stress[1]) {
        SigChange3_Stress<- paste((Rep_Df$Score_Stress[3] - Rep_Df$Score_Stress[1]))
      }
      
      if(Rep_Df$Score_Stress[4] > Rep_Df$CI_Upper_Lim_Stress[1] | Rep_Df$Score_Stress[4] < Rep_Df$CI_Lower_Lim_Stress[1]) {
        SigChange4_Stress<- paste((Rep_Df$Score_Stress[4] - Rep_Df$Score_Stress[1]), "**")
      } else if(Rep_Df$Score_Stress[4] < Rep_Df$CI_Upper_Lim_Stress[1] & Rep_Df$Score_Stress[4] > Rep_Df$CI_Lower_Lim_Stress[1]) {
        SigChange4_Stress<- paste((Rep_Df$Score_Stress[4] - Rep_Df$Score_Stress[1]))
      }
      
      if(Rep_Df$Score_Stress[5] > Rep_Df$CI_Upper_Lim_Stress[1] | Rep_Df$Score_Stress[5] < Rep_Df$CI_Lower_Lim_Stress[1]) {
        SigChange5_Stress<- paste((Rep_Df$Score_Stress[5] - Rep_Df$Score_Stress[1]), "**")
      } else if(Rep_Df$Score_Stress[5] < Rep_Df$CI_Upper_Lim_Stress[1] & Rep_Df$Score_Stress[5] > Rep_Df$CI_Lower_Lim_Stress[1]) {
        SigChange5_Stress<- paste((Rep_Df$Score_Stress[5] - Rep_Df$Score_Stress[1]))
      }
      
      
      Time1<- paste0(Rep_Df$Date[1])
      Change_Rep_Df5_Stress<- data.frame(Time1, SigChange2_Stress, SigChange3_Stress, SigChange4_Stress, SigChange5_Stress)
      names(Change_Rep_Df5_Stress)[2]<- paste0(Rep_Df$Date[2])
      names(Change_Rep_Df5_Stress)[3]<- paste0(Rep_Df$Date[3])
      names(Change_Rep_Df5_Stress)[4]<- paste0(Rep_Df$Date[4])
      names(Change_Rep_Df5_Stress)[5]<- paste0(Rep_Df$Date[5])  
  
  
kable(Change_Rep_Df5_Stress, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
 if(Rep_Df$Score_Stress[3] > Rep_Df$CI_Upper_Lim_Stress[2] | Rep_Df$Score_Stress[3] < Rep_Df$CI_Lower_Lim_Stress[2]) {
        SigChange5a_Stress<- paste(Rep_Df$Change_Stress[3], "**")
      } else if(Rep_Df$Score_Stress[3] < Rep_Df$CI_Upper_Lim_Stress[2] & Rep_Df$Score_Stress[3] > Rep_Df$CI_Lower_Lim_Stress[2]) {
        SigChange5a_Stress<- paste(Rep_Df$Change_Stress[3])
      }
      
      if(Rep_Df$Score_Stress[4] > Rep_Df$CI_Upper_Lim_Stress[2] | Rep_Df$Score_Stress[4] < Rep_Df$CI_Lower_Lim_Stress[2]) {
        SigChange5b_Stress<- paste((Rep_Df$Score_Stress[4] - Rep_Df$Score_Stress[2]), "**")
      } else if(Rep_Df$Score_Stress[4] < Rep_Df$CI_Upper_Lim_Stress[2] & Rep_Df$Score_Stress[4] > Rep_Df$CI_Lower_Lim_Stress[2]) {
        SigChange5b_Stress<- paste((Rep_Df$Score_Stress[4] - Rep_Df$Score_Stress[2]))
      }
      
      if(Rep_Df$Score_Stress[5] > Rep_Df$CI_Upper_Lim_Stress[2] | Rep_Df$Score_Stress[5] < Rep_Df$CI_Lower_Lim_Stress[2]) {
        SigChange5c_Stress<- paste((Rep_Df$Score_Stress[5] - Rep_Df$Score_Stress[2]), "**")
      } else if(Rep_Df$Score_Stress[5] < Rep_Df$CI_Upper_Lim_Stress[2] & Rep_Df$Score_Stress[5] > Rep_Df$CI_Lower_Lim_Stress[2]) {
        SigChange5c_Stress<- paste((Rep_Df$Score_Stress[5] - Rep_Df$Score_Stress[2]))
      }
      
      
      Time2<- paste0(Rep_Df$Date[2])
      Change_Rep_Df5a_Stress<- data.frame(Time2, SigChange5a_Stress, SigChange5b_Stress, SigChange5c_Stress)
      names(Change_Rep_Df5a_Stress)[2]<- paste0(Rep_Df$Date[3])  
      names(Change_Rep_Df5a_Stress)[3]<- paste0(Rep_Df$Date[4]) 
      names(Change_Rep_Df5a_Stress)[4]<- paste0(Rep_Df$Date[5])   
  
kable(Change_Rep_Df5a_Stress, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
if(Rep_Df$Score_Stress[4] > Rep_Df$CI_Upper_Lim_Stress[3] | Rep_Df$Score_Stress[4] < Rep_Df$CI_Lower_Lim_Stress[3]) {
        SigChange5d_Stress<- paste(Rep_Df$Change_Stress[4], "**")
      } else if(Rep_Df$Score_Stress[4] < Rep_Df$CI_Upper_Lim_Stress[3] & Rep_Df$Score_Stress[4] > Rep_Df$CI_Lower_Lim_Stress[3]) {
        SigChange5d_Stress<- paste(Rep_Df$Change_Stress[4])
      }
      
      if(Rep_Df$Score_Stress[5] > Rep_Df$CI_Upper_Lim_Stress[3] | Rep_Df$Score_Stress[5] < Rep_Df$CI_Lower_Lim_Stress[3]) {
        SigChange5e_Stress<- paste((Rep_Df$Score_Stress[5] - Rep_Df$Score_Stress[3]), "**")
      } else if(Rep_Df$Score_Stress[5] < Rep_Df$CI_Upper_Lim_Stress[3] & Rep_Df$Score_Stress[5] > Rep_Df$CI_Lower_Lim_Stress[3]) {
        SigChange5e_Stress<- paste((Rep_Df$Score_Stress[5] - Rep_Df$Score_Stress[3]))
      }
      
      
      Time3<- paste0(Rep_Df$Date[3])
      Change_Rep_Df5b_Stress<- data.frame(Time3, SigChange5d_Stress, SigChange5e_Stress)
      names(Change_Rep_Df5b_Stress)[2]<- paste0(Rep_Df$Date[4])  
      names(Change_Rep_Df5b_Stress)[3]<- paste0(Rep_Df$Date[5])    
  
kable(Change_Rep_Df5b_Stress, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

```{r, echo = FALSE, warning = FALSE,comment=NA}
if(length(Entered_Scores_Df$Date) == 5) {
  
 if(Rep_Df$Score_Stress[5] > Rep_Df$CI_Upper_Lim_Stress[4] | Rep_Df$Score_Stress[5] < Rep_Df$CI_Lower_Lim_Stress[4]) {
        SigChange5f_Stress<- paste(Rep_Df$Change_Stress[5], "**")
      } else if(Rep_Df$Score_Stress[5] < Rep_Df$CI_Upper_Lim_Stress[4] & Rep_Df$Score_Stress[5] > Rep_Df$CI_Lower_Lim_Stress[4]) {
        SigChange5f_Stress<- paste(Rep_Df$Change_Stress[5])
      }
      
      Time4<- paste0(Rep_Df$Date[4])
      Change_Rep_Df5c_Stress<- data.frame(Time4, SigChange5f_Stress)
      names(Change_Rep_Df5c_Stress)[2]<- paste0(Rep_Df$Date[5])   
  
kable(Change_Rep_Df5c_Stress, booktabs = T, format = "latex") %>% kable_styling(position = "left", full_width = F) %>% row_spec(0, bold = T) %>% column_spec(1, bold = T)
}

```

\newpage

#Most Recent Item Scores

#`r Scores_Table[nrow(Scores_Table),1]`

```{r,echo=FALSE,warning=FALSE,comment=NA}

kable(Item_Df, format = "latex", booktabs = T) %>% kable_styling(position = "left", full_width = T, font_size = 12, latex_options = "striped") %>% row_spec(0, bold = T)
```

\newpage 

\begingroup\Large

\begin{center} \textbf{Information about the Depression Anxiety Stress Scales - 21 (DASS-21)} \end{center} 

#What it Measures: 

* Severity of depression, anxiety and stress. The DASS-21 is **not a diagnostic instrument** and is based on a dimensional rather than categorical understanding of psychological disorder. 

Information below about DASS-21 subscales is derived from a summary provided by the University of New South Wales (http://www2.psy.unsw.edu.au/Groups/Dass/over.htm). 

* The Depression subscale assesses dysphoric mood, feelings of hopelessness, devaluation of life, self-deprecation, lack of interest/participation, anhedonia, and inertia. 
* The Anxiety scale assesses autonomic arousal, skeletal muscle changes, situational anxiety, and the subjective experience of anxious affect.

* The Stress scale is sensitive to levels of chronic non-specific arousal. It assesses difficulty relaxing, nervous arousal, and being easily upset/agitated, irritable/over-reactive and impatient.


#What Higher Scores Mean:

* More severe symptoms of depression, anxiety and stress.


#Scale Quality:

* The DASS-21 has undergone extensive psychometric validation and is one of the most frequently adopted measures within clinical psychology. It is suitable for use with a wide range of populations (Henry & Crawford, 2005). 


#Scale Structure:

* 21-item scale. 

* Three subscales (depression, anxiety & stress), each containing 7 items. Item scores on each subscale are summed.

* A general psychological distress score can be obtained by summing total scores across all subscales. 

* Respondents indicate on a 4-point Likert scale how often (0 = "never"; 3 = "almost always") each statement applied to them during the past week (e.g. "I found it hard to wind down"). 

* Factor analytic research has generally supported a 3-factor structure (Norton, 2007; Page, Hooke & Morisson, 2007), although alternative structural models have also been proposed (Osman, Wong, Bagge, Freedenthal, Gutierrez & Lozano, 2012). 

\endgroup
